### 2022-11-22 manuscripts/paper-1/main.tex
remove generated files, start inoring generated files

\documentclass{article}

\begin{document}

    \title{TODO}
    \author{TODO}
    \maketitle

    \begin{abstract}
        TODO
    \end{abstract}

    \section{Introduction}
    \label{section:introduction}
    TODO

    \section{Conclusion}
    \label{section:conclusion}
    TODO

\end{document}

### 2022-11-23 manuscripts/paper-1/main.tex
remove obsolete readme files; add bibliography commands
start working on first paper

@@
-\documentclass{article}
+\documentclass[conference]{IEEEtran}
+
+\usepackage[colorlinks,allcolors=blue]{hyperref}
 
@@
 
-    \title{TODO}
-    \author{TODO}
+    \title{Quality assurance of digital twins -- An experience report in the automotive industry}
+    \author{
+        \IEEEauthorblockN{
+            Georg Hackenberg
+        }
+        \IEEEauthorblockA{
+            School of Engineering\\
+            University of Applied Sciences Upper Austria\\
+            4600 Wels, Upper Austria, Austria\\
+            \href{mailto:georg.hackenberg@fh-wels.at}{georg.hackenberg@fh-wels.at}
+        }
+        \and
+        \IEEEauthorblockN{
+            Alican Tüzün
+        }
+        \IEEEauthorblockA{
+            School of Engineering\\
+            University of Applied Sciences Upper Austria\\
+            4600 Wels, Upper Austria, Austria\\
+            \href{mailto:alican.tuzuen@fh-wels.at}{alican.tuzuen@fh-wels.at}
+        }
+    }
     \maketitle
@@
     \begin{abstract}
-        TODO
+        Digital twins are becoming more and more important for the efficient and effective development and operation of cyber-physical systems.
+        However, digital twins are only useful if they reflect the real-world system accurately enough, i.e.\ their quality is high enough.
+        This claim entails the question, what the term quality in the context of digital twins actually means and how it can be measured.
+        In this article, we present our experience with quality assurance of a digital twin for an assembly line in the automotive industry.
+        We explain our preliminary definition of digital twin quality, which we derive from classical quality models for general software systems.
+        Furthermore, we describe quality issues, which we were able to detect in a digital twin of an assembly line in the automotive industry.
+        Finally, we draw conclusions about how to leverage from our experience in different contexts and how to generalize the underlying approaches.
     \end{abstract}
@@
     \label{section:introduction}
+    TODO~\cite{Boschert2016,Fuller2020,Jones2020}
+
+    \section{What is a digital twin?}
+    TODO
+
+    \subsection{Methodology}
+    TODO
+
+    \subsection{Result}
+    TODO
+
+    \subsection{Validation}
+    TODO
+
+    \section{What is digital twin quality?}
+    TODO
+
+    \subsection{Methodology}
+    TODO
+
+    \subsection{Result}
+    TODO
+
+    \subsection{Validation}
+    TODO
+
+    \section{What are digital twin quality issues?}
+    TODO
+
+    \subsection{Methodology}
+    TODO
+
+    \subsection{Result}
+    TODO
+
+    \subsection{Validation}
     TODO
@@
 
+    \bibliography{main}
+    \bibliographystyle{plain}
+
 \end{document}

### 2022-11-27 manuscripts/paper-1/main.tex
P1 add introduction  & test for the manual latex & git

@@
 
-    \section{Introduction}
-    \label{section:introduction}
-    TODO~\cite{Boschert2016,Fuller2020,Jones2020}
+    \section{Introduction}\label{section:introduction}
+    Cyber-physical system (CPS), is a conceptial architecture/approach which aims to conjoin the physical and virtual space. 
+    The aim of the CPS is to integrate communication and computing capabilities to physical assets to monitor, coordinate and control the physical space (where the physical assets exist)
+    from the virtual space (where the virtual models exist), while achieve seamless real-time connection between the spaces.
+    Digital twin approach is on the other hand, is a pragmatic solution, which is the execution of the CPS.\cite{TAO20193}
+    \section{What is a digital twin?}
+    First occurance of "Digital Twin" term  was introduced by Dr.Michael Grieves in 2003 at the University of Michigan while giving 
+    Product Lifecycle Management(PLM) course.\cite{article} His introduction to term was rather raw, but still introduced a pragmatic solution to uncoupled solutions of global manufacturers
+    ,which were working only with physical or virtual products.\newline
+    His approach had three dimensions, along with a physical entity, a virtual entity and a connection between these entities which constructed the main frame for the todays evaluating  
+    digital twins. \cite{article} \newline
+    Physical entity exists in the physical space with real functionalities and performance. They are responsible to accomplish certain tasks within the physical space, to give certain outputs. 
+    Different levels of abstraction can be usable for a physical entity such as a electric motor in the 1/10 of a RC Car, bearings in a certain machine, solar panels above some construction, human or a entire world can be counted as an example of a physical entity.
+    Virtual entity exists in the virtual space with
 
-    \section{What is a digital twin?}
-    TODO
+    With the imrpovement
 
+    %/TODO SHOULD WE EXPLAIN OUR DIGITAL TWIN HERE?
     \subsection{Methodology}

### 2022-12-06 manuscripts/paper-1/main.tex
refine paper outline

--- 2022-11-23 manuscripts/paper-1/main.tex
@@
 
-    \section{Introduction}
-    \label{section:introduction}
-    TODO~\cite{Boschert2016,Fuller2020,Jones2020}
+    \section{Introduction}\label{section:introduction}
 
-    \section{What is a digital twin?}
-    TODO
+    Cyber-physical system (CPS), is a conceptual architecture/approach which aims to conjoin the physical and virtual space. 
+    The aim of the CPS is to integrate communication and computing capabilities to physical assets to monitor, coordinate and control the physical space (where the physical assets exist) from the virtual space (where the virtual models exist), while achieve seamless real-time connection between the spaces.
+    Digital twin approach is on the other hand, is a pragmatic solution, which is the execution of the CPS.~\cite{TAO20193}
+
+    First occurrence of "Digital Twin" term  was introduced by Dr.~Michael Grieves in 2003 at the University of Michigan while giving  Product Lifecycle Management(PLM) course.~\cite{article}
+    His introduction to term was rather raw, but still introduced a pragmatic solution to uncoupled solutions of global manufacturers, which were working only with physical or virtual products.
+
+    His approach had three dimensions, along with a physical entity, a virtual entity and a connection between these entities which constructed the main frame for the today's evaluating digital twins.~\cite{article}
+
+    Physical entity exists in the physical space with real functionalities and performance. They are responsible to accomplish certain tasks within the physical space, to give certain outputs.
+    Different levels of abstraction can be usable for a physical entity such as an electric motor in the 1/10 of an RC Car, bearings in a certain machine, solar panels above some construction, human or an entire world can be counted as an example of a physical entity.
+    Virtual entity exists in the virtual space with
+
+    With the improvement
+
+    %/TODO SHOULD WE EXPLAIN OUR DIGITAL TWIN HERE?
+
+    \subsection{Research objectives}
+
+    Find approach for assessing the quality of digital twins...
+
+    \subsection{Research questions}
+
+    What is quality of digital twins?
+What is good quality?
+What is bad quality?
+What is impact of good quality?
+What is impact of bad quality?
+What are typical quality issues?
+How to assess quality?
+...
+
+    \subsection{Scientific contributions}
+
+    Literature review (see Section~\ref{section:literature}), case study (see Section~\ref{section:case})...
+
+    \section{Literature review}
+    \label{section:literature}
+
+    Methodology (see Section~\ref{section:liteature_methodology}), result (see Section~\ref{section:liteature_result}), and summary (See Section~\ref{section:liteature_summary})...
 
     \subsection{Methodology}
+    \label{section:liteature_methodology}
+
+    How did we find existing literature?
+
+    \begin{itemize}
+        \item ("digital twin" OR "simulation model" OR "system model" OR "CAD model") AND (quality OR defect OR issue OR error)
+        \item ("digital twin" OR "simulation model" OR "system model" OR "CAD model") AND (verification OR validation OR accreditation)
+    \end{itemize}
+
+    \subsection{Result}
+    \label{section:liteature_result}
+
+    What is existing literature?
+
+    \subsection{Summary}
+    \label{section:liteature_summary}
+
+    What do we learn from existing literature?
+    (Existing literature does at most partially solve our problem!)
+
+    \section{Case study (FELICE)}
+    \label{section:case}
+
+    TODO (Explain limitations of the FELICE digital twin! It is not a complete digital twin according to literature! It includes this, it is missing this.)
+
+    \subsection{Methodology}
+    \label{section:case_methodology}
+
     TODO
@@
     \subsection{Result}
+    \label{section:case_result}
+
     TODO
 
-    \subsection{Validation}
-    TODO
+    \subsection{Summary}
+    \label{section:case_summary}
 
-    \section{What is digital twin quality?}
-    TODO
-
-    \subsection{Methodology}
-    TODO
-
-    \subsection{Result}
-    TODO
-
-    \subsection{Validation}
-    TODO
-
-    \section{What are digital twin quality issues?}
-    TODO
-
-    \subsection{Methodology}
-    TODO
-
-    \subsection{Result}
-    TODO
-
-    \subsection{Validation}
     TODO
@@
 
+    \section*{Acknowledgements}
+    TODO
+
     \bibliography{main}

### 2022-12-11 manuscripts/paper-1/main.tex
fix email address
Finishing up the introduction

@@
-\documentclass[conference]{IEEEtran}
+\documentclass[9pt,conference]{IEEEtran}
 
@@
             4600 Wels, Upper Austria, Austria\\
-            \href{mailto:alican.tuzuen@fh-wels.at}{alican.tuzuen@fh-wels.at}
+            \href{mailto:alican.tuezuen@fh-wels.at}{alican.tuezuen@fh-wels.at}
         }
@@
 
-    Cyber-physical system (CPS), is a conceptual architecture/approach which aims to conjoin the physical and virtual space. 
-    The aim of the CPS is to integrate communication and computing capabilities to physical assets to monitor, coordinate and control the physical space (where the physical assets exist) from the virtual space (where the virtual models exist), while achieve seamless real-time connection between the spaces.
-    Digital twin approach is on the other hand, is a pragmatic solution, which is the execution of the CPS.~\cite{TAO20193}
+    Cyber-physical system (CPS), is a conceptual architecture/approach which aims to conjoin the physical and virtual space tightly. 
+    The aim of the CPS is to integrate communication and computing capabilities to physical entities to monitor, coordinate and control the physical space (where the physical assets exist) from the virtual space (where the virtual models exist), while achieving seamless, real-time connection between the spaces.
+    Digital twin approach is on the other hand, is a pragmatic solution, which is the execution of the CPS idea.~\cite{TAO20193}
 
     First occurrence of "Digital Twin" term  was introduced by Dr.~Michael Grieves in 2003 at the University of Michigan while giving  Product Lifecycle Management(PLM) course.~\cite{article}
-    His introduction to term was rather raw, but still introduced a pragmatic solution to uncoupled solutions of global manufacturers, which were working only with physical or virtual products.
+    His introduction to term was rather raw, but still introduced a pragmatic solution to gather more data from the physical entities, to achieve the "Lean" idea.
 
-    His approach had three dimensions, along with a physical entity, a virtual entity and a connection between these entities which constructed the main frame for the today's evaluating digital twins.~\cite{article}
+    His approach has three dimensions, along with a physical entity, a virtual entity and a connection between these entities which constructed the main frame for the today's evaluating digital twins.~\cite{article}
 
-    Physical entity exists in the physical space with real functionalities and performance. They are responsible to accomplish certain tasks within the physical space, to give certain outputs.
+    Physical entity exists only in the physical space with real functionalities and performance. It is responsible to accomplish certain tasks within the physical space, to give certain outputs.
     Different levels of abstraction can be usable for a physical entity such as an electric motor in the 1/10 of an RC Car, bearings in a certain machine, solar panels above some construction, human or an entire world can be counted as an example of a physical entity.
-    Virtual entity exists in the virtual space with
 
-    With the improvement
+    Virtual entity exists only in the virtual space, which should imitate the physical entity with high fidelity models. If we consider the virtual entity as a function;
+
+    \begin{equation}\label{Formulated Entity Equation}
+        VE = (G_v, P_v, B_v, R_v)
+    \end{equation}
+    where:
+
+    $G_v$ represents the geometry model, $P_v$ represents the physical model, $B_v$ represents  the behavior model, and $R_v$ represents the rule model~\cite{article}.
+
+    The last dimension, is the connection between the physical space and virtual space.
+Physical space created realtime data, and through the connection, these data will be received by the virtual space,
+    and updates the states of the models. Virtual space sends the needed information to the physical space.
+
+    There is also another, up to date approach which adds two more dimensions(Data and Services), to the traditional digital twin model which is descriebed above.~\cite{article}
+
+    \begin{equation}
+        M_{dt} = (PE,VE,Ss,DD,CN)
+    \end{equation}
+    \begin{description}
+        \item[PE] Represents Physical Entity
+        \item[VE] Represents Virtual Entity
+        \item[Ss] Represents Digital Twin Services
+        \item[DD] Represents Digital Twin Data
+        \item[CN] Represents Connections
+        \end{description}
 

### 2022-12-11 manuscripts/paper-1/main.tex
Grammer Check as well as read  through should be done. Still going to write literature review tomorrow.

@@
         However, digital twins are only useful if they reflect the real-world system accurately enough, i.e.\ their quality is high enough.
-        This claim entails the question, what the term quality in the context of digital twins actually means and how it can be measured.
-        In this article, we present our experience with quality assurance of a digital twin for an assembly line in the automotive industry.
+        This claim entails the question, of what the term quality in the context of digital twins means and how it can be measured.
+        In this article, we present our experience with the quality assurance of a digital twin for an assembly line in the automotive industry.
         We explain our preliminary definition of digital twin quality, which we derive from classical quality models for general software systems.
         Furthermore, we describe quality issues, which we were able to detect in a digital twin of an assembly line in the automotive industry.
-        Finally, we draw conclusions about how to leverage from our experience in different contexts and how to generalize the underlying approaches.
+        Finally, we conclude how to leverage our experience in different contexts and how to generalize the underlying approaches.
     \end{abstract}
@@
     Cyber-physical system (CPS), is a conceptual architecture/approach which aims to conjoin the physical and virtual space tightly. 
-    The aim of the CPS is to integrate communication and computing capabilities to physical entities to monitor, coordinate and control the physical space (where the physical assets exist) from the virtual space (where the virtual models exist), while achieving seamless, real-time connection between the spaces.
-    Digital twin approach is on the other hand, is a pragmatic solution, which is the execution of the CPS idea.~\cite{TAO20193}
+    The CPS aims to integrate communication and computing capabilities to physical entities to monitor, coordinate and control the physical space (where the physical assets exist) from the virtual space (where the virtual models exist) while achieving seamless, real-time connection between the spaces.
+    The Digital twin approach, on the other hand, is a pragmatic solution, which is the execution of the CPS idea.~\cite{TAOCHAPTER1}
 
-    First occurrence of "Digital Twin" term  was introduced by Dr.~Michael Grieves in 2003 at the University of Michigan while giving  Product Lifecycle Management(PLM) course.~\cite{article}
-    His introduction to term was rather raw, but still introduced a pragmatic solution to gather more data from the physical entities, to achieve the "Lean" idea.
+    The first occurrence of the "Digital Twin" term was introduced by Dr.~Michael Grieves in 2003 at the University of Michigan while giving the Product Lifecycle Management (PLM) course.~\cite{DTGRIEVES}
+    His introduction to the term was rather raw but still introduced a pragmatic solution to gather more data from the physical entities, to achieve the "Lean" idea.
 
-    His approach has three dimensions, along with a physical entity, a virtual entity and a connection between these entities which constructed the main frame for the today's evaluating digital twins.~\cite{article}
+    His approach has three dimensions, along with a physical entity, a virtual entity and a connection between these entities which constructed the main frame for today's evaluating digital twins.~\cite{DTGRIEVES}
 
-    Physical entity exists only in the physical space with real functionalities and performance. It is responsible to accomplish certain tasks within the physical space, to give certain outputs.
+    A physical entity exists only in the physical space with real functionalities and performance. It is responsible to accomplish certain tasks within the physical space, to give certain outputs.
     Different levels of abstraction can be usable for a physical entity such as an electric motor in the 1/10 of an RC Car, bearings in a certain machine, solar panels above some construction, human or an entire world can be counted as an example of a physical entity.
 
-    Virtual entity exists only in the virtual space, which should imitate the physical entity with high fidelity models. If we consider the virtual entity as a function;
+    A virtual entity exists only in the virtual space, which should imitate the physical entity with high-fidelity models. If we consider the virtual entity as a function;
 
@@
 
-    $G_v$ represents the geometry model, $P_v$ represents the physical model, $B_v$ represents  the behavior model, and $R_v$ represents the rule model~\cite{article}.
+    $G_v$ represents the geometry model, $P_v$ represents the physical model, $B_v$ represents  the behavior model, and $R_v$ represents the rule model~\cite{DTGRIEVES}.
 
-    The last dimension, is the connection between the physical space and virtual space.
-Physical space created realtime data, and through the connection, these data will be received by the virtual space,
+    The last dimension is the connection between physical space and virtual space. Physical space created real-time data, and through the connection, these data will be received by the virtual space 
     and updates the states of the models. Virtual space sends the needed information to the physical space.
 
-    There is also another, up to date approach which adds two more dimensions(Data and Services), to the traditional digital twin model which is descriebed above.~\cite{article}
+    There is also another, an up-to-date approach that adds two more dimensions(Data and Services), to the traditional digital twin model which is described above.~\cite{DTGRIEVES}
 
@@
     \end{equation}
+
     \begin{description}
-        \item[PE] Represents Physical Entity
-        \item[VE] Represents Virtual Entity
-        \item[Ss] Represents Digital Twin Services
-        \item[DD] Represents Digital Twin Data
-        \item[CN] Represents Connections
+        \item[PE] Represents DT Physical Entity
+        \item[VE] Represents DT Virtual Entity
+        \item[Ss] Represents DT Services
+        \item[DD] Represents DT Data
+        \item[CN] Represents DT Connections
     \end{description}
+    If we consider the dimensions we above discussed as vertical dimensions, if we divide our digital twin horizontally into three different layers, the explanation of the digital twin systems becomes much clearer.
+    \begin{itemize}
+        \item Unit DT which only has one PE in the physical space
+        \item System DT  is an assembly of PE's in the physical space
+        \item System of Systems DT  is an assembly of systems in the physical space
+    \end{itemize}
 
-    %/TODO SHOULD WE EXPLAIN OUR DIGITAL TWIN HERE?
+    Of course, there are other explanations, approaches, and architectures to digital twins, but like every other digital transformation approach, the main goal is to get into the lean state,
+    which is an optimal approach to our problem.
 
+    Also should be noted that the digital twin approach was introduced within the PLM course.
+PLM is nothing but an improvement to the lean manufacturing philosophy, which aims to eliminate waste(Time, energy, Material) not only during the
+    manufacturing process but also during the lifecycle of the product.~\cite{grieves2006PLM} 
+    It's an approach to achieve the lean state, which overlaps with the idea of digital twins, which both aim to gather more information about the product, starting from the design phase to the disposal of the product.
+
+    Achieving a full-scale cyber-physical system is not only a goal for the digital twin but also an essential challenge.
+The following are some examples of the challenges which is occurring during the development of a digital twin:
+    \begin{itemize}
+        \item High fidelity modeling and simulation
+        \item Real-Time communication between the components of digital twin 
+        \item Flexible data architecture
+        \item Developing standards and protocols for the use of digital twins so that they can be used consistently across different industries and applications.
+        \item Cost and Cost Management
+        \item Cyber Security
+        \item Quality Assurance of the digital twin
+        \item Information inefficiency regarding the theme Digital Twins
+        \item \dots{}
+    \end{itemize}
+
+    %TODO: How we are writing this?
     \subsection{Research objectives}
 
-    Find approach for assessing the quality of digital twins...
+    Find an approach to assess the quality of Digital twins
 
@@
 
-    What is quality of digital twins?
+    What is the quality of digital twins?
 What is good quality?
 What is bad quality?
-What is impact of good quality?
+What is the impact of good quality?
 What is impact of bad quality?
@@
 
-    What is existing literature?
+    What is the existing literature?
 
@@
 
-    TODO (Explain limitations of the FELICE digital twin! It is not a complete digital twin according to literature! It includes this, it is missing this.)
+    TODO (Explain the limitations of the FELICE digital twin! It is not a complete digital twin according to literature! It includes this, it is missing this.)
 

### 2022-12-13 manuscripts/paper-1/main.tex
Improving the literature review methodology

@@
     \subsection{Research questions}
+    \label{section:Research Questions}
 
@@
     What is the impact of good quality? 
-What is impact of bad quality?
+    What is impact of bad quality? W
     What are typical quality issues? 
     How to assess quality?
-...
 
@@
 
-    Literature review (see Section~\ref{section:literature}), case study (see Section~\ref{section:case})...
+    Literature review (see Section~\ref{section:literature}), case study (see Section~\ref{section:Research Questions})...
 
@@
     \label{section:literature}
+    Literature analysis was executed, to analyze current DT literature within the concept of digital twin quality. The analysis, especially focused on 
+    how the digital twin quality is mentioned and assessed within the academic dissertations.
 
     Methodology (see Section~\ref{section:liteature_methodology}), result (see Section~\ref{section:liteature_result}), and summary (See Section~\ref{section:liteature_summary})...
-
     \subsection{Methodology}
@@
 
-    How did we find existing literature?
+    Google Scholar(GS), Scopus(SCP) and Research Rabbit(RR) tools are used to fulfill our requirements for the literature review. 
+    Since there is a great number of digital twin publications in academics, narrowing the research is necessary, so the following filtering has been done for all searches.
+    \begin{itemize}
+        \item Dissertations should be written in English and published in a journal.
+        \item Paper is not older than 2018
+    \end{itemize}
 
+    Search terms appeared in the title/abstract with "digital twin quality";
     \begin{itemize}
-        \item ("digital twin" OR "simulation model" OR "system model" OR "CAD model") AND (quality OR defect OR issue OR error)
-        \item ("digital twin" OR "simulation model" OR "system model" OR "CAD model") AND (verification OR validation OR accreditation)
+        \item GS = allintitle: "digital twin quality" Return articles dated between 2018 - NOW  
+        \item Scopus = TITLE-ABS-KEY ( "digital twin quality" )  AND  PUBYEAR  \textgreater  2018  AND  PUBYEAR  \textless  2023  AND  ( LIMIT-TO ( LANGUAGE ,  "English" ) ) 
     \end{itemize}
+
+    GS gave five different results, while SCP gave 2 results.
+
+    Further inspection has been done, and
 

### 2022-12-13 manuscripts/paper-1/main.tex
Added the method, also nearly done with the literature review for the first subject

--- 2022-12-11 manuscripts/paper-1/main.tex
@@
 \documentclass[9pt,conference]{IEEEtran}
-
+\usepackage{listings}
+\usepackage{graphicx}
 \usepackage[colorlinks,allcolors=blue]{hyperref}
+\graphicspath{{./images/}}
 
@@
 
-    \subsection{Research questions}
+    \subsection{Research questions}~\label{section: Research Questions}
 
@@
     What is the impact of good quality? 
-What is impact of bad quality?
+    What is the impact of bad quality? W
     What are typical quality issues? 
     How to assess quality?
-...
 
@@
 
-    Literature review (see Section~\ref{section:literature}), case study (see Section~\ref{section:case})...
+    Literature review (see Section~\ref{section: literature}), case study (see Section~\ref{section: Research Questions})...
 
-    \section{Literature review}
-    \label{section:literature}
+    \section{Literature review}~\label{section: literature}
+    Literature analysis was executed, to analyze current DT literature within the concept of digital twin quality. The analysis especially focused on 
+    how the digital twin quality is mentioned and assessed within the academic dissertations.
 
     Methodology (see Section~\ref{section:liteature_methodology}), result (see Section~\ref{section:liteature_result}), and summary (See Section~\ref{section:liteature_summary})...
+    \subsection{Methodology}~\label{section:liteature_methodology}
+    Google Scholar (GS), Scopus (SCP) and Research Rabbit (RR) tools are used to fulfill our requirements for the literature review. 
+    Since there is a great number of digital twin publications in academics, 
+    narrowing the research is necessary, so the following algorithm which can be seen in Figure \ref{fig:literaturesearchalgorithm} with several levels of filtering will be applied.
 
-    \subsection{Methodology}
-    \label{section:liteature_methodology}
-
-    How did we find existing literature?
-
+    First filtering will be done with the following criteria:
     \begin{itemize}
-        \item ("digital twin" OR "simulation model" OR "system model" OR "CAD model") AND (quality OR defect OR issue OR error)
-        \item ("digital twin" OR "simulation model" OR "system model" OR "CAD model") AND (verification OR validation OR accreditation)
+        \item Dissertations should be written in English and published in a journal/conference.
+        \item Paper is not older than 2018
+        \item Search term should be exactly searched.
     \end{itemize}
 
-    \subsection{Result}
-    \label{section:liteature_result}
+    Filtering query calls for the GS and SCP are the following:
+    \begin{itemize}
+        \item Google Scholar = "search term"
+        \item Scopus = ALL ( "digital twin quality" ) AND PUBYEAR > 2018 AND PUBYEAR < 2023 AND ( LIMIT-TO ( LANGUAGE , "English" )) 
+    \end{itemize}
 
-    What is the existing literature?
+    Also want to note that, in the GS, there isn't a function that filters the dates, instead the user should click the Since 2018 option to filter the dates.
 
-    \subsection{Summary}
-    \label{section:liteature_summary}
+    Second filtering will be done to eliminate the duplications, which can occur when GS and SCP give the same result.
+    \begin{itemize}
+        \item Remove Duplications
+        \item Remove the dissertations which are not English manually
+    \end{itemize}
+
+    Even though we already filtered the language, still some dissertations results will appear because of the auto translation which they put on the website.
+    So second time should be filtered manually.
+
+    After the second filtration, the third filtering which is a manual investigation should occur with the following filtering criteria:
+    \begin{itemize}
+        \item Proper literature review should be present in the selected paper
+        \item Abstract and conclusion should be relevant to the search term
+    \end{itemize}
+
+    \begin{figure}
+        \centering
+        \includegraphics[width =0.45\textwidth]{LRMethod.png}
+        \caption{Literature Search Algorithm}
+        \label{fig:literaturesearchalgorithm}
+    \end{figure} 
+    \begin{figure}
+        \centering
+        \includegraphics[width =0.45\textwidth]{LRMethodLegacy.png}
+        \caption{Literature Search Algorithm Legend}
+        \label{fig:literaturesearchalgorithmlegend}
+    \end{figure}
+
+    %TODO: ADD THE METHOD HERE
+
+    \subsection{Result}~\label{section:liteature_result}
+    The following results were achieved by selecting several  search terms, which is 
+    \subsubsection*{Digital Twin Quality}\label{subsection:Digital Twin Quality}
+
+    First filtering is done for the search term "digital twin quality", meanwhile GS gave 41 different results, and SCP gave only 3 results.
+    After the second filtering process, 3 duplications and 31 different results were found. 10 dissertations were not in English.
+    After the third filtering process, 9 dissertations passed and the rest is rejected.
+
+    \subsubsection*{Digital Twin Testing}\label{subsection:Digital Twin Quality}
+    %What is the existing literature?
+
+    \subsection{Summary}~\label{section:liteature_summary}
 
@@
 
-    \section{Case study (FELICE)}
-    \label{section:case}
+    \section{Case study (FELICE)}~\label{section:case}
 
@@
 
-    \subsection{Methodology}
-    \label{section:case_methodology}
+    \subsection{Methodology}~\label{section:case_methodology}
 
@@
 
-    \subsection{Result}
-    \label{section:case_result}
+    \subsection{Result}~\label{section:case_result}
 
@@
 
-    \subsection{Summary}
-    \label{section:case_summary}
+    \subsection{Summary}~\label{section:case_summary}
 
@@
 
-    \section{Conclusion}
-    \label{section:conclusion}
+    \section{Conclusion}~\label{section:conclusion}
     TODO

### 2022-12-14 manuscripts/paper-1/main.tex
Last one before meeting

@@
     The first occurrence of the "Digital Twin" term was introduced by Dr.~Michael Grieves in 2003 at the University of Michigan while giving the Product Lifecycle Management (PLM) course.~\cite{DTGRIEVES}
-    His introduction to the term was rather raw but still introduced a pragmatic solution to gather more data from the physical entities, to achieve the "Lean" idea.
+    His introduction to the term was rather raw but still introduced a pragmatic solution to gather more data from the physical entities, to achieve the "Lean" state.
 
@@
 
-    A virtual entity exists only in the virtual space, which should imitate the physical entity with high-fidelity models. If we consider the virtual entity as a function;
+    On the other hand, a virtual entity exists only in the virtual space, which should imitate the physical entity with high-fidelity models. If we consider the virtual entity as a function;
 
@@
 
-    The last dimension is the connection between physical space and virtual space. Physical space created real-time data, and through the connection, these data will be received by the virtual space 
+    The last dimension of a 3D-DT is the connection between physical space and virtual space.
+Physical space creates real-time data, and through the connection, these data will be received by the virtual space
     and updates the states of the models. Virtual space sends the needed information to the physical space.
 
-    There is also another, an up-to-date approach that adds two more dimensions(Data and Services), to the traditional digital twin model which is described above.~\cite{DTGRIEVES}
+    There is also another, an up-to-date approach that adds two more dimensions (Data and Services), to the traditional digital twin model which is described above.~\cite{DTGRIEVES}
 
@@
     \end{description}
-    If we consider the dimensions we above discussed as vertical dimensions, if we divide our digital twin horizontally into three different layers, the explanation of the digital twin systems becomes much clearer.
+    If we consider the dimensions, we discussed above as vertical dimensions within a single layer, the digital twins also can have three different horizontal layers\cite{TAOCHAPTER1}. 
+    The need for such layers is that the explanation of the digital twin systems becomes much clearer. These can be identified as:
     \begin{itemize}
-        \item Unit DT which only has one PE in the physical space
+        \item Unit DT has one PE in the physical space
         \item System DT is an assembly of PE's in the physical space
@@
 
+    There is also the possibility to add more horizontal layers and define them differently such as a Part layer, Component layer, Machine layer, Production line layer, Shop-floor Layer.\cite{MultiScaleModeling4Layers}
+
     Of course, there are other explanations, approaches, and architectures to digital twins, but like every other digital transformation approach, the main goal is to get into the lean state,
-    which is an optimal approach to our problem.
+    which regards the optimal approach to any problem.
 
-    Also should be noted that the digital twin approach was introduced within the PLM course.
-PLM is nothing but an improvement to the lean manufacturing philosophy, which aims to eliminate waste(Time, energy, Material) not only during the
+    Also should be noted that the digital twin approach was introduced within the PLM course. PLM is nothing but an improvement to the lean manufacturing philosophy,
+    which aims to eliminate waste (Time, Energy and Material waste) not only during the
     manufacturing process but also during the lifecycle of the product.~\cite{grieves2006PLM} 
-    It's an approach to achieve the lean state, which overlaps with the idea of digital twins, which both aim to gather more information about the product, starting from the design phase to the disposal of the product.
+    It's an approach to achieve the lean state, which overlaps with the idea of digital twins.
+Both aim to gather more information about the product, starting from the design phase to the disposal of the product.
 
@@
         \item Flexible data architecture
-        \item Developing standards and protocols for the use of digital twins so that they can be used consistently across different industries and applications.
+        \item Developing standards and protocols for the use of digital twins so that they can be used consistently across different 
+        industries and applications
         \item Cost and Cost Management
@@
         \item Quality Assurance of the digital twin
-        \item Information inefficiency regarding the theme Digital Twins
+        \item Information inefficiency
         \item \dots{}
@@
 
-    Methodology (see Section~\ref{section:liteature_methodology}), result (see Section~\ref{section:liteature_result}), and summary (See Section~\ref{section:liteature_summary})...
+    Methodology (see Section~\ref{section:liteature_methodology}), Result (see Section~\ref{section:liteature_result}), and Summary (See Section~\ref{section:liteature_summary})...
     \subsection{Methodology}~\label{section:liteature_methodology}
@@
         \item Dissertations should be written in English and published in a journal/conference.
-        \item Paper is not older than 2018
+        \item Dissertations should not be older than 2018
         \item Search term should be exactly searched.
@@
 
-    Second filtering will be done to eliminate the duplications, which can occur when GS and SCP give the same result.
+    Second filtering will be done to eliminate the duplications and even though authors already filtered the search for the English language,
+    still some results without the English language will appear. Again, language filtering should be done to clean the results.
+
     \begin{itemize}
@@
 
-    Even though we already filtered the language, still some dissertations results will appear because of the auto translation which they put on the website.
-    So second time should be filtered manually.
-
     After the second filtration, the third filtering which is a manual investigation should occur with the following filtering criteria:
     \begin{itemize}
-        \item Proper literature review should be present in the selected paper
+        \item Proper literature review should be present in the selected dissertation
         \item Abstract and conclusion should be relevant to the search term
@@
 
+    If an interesting dissertation(s) would be found during the reading, it will be checked again with the first filter.
     \begin{figure}
@@
 
-    %TODO: ADD THE METHOD HERE
+    \subsection{Result}~\label{section:liteature_result}
+    The following results were achieved by selecting several search terms.
+    \subsubsection*{Digital Twin Quality}\label{subsection:DigitalTwinQuality}
 
-    \subsection{Result}~\label{section:liteature_result}
-    The following results were achieved by selecting several  search terms, which is 
-    \subsubsection*{Digital Twin Quality}\label{subsection:Digital Twin Quality}
-
-    First filtering is done for the search term "digital twin quality", meanwhile GS gave 41 different results, and SCP gave only 3 results.
+    First filtering was done for the search term "digital twin quality", meanwhile GS gave 41 different results, and SCP gave only 3 results.
     After the second filtering process, 3 duplications and 31 different results were found. 10 dissertations were not in English.
@@
 
-    \subsubsection*{Digital Twin Testing}\label{subsection:Digital Twin Quality}
+    \subsubsection*{Digital Twin Model Verification}\label{subsection:DigitalTwinVerification}
+
+    \subsubsection*{Digital Twin Model Validation}\label{subsection:DigitalTwinValidation}
     %What is the existing literature?
@@
     What do we learn from existing literature?
+
+    He Zhang et al.introduced a consistency evaluation method for digital twin models, which can be used to assess the quality of the digital twin~\cite{ConsistencyEvolutionMethodForDigitalTwins}.
     (Existing literature does at most partially solve our problem!)

### 2023-01-17 manuscripts/paper-1/main.tex
introduce framework sections

--- 2022-12-13 manuscripts/paper-1/main.tex
@@
-\documentclass[9pt,conference]{IEEEtran}
+\documentclass[conference]{IEEEtran}
 
 \usepackage[colorlinks,allcolors=blue]{hyperref}
+\usepackage{amsfonts}
 
@@
         However, digital twins are only useful if they reflect the real-world system accurately enough, i.e.\ their quality is high enough.
-        This claim entails the question, of what the term quality in the context of digital twins means and how it can be measured.
-        In this article, we present our experience with the quality assurance of a digital twin for an assembly line in the automotive industry.
+        This claim entails the question, what the term quality in the context of digital twins actually means and how it can be measured.
+        In this article, we present our experience with quality assurance of a digital twin for an assembly line in the automotive industry.
         We explain our preliminary definition of digital twin quality, which we derive from classical quality models for general software systems.
         Furthermore, we describe quality issues, which we were able to detect in a digital twin of an assembly line in the automotive industry.
-        Finally, we conclude how to leverage our experience in different contexts and how to generalize the underlying approaches.
+        Finally, we draw conclusions about how to leverage from our experience in different contexts and how to generalize the underlying approaches.
     \end{abstract}
@@
 
-    Cyber-physical system (CPS), is a conceptual architecture/approach which aims to conjoin the physical and virtual space tightly. 
-    The CPS aims to integrate communication and computing capabilities to physical entities to monitor, coordinate and control the physical space (where the physical assets exist) from the virtual space (where the virtual models exist) while achieving seamless, real-time connection between the spaces.
-    The Digital twin approach, on the other hand, is a pragmatic solution, which is the execution of the CPS idea.~\cite{TAOCHAPTER1}
+    Cyber-physical system (CPS), is a conceptual architecture/approach which aims to conjoin the physical and virtual space. 
+    The aim of the CPS is to integrate communication and computing capabilities to physical assets to monitor, coordinate and control the physical space (where the physical assets exist) from the virtual space (where the virtual models exist), while achieve seamless real-time connection between the spaces.
+    Digital twin approach is on the other hand, is a pragmatic solution, which is the execution of the CPS.~\cite{TAO20193}
 
-    The first occurrence of the "Digital Twin" term was introduced by Dr.~Michael Grieves in 2003 at the University of Michigan while giving the Product Lifecycle Management (PLM) course.~\cite{DTGRIEVES}
-    His introduction to the term was rather raw but still introduced a pragmatic solution to gather more data from the physical entities, to achieve the "Lean" idea.
+    First occurrence of "Digital Twin" term  was introduced by Dr.~Michael Grieves in 2003 at the University of Michigan while giving  Product Lifecycle Management(PLM) course.~\cite{article}
+    His introduction to term was rather raw, but still introduced a pragmatic solution to uncoupled solutions of global manufacturers, which were working only with physical or virtual products.
 
-    His approach has three dimensions, along with a physical entity, a virtual entity and a connection between these entities which constructed the main frame for today's evaluating digital twins.~\cite{DTGRIEVES}
+    His approach had three dimensions, along with a physical entity, a virtual entity and a connection between these entities which constructed the main frame for the today's evaluating digital twins.~\cite{article}
 
-    A physical entity exists only in the physical space with real functionalities and performance. It is responsible to accomplish certain tasks within the physical space, to give certain outputs.
+    Physical entity exists in the physical space with real functionalities and performance. They are responsible to accomplish certain tasks within the physical space, to give certain outputs.
     Different levels of abstraction can be usable for a physical entity such as an electric motor in the 1/10 of an RC Car, bearings in a certain machine, solar panels above some construction, human or an entire world can be counted as an example of a physical entity.
+    Virtual entity exists in the virtual space with
 
-    A virtual entity exists only in the virtual space, which should imitate the physical entity with high-fidelity models. If we consider the virtual entity as a function;
+    With the improvement
 
-    \begin{equation}\label{Formulated Entity Equation}
-        VE = (G_v, P_v, B_v, R_v)
-    \end{equation}
-    where:
+    %/TODO SHOULD WE EXPLAIN OUR DIGITAL TWIN HERE?
 
-    $G_v$ represents the geometry model, $P_v$ represents the physical model, $B_v$ represents  the behavior model, and $R_v$ represents the rule model~\cite{DTGRIEVES}.
-
-    The last dimension is the connection between physical space and virtual space. Physical space created real-time data, and through the connection, these data will be received by the virtual space 
-    and updates the states of the models. Virtual space sends the needed information to the physical space.
-
-    There is also another, an up-to-date approach that adds two more dimensions(Data and Services), to the traditional digital twin model which is described above.~\cite{DTGRIEVES}
-
-    \begin{equation}
-        M_{dt} = (PE,VE,Ss,DD,CN)
-    \end{equation}
-
-    \begin{description}
-        \item[PE] Represents DT Physical Entity
-        \item[VE] Represents DT Virtual Entity
-        \item[Ss] Represents DT Services
-        \item[DD] Represents DT Data
-        \item[CN] Represents DT Connections
-    \end{description}
-    If we consider the dimensions we above discussed as vertical dimensions, if we divide our digital twin horizontally into three different layers, the explanation of the digital twin systems becomes much clearer.
-    \begin{itemize}
-        \item Unit DT which only has one PE in the physical space
-        \item System DT  is an assembly of PE's in the physical space
-        \item System of Systems DT  is an assembly of systems in the physical space
-    \end{itemize}
-
-    Of course, there are other explanations, approaches, and architectures to digital twins, but like every other digital transformation approach, the main goal is to get into the lean state,
-    which is an optimal approach to our problem.
-
-    Also should be noted that the digital twin approach was introduced within the PLM course.
-PLM is nothing but an improvement to the lean manufacturing philosophy, which aims to eliminate waste(Time, energy, Material) not only during the
-    manufacturing process but also during the lifecycle of the product.~\cite{grieves2006PLM} 
-    It's an approach to achieve the lean state, which overlaps with the idea of digital twins, which both aim to gather more information about the product, starting from the design phase to the disposal of the product.
-
-    Achieving a full-scale cyber-physical system is not only a goal for the digital twin but also an essential challenge.
-The following are some examples of the challenges which is occurring during the development of a digital twin:
-    \begin{itemize}
-        \item High fidelity modeling and simulation
-        \item Real-Time communication between the components of digital twin 
-        \item Flexible data architecture
-        \item Developing standards and protocols for the use of digital twins so that they can be used consistently across different industries and applications.
-        \item Cost and Cost Management
-        \item Cyber Security
-        \item Quality Assurance of the digital twin
-        \item Information inefficiency regarding the theme Digital Twins
-        \item \dots{}
-    \end{itemize}
-
-    %TODO: How we are writing this?
     \subsection{Research objectives}
 
-    Find an approach to assess the quality of Digital twins
+    Find approach for assessing the quality of digital twins...
 
     \subsection{Research questions}
-    \label{section:Research Questions}
 
-    What is the quality of digital twins? 
+    What is a digital twin?
+What is quality of digital twins?
 What is good quality?
 What is bad quality?
-    What is the impact of good quality? 
-    What is impact of bad quality? W
+What is impact of good quality?
+What is impact of bad quality?
 What are typical quality issues?
 How to assess quality?
+...
 
@@
 
-    Literature review (see Section~\ref{section:literature}), case study (see Section~\ref{section:Research Questions})...
+    Literature review (see Section~\ref{section:literature}), case study (see Section~\ref{section:case})...
 
@@
     \label{section:literature}
-    Literature analysis was executed, to analyze current DT literature within the concept of digital twin quality. The analysis, especially focused on 
-    how the digital twin quality is mentioned and assessed within the academic dissertations.
 
     Methodology (see Section~\ref{section:liteature_methodology}), result (see Section~\ref{section:liteature_result}), and summary (See Section~\ref{section:liteature_summary})...
+
     \subsection{Methodology}
@@
 
-    Google Scholar(GS), Scopus(SCP) and Research Rabbit(RR) tools are used to fulfill our requirements for the literature review. 
-    Since there is a great number of digital twin publications in academics, narrowing the research is necessary, so the following filtering has been done for all searches.
+    How did we find existing literature?
+
     \begin{itemize}
-        \item Dissertations should be written in English and published in a journal.
-        \item Paper is not older than 2018
+        \item ("digital twin" OR "simulation model" OR "system model" OR "CAD model") AND (quality OR defect OR issue OR error)
+        \item ("digital twin" OR "simulation model" OR "system model" OR "CAD model") AND (verification OR validation OR accreditation)
     \end{itemize}
-
-    Search terms appeared in the title/abstract with "digital twin quality";
-    \begin{itemize}
-        \item GS = allintitle: "digital twin quality" Return articles dated between 2018 - NOW  
-        \item Scopus = TITLE-ABS-KEY ( "digital twin quality" )  AND  PUBYEAR  \textgreater  2018  AND  PUBYEAR  \textless  2023  AND  ( LIMIT-TO ( LANGUAGE ,  "English" ) ) 
-    \end{itemize}
-
-    GS gave five different results, while SCP gave 2 results.
-
-    Further inspection has been done, and
 
@@
 
-    What is the existing literature?
+    What is existing literature?
 
@@
 
+    \section{Digital twin framework}
+    \label{section:framework_1}
+
+    TODO
+
+    \subsection{Real system}
+
+    TODO
+
+    \subsubsection{Real state (RS)}
+
+    TODO
+
+    \subsubsection{Real state history (RSH)}
+
+    TODO
+
+    \[
+        RSH: \mathbb{R} \rightarrow RS
+    \]
+
+    \subsubsection{Real state transition function (RSTF)}
+
+    TODO
+
+    \[
+        RSTF: RS \rightarrow RS
+    \]
+
+    \subsubsection{Real state prediction (RSP)}
+
+    TODO
+
+    \subsection{Digital twin}
+
+    TODO
+
+    \subsubsection{Digital state (DS)}
+
+    TODO
+
+    \subsubsection{Digital state history (DSH)}
+
+    In our digital world we cannot represent the continuous time domain of the real system completely.
+    Instead, we have to discretize the time domain and sample the state history function.
+
+    \[
+        RSH: \mathbb{N} \rightarrow RS
+    \]
+
+    \subsubsection{Digital state transition function (DSTF)}
+
+    Since we do not have perfect knowledge about real state and real state transition function, our simulation models typically are non-deterministic or probabilistic.
+    Here we take a probabilistic viewpoint.
+
+    \[
+        DSRF: DS \rightarrow \mathbb{P}(DS)
+    \]
+
+    \subsubsection{Digital state prediction (DSP)}
+
+    TODO
+
+    \section{Digital twin quality framework}
+    \label{section:framework_2}
+
+    TODO
+
     \section{Case study (FELICE)}
@@
 
-    TODO (Explain the limitations of the FELICE digital twin! It is not a complete digital twin according to literature! It includes this, it is missing this.)
+    TODO (Explain limitations of the FELICE digital twin! It is not a complete digital twin according to literature! It includes this, it is missing this.)
 

### 2023-01-17 manuscripts/paper-1/main.tex

--- 2022-12-14 manuscripts/paper-1/main.tex
@@
 \documentclass[9pt,conference]{IEEEtran}
+
+\usepackage[colorlinks,allcolors=blue]{hyperref}
 \usepackage{listings}
 \usepackage{graphicx}
-\usepackage[colorlinks,allcolors=blue]{hyperref}
+\usepackage{amsfonts}
 \graphicspath{{./images/}}
@@
     \section{Introduction}\label{section:introduction}
-
     Cyber-physical system (CPS), is a conceptual architecture/approach which aims to conjoin the physical and virtual space tightly. 
@@
     \subsection{Research objectives}
-
     Find an approach to assess the quality of Digital twins
 
-    \subsection{Research questions}~\label{section: Research Questions}
-
+    \subsection{Research questions}
+    \label{section: Research Questions}
+    What is a digital twin?
     What is the quality of digital twins? 
@@
     \subsection{Scientific contributions}
-
     Literature review (see Section~\ref{section: literature}), case study (see Section~\ref{section: Research Questions})...
 
-    \section{Literature review}~\label{section: literature}
+    \section{Literature review}
+    \label{section: literature}
     Literature analysis was executed, to analyze current DT literature within the concept of digital twin quality. The analysis especially focused on 
@@
     Methodology (see Section~\ref{section:liteature_methodology}), Result (see Section~\ref{section:liteature_result}), and Summary (See Section~\ref{section:liteature_summary})...
-    \subsection{Methodology}~\label{section:liteature_methodology}
+
+    \subsection{Methodology}
+    \label{section:liteature_methodology}
     Google Scholar (GS), Scopus (SCP) and Research Rabbit (RR) tools are used to fulfill our requirements for the literature review. 
@@
     still some results without the English language will appear. Again, language filtering should be done to clean the results.
-
     \begin{itemize}
@@
 
-    \subsection{Result}~\label{section:liteature_result}
+    \subsection{Result}
+    \label{section:liteature_result}
     The following results were achieved by selecting several search terms.
-    \subsubsection*{Digital Twin Quality}\label{subsection:DigitalTwinQuality}
 
+    \subsubsection*{Digital Twin Quality}
+    \label{subsection:DigitalTwinQuality}
     First filtering was done for the search term "digital twin quality", meanwhile GS gave 41 different results, and SCP gave only 3 results.
@@
 
-    \subsubsection*{Digital Twin Model Verification}\label{subsection:DigitalTwinVerification}
+    \subsubsection*{Digital Twin Model Verification}
+    \label{subsection:DigitalTwinVerification}
 
-    \subsubsection*{Digital Twin Model Validation}\label{subsection:DigitalTwinValidation}
+    \subsubsection*{Digital Twin Model Validation}
+    \label{subsection:DigitalTwinValidation}
     %What is the existing literature?
@@
     \subsection{Summary}~\label{section:liteature_summary}
-
     What do we learn from existing literature?
@@
 
-    \section{Case study (FELICE)}~\label{section:case}
+    \section{Digital twin framework}
+    \label{section:framework_1}
+    TODO
 
+    \begin{figure}[htbp]
+        \includegraphics[width=\columnwidth]{Digital Twin.png}
+        \caption{TODO}
+        \label{todo}
+    \end{figure}
+
+    \begin{figure}[htbp]
+        \includegraphics[width=\columnwidth]{Digital Twin Deviation.png}
+        \caption{TODO}
+        \label{todo}
+    \end{figure}
+
+    \begin{figure}[htbp]
+        \includegraphics[width=\columnwidth]{Continuous Quality Control.png}
+        \caption{TODO}
+        \label{todo}
+    \end{figure}
+
+    \subsection{Real system}
+    TODO
+
+    \subsubsection{Real state (RS)}
+    TODO
+
+    \subsubsection{Real state history (RSH)}
+    TODO
+    \[
+        RSH: \mathbb{R} \rightarrow RS
+    \]
+
+    \subsubsection{Real state transition function (RSTF)}
+    TODO
+    \[
+        RSTF: RS \rightarrow RS
+    \]
+
+    \subsubsection{Real state prediction (RSP)}
+    TODO
+
+    \subsection{Digital twin}
+    TODO
+
+    \subsubsection{Digital state (DS)}
+    TODO
+
+    \subsubsection{Digital state history (DSH)}
+    In our digital world we cannot represent the continuous time domain of the real system completely.
+    Instead, we have to discretize the time domain and sample the state history function.
+    \[
+        RSH: \mathbb{N} \rightarrow RS
+    \]
+
+    \subsubsection{Digital state transition function (DSTF)}
+    Since we do not have perfect knowledge about real state and real state transition function, our simulation models typically are non-deterministic or probabilistic.
+    Here we take a probabilistic viewpoint.
+    \[
+        DSRF: DS \rightarrow \mathbb{P}(DS)
+    \]
+
+    \subsubsection{Digital state prediction (DSP)}
+    TODO
+
+    \section{Digital twin quality framework}
+    \label{section:framework_2}
+    TODO
+
+    \section{Case study (FELICE)}
+    \label{section:case}
     TODO (Explain the limitations of the FELICE digital twin! It is not a complete digital twin according to literature! It includes this, it is missing this.)
@@
     \subsection{Methodology}~\label{section:case_methodology}
-
     TODO
@@
     \subsection{Result}~\label{section:case_result}
-
     TODO
@@
     \subsection{Summary}~\label{section:case_summary}
-
     TODO

### 2023-01-17 manuscripts/paper-1/main.tex
remove obsolete content and improve formatting

@@
 
-    \section{Digital twin framework}
+    \section{Our framework}
     \label{section:framework_1}
@@
         \caption{TODO}
-        \label{todo}
+        \label{todo-1}
     \end{figure}
@@
         \caption{TODO}
-        \label{todo}
+        \label{todo-2}
     \end{figure}
@@
         \caption{TODO}
-        \label{todo}
+        \label{todo-3}
     \end{figure}
-
-    \subsection{Real system}
-    TODO
-
-    \subsubsection{Real state (RS)}
-    TODO
-
-    \subsubsection{Real state history (RSH)}
-    TODO
-    \[
-        RSH: \mathbb{R} \rightarrow RS
-    \]
-
-    \subsubsection{Real state transition function (RSTF)}
-    TODO
-    \[
-        RSTF: RS \rightarrow RS
-    \]
-
-    \subsubsection{Real state prediction (RSP)}
-    TODO
-
-    \subsection{Digital twin}
-    TODO
-
-    \subsubsection{Digital state (DS)}
-    TODO
-
-    \subsubsection{Digital state history (DSH)}
-    In our digital world we cannot represent the continuous time domain of the real system completely.
-    Instead, we have to discretize the time domain and sample the state history function.
-    \[
-        RSH: \mathbb{N} \rightarrow RS
-    \]
-
-    \subsubsection{Digital state transition function (DSTF)}
-    Since we do not have perfect knowledge about real state and real state transition function, our simulation models typically are non-deterministic or probabilistic.
-    Here we take a probabilistic viewpoint.
-    \[
-        DSRF: DS \rightarrow \mathbb{P}(DS)
-    \]
-
-    \subsubsection{Digital state prediction (DSP)}
-    TODO
-
-    \section{Digital twin quality framework}
-    \label{section:framework_2}
-    TODO
 

### 2023-01-24 manuscripts/paper-1/main.tex
Update

@@
 \documentclass[9pt,conference]{IEEEtran}
-
 \usepackage[colorlinks,allcolors=blue]{hyperref}
@@
     \section{Introduction}\label{section:introduction}
-    Cyber-physical system (CPS), is a conceptual architecture/approach which aims to conjoin the physical and virtual space tightly. 
-    The CPS aims to integrate communication and computing capabilities to physical entities to monitor, coordinate and control the physical space (where the physical assets exist) from the virtual space (where the virtual models exist) while achieving seamless, real-time connection between the spaces.
-    The Digital twin approach, on the other hand, is a pragmatic solution, which is the execution of the CPS idea.~\cite{TAOCHAPTER1}
+    A popular but highly misunderstood notion with fuzzy boundaries is the `digital twin.' 
+    The misunderstanding began with the Apollo 13 mission, which many authors claim, had a first digital twin The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilized in the physical simulations.
+Even though the `digital' aspect was expected to be present,
+    it wasn't.  The historic D-day map (also known as the Big Board) in Southwick House England, which was used simultaneously before and during operation, can be argued to be similar. 
+    The board was a twin of the operation, and it included models of battalions and ships that reflected the actual locations of the corresponding formations. 
+    Furthermore, synchronization was implemented with radio communication to give directives from the real system to control the operation flow and also to update the twin's state.
 
-    The first occurrence of the "Digital Twin" term was introduced by Dr.~Michael Grieves in 2003 at the University of Michigan while giving the Product Lifecycle Management (PLM) course.~\cite{DTGRIEVES}
-    His introduction to the term was rather raw but still introduced a pragmatic solution to gather more data from the physical entities, to achieve the "Lean" state.
+    To begin analyzing `digital' twins and their components, authors needed to come up with a concrete description that involved a great level of abstraction. 
+    The definition of a digital twin given by the digital twin consortium, according to the authors, is the best one currently available: `A digital twin is a virtual representation of real-world entities and processes, synchronized at a specified frequency and fidelity.'.
+    What makes that definition the best?
+Because it provides the highest abstraction level among the definitions of digital twins that we discovered during our literature analysis.
+The following is a poor example of abstraction taken from the initial definition of a digital twin from NASA's roadmap from 2010: `A digital twin is an integrated multi-physics, multi-scale, probabilistic simulation of a
+    vehicle or system that uses the best available physical models, sensor updates, fleet history, etc., to mirror the life of its flying twin.'
+    The digital twins that we encounter nowadays don't typically fall under NASA's definition.
+We want to stress that NASA's definition of a  digital twin is accurate since, as we will see, digital twins are systems that are `context' centered.
+    This definition, therefore, is appropriate in the context of NASA's use case and is thus accurate, but the abstraction level is not sufficiently high to allow for a thorough understanding of digital twins.
 
-    His approach has three dimensions, along with a physical entity, a virtual entity and a connection between these entities which constructed the main frame for today's evaluating digital twins.~\cite{DTGRIEVES}
+    In addition, we would want to emphasize the significance of Grieves' 2006 description of digital twins in the PLM book, which traces the origins of the concept.
+Although it featured the same components as a digital twin at the time, it was known as an Information Mirroring Model (IM).
+They decided to use NASA's Digital Twin rather than IM after co-authoring the article with  Vickers.
+    We presented a definition of digital twins(consortium one) that we agreed on, but we haven't reached an agreement yet.
+We must therefore analyze the digital twins to comprehend what a digital twin is.
+We may probably all agree that the line delineating the chosen definition of the digital twin is blurry enough that we cannot easily perceive it.
+Starting with Grieves' perspective, we'll move forward from there.
+Concurrently, the definition of the consortium will show us the route.
 
-    A physical entity exists only in the physical space with real functionalities and performance. It is responsible to accomplish certain tasks within the physical space, to give certain outputs.
-    Different levels of abstraction can be usable for a physical entity such as an electric motor in the 1/10 of an RC Car, bearings in a certain machine, solar panels above some construction, human or an entire world can be counted as an example of a physical entity.
+    \subsection{Grieves Information Mirroring Model}
 
-    On the other hand, a virtual entity exists only in the virtual space, which should imitate the physical entity with high-fidelity models. If we consider the virtual entity as a function;
+    His conceptual model is an ideal Product Lifecycle Management (PLM), has just one important goal which is to gather as much information about the actual space as feasible to minimize the waste of energy, time, and materials.
+    It is composed primarily of four parts. Real or physical space, virtual space, connections between real and virtual space, and virtual simulations.
 
-    \begin{equation}\label{Formulated Entity Equation}
-        VE = (G_v, P_v, B_v, R_v)
-    \end{equation}
-    where:
+    As we can see, it shares almost all of the same components as the digital twins of today.
+Virtual simulation is an optional component that Grieves subsequently removed to simplify the model.
+[GrievesEliminateForthElement]
+    The simple model version is indicated by the fact that only the first three (Physical System, Virtual System, and Connection Between Them) will be taken into account. 
+    It should be mentioned that we shall define these three components in our own words using previous definitions of each component.  Additionally, by using the consortium's definition, we are simply improving the grieves IM model as a reference.
+    The physical space is where we start first.
 
-    $G_v$ represents the geometry model, $P_v$ represents the physical model, $B_v$ represents  the behavior model, and $R_v$ represents the rule model~\cite{DTGRIEVES}.
+    \begin{figure}[htbp]
+        \includegraphics[width=\columnwidth]{Grieves Information Mirroring Model.png}
+        \caption{Information Mirroring Model}
+        \label{IM}
+    \end{figure}
 
-    The last dimension of a 3D-DT is the connection between physical space and virtual space.
-Physical space creates real-time data, and through the connection, these data will be received by the virtual space
-    and updates the states of the models. Virtual space sends the needed information to the physical space.
+    \subsection{Real System}
+    We shall refer to a real system instead of calling it a real space. 
+    Why? Because everything is an open system according to the system theory, 
+    with the upper bound of the universe and lower bound as subatomic particles.
+    As a result, the universe and subatomic particles can be viewed as closed systems, 
+    simplifying definitions and facilitating the analysis of entities as systems. 
+    In the literature, we see most of the time a notion called " entity" and sometimes an "artifact". 
+    For instance, the digital twin framework developed by (TAO et al.) has both a physical and virtual entity.
+    An entity is any separate and independent system, whether it be real or abstract.
+    On the other hand, an artifact is a thing that humans have created or constructed. 
+    Therefore, when we speak of entities, we really mean systems. 
+    And when we discuss artifacts, we are still discussing physical systems but with the caveat of human interaction. 
+    Automobiles, engines, software, artwork, food, and telephones are a few examples of artifacts.
 
-    There is also another, an up-to-date approach that adds two more dimensions (Data and Services), to the traditional digital twin model which is described above.~\cite{DTGRIEVES}
+    Above, we established the term "entity," but what about the physical connection of an entity? 
+    Because an entity could be a physical system or an abstract system. 
+    We won't go into further depth about these two distinct ideas, but just so you know, 
+    when we talk about physical systems, we do not include abstract systems that require a
+    media to exist, such as ideas, texts, diagrams, and mathematics, which are nothing more than abstractions.
 
-    \begin{equation}
-        M_{dt} = (PE,VE,Ss,DD,CN)
-    \end{equation}
+    The term "real system" in the context of digital twins refers to a system that is a tangible thing and also has 
+    the characteristics of a system. The usage of various artifacts by Grieves in a system he referred to as `real space' 
+    can be seen in figure X. 
+    For convenience, we'll refer to this system as a "real system" or, as Mobus prefers to say, a `system of interest.'. 
+    Instead of using black-and-white images, we instead created subsystems out of circles, each of which represented an artifact. 
+    It is clear to see that every subsystem (artifact) includes smaller subsystems as well. 
+    Once more using Grieves' example, an automobile(an element of the real space according to figure 1), 
+    which is an artifact, that includes several parts, including a radio, a motor, wheels, etc. 
+    Additionally, these subsystems (artifacts) can be further broken down into even smaller subsystems, 
+    down to subatomic particles, which, as we mentioned above, is the lowest we can go in terms of the system theory. 
+    But the question is, should we break things down to the level of subatomic particles to comprehend the system? Considering digital twins, 
+    the answer is a resounding no.
 
-    \begin{description}
-        \item[PE] Represents DT Physical Entity
-        \item[VE] Represents DT Virtual Entity
-        \item[Ss] Represents DT Services
-        \item[DD] Represents DT Data
-        \item[CN] Represents DT Connections
-    \end{description}
-    If we consider the dimensions, we discussed above as vertical dimensions within a single layer, the digital twins also can have three different horizontal layers\cite{TAOCHAPTER1}. 
-    The need for such layers is that the explanation of the digital twin systems becomes much clearer. These can be identified as:
-    \begin{itemize}
-        \item Unit DT has one PE in the physical space
-        \item System DT is an assembly of PE's in the physical space
-        \item System of Systems DT is an assembly of systems in the physical space
-    \end{itemize}
+    Consequently, why bother to define these terms? Because the granularity of the digital twin is determined by the complexity of the real system. 
+    In the end, a System of Interest is what we'll be twinning! Of course, the system of interest is not as simple to define as in figure X. 
+    One crucial component and stage of the digital twin is to comprehend how the real system, or more precisely the system of interest, 
+    actually functions. How can one know what to twin if it is not well understood?
+    The system of interest can be analyzed in three different ways. If we don't have the opportunity to examine the inner workings of the system, 
+    we can use the black boxing technique, which focuses primarily on the mathematical (and frequently statistical) 
+    relationships between inputs and outputs. This method doesn't provide insight into the inner workings of the system, but it still provides 
+    a basic grasp of how a system operates. If the system exhibits linear behavior, it works great.
 
-    There is also the possibility to add more horizontal layers and define them differently such as a Part layer, Component layer, Machine layer, Production line layer, Shop-floor Layer.\cite{MultiScaleModeling4Layers}
+    The second method, known as the gray box method, examines the inner workings of comparable systems that should be `like' 
+    the system of interest to understand how the inner workings of a similar system react when various inputs are applied and the results of the system are monitored. 
+    This method is used for the majority of biological work, such as the experiments medical students conduct on cadavers to learn how the human body functions.
 
-    Of course, there are other explanations, approaches, and architectures to digital twins, but like every other digital transformation approach, the main goal is to get into the lean state,
-    which regards the optimal approach to any problem.
+    The final method, known as the `white box method,' is better than the others since it examines every system's component. 
+    The interesting thing to realize is that the system's integrity(Objectiveness) shouldn't be impaired.
+    What objectiveness means is that while the system functions as a whole, we should also study the relationships 
+    between the subsystems in addition to the subsystems themselves. 
+    Observing our galaxy is a fantastic example. Telescopes allow us to individually assess the condition of the subsystems (planets, solar systems) 
+    without affecting the overall system.
 
-    Also should be noted that the digital twin approach was introduced within the PLM course. PLM is nothing but an improvement to the lean manufacturing philosophy,
-    which aims to eliminate waste (Time, Energy and Material waste) not only during the
-    manufacturing process but also during the lifecycle of the product.~\cite{grieves2006PLM} 
-    It's an approach to achieve the lean state, which overlaps with the idea of digital twins.
-Both aim to gather more information about the product, starting from the design phase to the disposal of the product.
+    Physical space, as a whole, is a physical system (which we refer to as the system of interest),
+    with subsystems and linkages between them. Depending on the SOI's context, we can use black box, gray box, or white box methodologies to study the system.
+    In addition, I wish to draw attention to the fact that the SOI's details are not fully depicted in figure 2. 
+    For additional details on the system theory, we strongly advise reading `von Bertalanffy 2003'.
 
-    Achieving a full-scale cyber-physical system is not only a goal for the digital twin but also an essential challenge.
-The following are some examples of the challenges which is occurring during the development of a digital twin:
-    \begin{itemize}
-        \item High fidelity modeling and simulation
-        \item Real-Time communication between the components of digital twin 
-        \item Flexible data architecture
-        \item Developing standards and protocols for the use of digital twins so that they can be used consistently across different 
-        industries and applications
-        \item Cost and Cost Management
-        \item Cyber Security
-        \item Quality Assurance of the digital twin
-        \item Information inefficiency
-        \item \dots{}
-    \end{itemize}
+    \begin{figure}[htbp]
+        \includegraphics[width=\columnwidth]{SOI.png}
+        \caption{System Of Interest}
+        \label{SOI}
+    \end{figure}
 
-    %TODO: How we are writing this?
+    \subsection{Virtual System(Digital Twin)}
+
+    First of all, what does the term `virtual' mean? Virtual refers to an existence (or entity?) that exists in a computer system as opposed to a physical system. 
+    Therefore, we made sure to note that we are not speaking of abstract systems when we described physical systems. 
+    We also discussed the distinction between an entity and an artifact. The term `abstract systems'  refers to systems that have had their set of variables and functions 
+    `abstracted'  so that they may be computed by a solver, which in this case could be either the human brain or a computer.
+    Additionally, just because a system is abstract doesn't mean it lacks a physical body; rather, as we previously established, 
+    it is abstracted. Computers, symbolic language, and the human mind all can contain these abstract systems.
+    Symbolic text in this sense covers not only text on the sheet but also mathematical symbols, logic, etc.
+
+    Virtual systems can't exist on their own since, like abstract systems, they require a medium to exist.
+    Computer systems, a higher system of virtual systems, are an ideal medium for virtual systems.
+
+    \begin{figure}[htbp]
+        \includegraphics[width=\columnwidth]{DT SOI.png}
+        \caption{Digital Twin SOI}
+        \label{DTSOI}
+    \end{figure}
+
+    Recall that Grieves referred to the virtual system as a virtual space in figure 1. 
+    We refer to it as a virtual system because it can only exist inside a computer system. 
+    Additionally, we refer to the entities he depicted in the virtual space as virtual subsystems rather than the virtual entities he used. In figure 3, 
+    we were creative and wrote `digital twin'  rather than `virtual system.'  Where does this digital twin emerge from?
+
+    We must first understand what digital implies to comprehend the concept of a digital twin.  
+    The term `digital has been in use since the late 14th century and is derived from the Latin word `digitus, ' 
+    which means `finger'  or `toe.'. It gained popularity after digitalization in the 20th century and refers to the use of discrete digits to represent data. 
+    Digital images, for instance, are represented by a matrix of pixels, which are nothing more than 8-bit integer values between 0 and 255 which represent the intensity 
+    of the pixel. 
+    We will therefore have digital models if we can digitally model our models. 
+    Therefore, we will have digital models if we can digitally model our models. Where are these digital models being created? Throughout the digital system! 
+    This system is referred to as a `digital twin'  since it is a digital twin of the SOI that is represented in the computer system.
+
+    The reader will quickly and easily comprehend that a computer system may have several digital twins, 
+    and that these systems may also be connected in some way, 
+    creating yet another system that is also referred to as a digital twin. 
+    Another immediate realization is that perhaps we won't have our SOI yet, 
+    so how can we twin something that doesn't exist? Although the term we preferred was the best definition (for us), 
+    it does not directly address the second question. In reality, most of the time, 
+    the physical product will not be ready or not present to make a digital twin out of it. 
+    But if we could have some data about the physical system, for example how it should look, 
+    how much weight it should have, approximate dimensions and so on,  we can start constructing our system abstractly, 
+    within the computer systems, with diagrams, or with using symbolic language. 
+    But the important point is that everyone, who works on this abstract system should have a singular reference so that it can be constructed. Also after the construction, 
+    still a real system is needed to validate and verify. Most frequently, this viewpoint is referred to as a prototype digital twin. And if the SOI is present its called instance digital twin.
+
+    So far, we inspected the real system (system of interest), and virtual system. 
+    As we talked about above, there is a third part which is a connection between the real system and the virtual system, which we will explain next.
+
+    \subsection{Connection Between the Systems}
+
+    \subsection{Possibility of States}
+    \subsection{Context of Digital Twin}
+    \subsection{Quality of Digital Twin}
+
     \subsection{Research objectives}
@@
         \item Google Scholar = "search term"
-        \item Scopus = ALL ( "digital twin quality" ) AND PUBYEAR > 2018 AND PUBYEAR < 2023 AND ( LIMIT-TO ( LANGUAGE , "English" )) 
+        \item Scopus = ALL ( "digital twin quality" ) AND PUBYEAR > 2018 AND PUBYEAR < 2023 AND ( LIMIT-TO (LANGUAGE , "English" )) 
     \end{itemize}
@@
 
-    He Zhang et al.introduced a consistency evaluation method for digital twin models, which can be used to assess the quality of the digital twin~\cite{ConsistencyEvolutionMethodForDigitalTwins}.
+    He Zhang et al.introduced a consistency evaluation method for digital twin models, which can be used to assess the quality of the digital twin ~\cite{Jones2020}.
     (Existing literature does at most partially solve our problem!)

### 2023-01-24 manuscripts/paper-1/main.tex
work on paper structure; comment out some parts

@@
 \documentclass[9pt,conference]{IEEEtran}
+
 \usepackage[colorlinks,allcolors=blue]{hyperref}
@@
 \usepackage{amsfonts}
+\usepackage{verbatim}
 \graphicspath{{./images/}}
@@
 
+    \subsection{Research objective}
+    Find an approach to assess the quality of Digital twins~\cite{Jones2020}
+
+    \subsection{Research question}\label{section: Research Questions}
+    What is quality of digital twins?
+
+    \subsection{Research methodology}
+    TODO
+
+    \section{State of the art on quality}
+    TODO
+
+    \subsection{Product quality}
+    Most generic (e.g.~House of quality, ...)
+
+    \subsection{Software quality}
+    Medium (e.g.~ISO/IEC 9126 and ISO 25010, ...)
+
+    \subsection{Digital twin quality}
+    Most specific (a bit more research here!)
+
+    \section{Initial approach in the FELICE project}
+    Inspired by ISO 25010...
+
+    \subsection{First criterion: Correctness}
+
+    \subsubsection{Definition}
+    Car vs airplane (with nice pictures!)
+
+    \subsubsection{Motivation}
+    TODO
+
+    \subsubsection{Findings from FELICE}
+    TODO
+
+    \subsection{Second criterion: Completeness}
+
+    \subsubsection{Definition}
+    Car vs engine (with nice pictures!)
+
+    \subsubsection{Motivation}
+    TODO
+
+    \subsubsection{Findings from FELICE}
+    TODO
+
+    \subsection{Third criterion: Fidelity}
+
+    \subsubsection{Definition}
+    Linear vs differential (with nice pictures!)
+
+    \subsubsection{Motivation}
+    TODO
+
+    \subsubsection{Findings from FELICE}
+    TODO
+
+    \subsection{Fourth criterion: Efficiency}
+
+    \subsubsection{Definition}
+    1ms vs 1min (with nice pictures!)
+
+    \subsubsection{Motivation}
+    TODO
+
+    \subsubsection{Findings from FELICE}
+    TODO
+
+    \subsection{Fifth criterion: Evolvability}
+
+    \subsubsection{Definition}
+    Effort to adapt the digital twin to new circumstances (e.g.\ add new machine, replace machine, etc.)
+
+    \subsubsection{Motivation}
+    TODO
+
+    \subsubsection{Findings from FELICE}
+    TODO
+
+    \begin{comment}
+        \section{Whatever}
+
         \subsection{Grieves Information Mirroring Model}
+
+        \subsubsection{How it is defined?}
 
@@
         \end{figure}
+
+        \subsubsection{Why it is problematic?}
+
+        TODO
 
@@
         \subsection{Quality of Digital Twin}
+    \end{comment}
 
-    \subsection{Research objectives}
-    Find an approach to assess the quality of Digital twins
-
-    \subsection{Research questions}
-    \label{section: Research Questions}
-    What is a digital twin?
-    What is the quality of digital twins? 
-    What is good quality?
-    What is bad quality? 
-    What is the impact of good quality? 
-    What is the impact of bad quality? W
-    What are typical quality issues? 
-    How to assess quality?
-
-    \subsection{Scientific contributions}
-    Literature review (see Section~\ref{section: literature}), case study (see Section~\ref{section: Research Questions})...
-
+    \begin{comment}
         \section{Literature review}
@@
         (Existing literature does at most partially solve our problem!)
+    \end{comment}
 
-    \section{Our framework}
+    \section{Future approach in the FELICE project}
     \label{section:framework_1}
     TODO
+
+    \begin{figure}[htbp]
+        \includegraphics[width=\columnwidth]{Digital Twin Deviation.png}
+        \caption{TODO}
+        \label{todo-2}
+    \end{figure}
 
@@
     \begin{figure}[htbp]
-        \includegraphics[width=\columnwidth]{Digital Twin Deviation.png}
-        \caption{TODO}
-        \label{todo-2}
-    \end{figure}
-
-    \begin{figure}[htbp]
         \includegraphics[width=\columnwidth]{Continuous Quality Control.png}
@@
 
-    \section{Case study (FELICE)}
-    \label{section:case}
+    \begin{comment}
+        \section{Case study (FELICE)}\label{section:case}
         TODO (Explain the limitations of the FELICE digital twin! It is not a complete digital twin according to literature! It includes this, it is missing this.)
@@
         TODO
+    \end{comment}
 

### 2023-02-05 manuscripts/paper-1/main.tex
Introduction Finished

@@
 Even though the `digital' aspect was expected to be present,
-    it wasn't. The historic D-day map (also known as the Big Board) in Southwick House England, which was used simultaneously before and during operation, can be argued to be similar. 
+    it wasn't~\cite{GrievesApollo13}.
+The historic D-day map (also known as the Big Board) in Southwick House England, which was used simultaneously before and during operation, can be argued to be similar.
     The board was a twin of the operation, and it included models of battalions and ships that reflected the actual locations of the corresponding formations. 
-    Furthermore, synchronization was implemented with radio communication to give directives from the real system to control the operation flow and also to update the twin's state.
+    Furthermore, synchronization was implemented with radio communication to give directives from the real system to control the operation flow and also to update the twin's state~\cite{AMRC}.
 
-    To begin analyzing `digital' twins and their components, authors needed to come up with a concrete description that involved a great level of abstraction. 
-    The definition of a digital twin given by the digital twin consortium, according to the authors, is the best one currently available: `A digital twin is a virtual representation of real-world entities and processes, synchronized at a specified frequency and fidelity.'.
+    To begin analyzing `the digital twin' and its quality, authors needed to come up with a concrete description that involved a great level of abstraction. 
+    The definition of a digital twin given by the digital twin consortium, according to the authors, is the best one currently available: `A digital twin is a virtual representation of real-world entities and processes, synchronized at
+    a specified frequency and fidelity.'~\cite{digitaltwinconsortium2022}.
+
     What makes that definition the best?
@@
 The following is a poor example of abstraction taken from the initial definition of a digital twin from NASA's roadmap from 2010: `A digital twin is an integrated multi-physics, multi-scale, probabilistic simulation of a
-    vehicle or system that uses the best available physical models, sensor updates, fleet history, etc., to mirror the life of its flying twin.'
+    vehicle or system that uses the best available physical models, sensor updates, fleet history, etc., to mirror the life of its flying twin~\cite{NASA}.'
     The digital twins that we encounter nowadays don't typically fall under NASA's definition.
-We want to stress that NASA's definition of a  digital twin is accurate since, as we will see, digital twins are systems that are `context' centered.
+We want to stress that NASA's definition of a  digital twin is accurate since digital twins are systems that are `context' centered.
     This definition, therefore, is appropriate in the context of NASA's use case and is thus accurate, but the abstraction level is not sufficiently high to allow for a thorough understanding of digital twins.
 
-    In addition, we would want to emphasize the significance of Grieves' 2006 description of digital twins in the PLM book, which traces the origins of the concept.
-Although it featured the same components as a digital twin at the time, it was known as an Information Mirroring Model (IM).
+    In addition, we would want to emphasize the significance of Grieves' 2006 description of digital twins in the PLM book,
+    which traces the origins of the concept. Although it featured the same components as a digital twin at the time, it was known as an Information Mirroring Model (IM)~\cite{GrievesPLMBook}. 
     They decided to use NASA's Digital Twin rather than IM after co-authoring the article with Vickers.
-    We presented a definition of digital twins(consortium one) that we agreed on, but we haven't reached an agreement yet.
-We must therefore analyze the digital twins to comprehend what a digital twin is.
-We may probably all agree that the line delineating the chosen definition of the digital twin is blurry enough that we cannot easily perceive it.
-Starting with Grieves' perspective, we'll move forward from there.
-Concurrently, the definition of the consortium will show us the route.
 
+    \begin{figure}
+        \centering
+        \includegraphics[width =0.45\textwidth]{GrievesInformationMirroringModel.png}
+        \caption{Grieves Information Mirroring Model}
+        \label{fig:GrievesInformationMirroringModel}
+        \cite{GrievesPLMBook}
+    \end{figure}
+
+    \subsection*{Real System}
+
+    The term `real system' in the context of digital twins refers to a system that is a tangible thing that has the characteristics of a system.
+Depending on the system's context, we can use black-box, gray-box, or white-box methodologies to study the system.
+    The usage of various artifacts by Grieves in a system he referred to as `real space' can be seen in Figure~\ref{fig:GrievesInformationMirroringModel}.
+
+    \subsection*{Virtual System}
+    Virtual refers to an existence that exists in a computer system as opposed to a physical system.
+Therefore, virtual systems are abstract systems, which are nothing but an abstraction of the real system.
+    The term `abstract systems' refers to systems that have had their set of variables and functions `abstracted' so that they may be computed by a solver, which in this case solver could be either the human brain or a computer.
+    Additionally, just because a system is an abstract system doesn't mean it lacks a physical body; rather, it is abstracted. 
+    Virtual systems can't exist on their own since, like abstract systems, they require a medium to exist.
+Computer systems, a higher system of virtual systems, are an ideal medium for virtual systems.
+
+    \subsection*{Connection Between the Real and Virtual System}
+    If we step back and observe the consortium's definition in~\ref{section:introduction}, which we told is the best definition we could find, 
+    it talks about synchronization, fidelity and some specified frequency. As can be guessed these terms are attributes of the real-virtual connection.
+    Synchronization is used here instead of twinning, mirroring and connecting. 
+    Real-time is a time value, which is most of the time a constant value and defines the update frequency of the state of the virtual system of interest relative to the system of interest.
+    Fidelity is the degree of precision and accuracy of our digital twin, relative to the system of interest.
+    These words are highly dependent on the context of the digital twin.
     \subsection{Research objective}
@@
     \subsection{Research question}\label{section: Research Questions}
-    What is quality of digital twins?
+    What is the quality of digital twins?
 

### 2023-02-06 manuscripts/paper-1/main.tex
Second Part Finished

@@
     \section{State of the art on quality}
-    TODO
+    In the Oxford English Dictionary, the word `quality' is described as a noun as well as an adjective. The Adjective form indicates, a high standard or excellence. 
+    For example, the phrase `quality products' implies that quality adds a high standard state to the product. 
+    There are several meanings for the noun, but the one that interests us in this situation is `the standard of something as measured against other things of a similar kind. \cite{OxfordDictionary}'
+    This definition shows the relativity of quality.
 
-    \subsection{Product quality}
-    Most generic (e.g.~House of quality, ...)
+    According to ISO 9000:2015, quality is the degree to which a set of inherent characteristics of an object fulfills requirements~\cite{ISO9000}.
+Several words need to be expanded, to understand this definition.
+
+    First, the standard also explains characteristics as distinguishing features such as physical, sensory, behavioral, temporal, ergonomic and functional. 
+    Instead of an object, a system can be used for more generalization.
+    As for the requirements, the standard also explains as a requirement is a need or expectation that is stated, generally implied or obligatory.~\cite{ISO9000}
+
+    Thus, when these definitions are combined, we obtain the following: `Quality is a degree to which a set of inherent distinguishing features of a system fulfills a need or expectation that is stated, generally implied or obligatory'.
+    It should be highlighted that there are various quality definitions by so-called `Quality Gurus', but the authors decided to expand the standard definition of ISO 9000.
+
+    \subsection{Product quality and Management}
+    A product is a tangible or intangible system that satisfies the needs or wants of a customer. It could be a physical system like a car, or an abstract system, like a digital twin. 
+    Regarding product quality, there are two different aspects~\cite{GrievesPLMBook}.
+    First, quality is an attribute of a product, which meets product specifications.
+Specifications are mostly defined by the supra-systems subsystems, such as by the stakeholders within the supra-system,  If the stakeholders' expectations, or needs, are met, we can consider high quality.
+    The ability to execute to a specific usage standard is the second facet of product quality.
+Since this standardization is usually not controllable, unlike the first, the system's quality will be determined by how the implied or obligatory standards are fulfilled.
+
+    Quality management is a management type, which has an interest in Quality, and quality assurance is one of the parts of quality management, 
+    which focuses on providing fidelity that quality requirements will be fulfilled. This means that quality assurance is a subsystem of quality management.
+
+    Quality management systems(QMS) are being used to plan and execute the organization's quality policies and goals. 
+    Examples of such systems can be a standard like ISO 9001 which can provide a framework for an organization, or a data-driven methodology 
+    such as Six Sigma to reduce defects and improve efficiency. These concepts are not new, for example, ISO 9001 standard has been established in 1987, 
+    and is still being regularly updated~\cite{ISO9001DebunkingtheMyth}.
 
     \subsection{Software quality}
-    Medium (e.g.~ISO/IEC 9126 and ISO 25010, ...)
+    Software is a  virtual system, which has a set of instructions, data or programs used to perform a specific task. 
+    All virtual systems, which we described above, need a medium to live on, hence these systems can be found in a computer or other electronic device.  
+    Software quality according to IEEE 730-2014, is: 
+    `The degree to which a software product meets established requirements; however, 
+    quality depends upon the degree to which those established requirements accurately represent stakeholder needs, wants, and expectations'~\cite{IEE730-2014}. 
+    As can be seen, it's a generic explanation of a quality, which doesn't differ much from the explanation we gave above.
+
+    Software quality management techniques come from already used manufacturing techniques in the industries.
+    For example, the quality assurance which we mentioned above, also has been used as a software quality management activity with some differences. 
+    In manufacturing, products will never exactly meet a specification, due to errors in the machining so there should be some tolerance for the manufacturing. 
+    But in the software systems, or more precisely in the virtual systems, it's most of the time, not the case. 
+    Also its nearly impossible to conclude that, the software product fully meets its specifications\cite{SoftwareEngineering}.
+
+    According to ISO/IEC:25010:2011, there are eight software quality attributes. Functional Suitability, 
+    Performance efficiency, compatibility, usability, reliability, security, maintainability and portability.\cite{ISO/IEC:25010}
+    Of course, not all aspects can be inspected and the person, who is responsible for the quality of the product, should choose the critical aspects of the software product and further the process according to that decision.
 
     \subsection{Digital twin quality}
-    Most specific (a bit more research here!)
+    To analyze current DT literature within the concept of digital twin quality literature analysis was executed. 
+    The analysis especially focused on how the digital twin quality is mentioned and assessed within the academic dissertations.
+
+    \subsubsection*{Literature Search Methodology}
+    Google Scholar (GS), Scopus (SCP) and Research Rabbit (RR) tools are used to fulfill our requirements for the literature review.
+Since there is a great number of digital twin publications in academics,
+    narrowing the research is necessary, so the following algorithm with several levels of filtering will be applied.
+
+    First filtering will be done with the following criteria
+
+    \begin{itemize}
+        \item  Dissertations should be written in English and published in a journal/conference.
+        \item  Dissertations should not be older than 2016
+        \item  Search term should be exactly searched
+    \end{itemize}
+
+    Filtering query calls for the GS and SCP are the following
+    \begin{itemize}
+        \item Google Scholar = `search term'
+        \item Scopus = ALL (`digital twin quality') AND PUBYEAR > 2016 AND PUBYEAR < 2023 AND (LIMIT-TO (LANGUAGE, `English'))
+    \end{itemize}
+    Also want to note that, in the GS, there isn't a function that filters the dates, instead the user should click the Since 2016 option to filter the dates.
+
+    Second filtering will be done to eliminate the duplications and even though authors already filtered the search for the English language, 
+    still some results without the English language will appear. Again, language filtering should be done to clean the results.
+    \begin{itemize}
+        \item Remove Duplications
+        \item Remove the dissertations which are not English manually
+    \end{itemize}
+
+    After the second filtration, the third filtering which is a manual investigation should occur with the following filtering criteria:
+    \begin{itemize}
+        \item  Proper literature review should be present in the selected dissertation
+        \item  Abstract and conclusion should be relevant to the search term
+    \end{itemize}
+
+    If an interesting dissertation(s) would be found during the reading, it will be checked again with the first filter.
+
+    \subsection*{Literature Result}
+    First filtering was done for the search term "digital twin quality", meanwhile GS gave 41 different results, and SCP gave only 3 results.
+After the second filtering process, 3 duplications and 31 different results were found and 10 dissertations were not in English.
+    After the third filtering process, 9 dissertations passed and the rest is rejected.
+
+    \subsection*{Important Findings}
+
+    Important findings are the following;
+
+    \begin{itemize}
+        \item Shcherba et al.
+center their attention on the model quality, which is an observation for a digital twin subsystem.
+Despite being a crucial component of the digital twin, models alone cannot be used to assess the quality of the digital twin.
+        \item A consistency evaluation approach for digital twin models was developed by He Zhang et al.
+and can be used to assess the quality of the models.
+Additionally, the authors discuss crucial ideas like consistency between real and virtual systems and ultra-fidelity models.
+The improvement of the service component is the primary emphasis of this article.
+Tao's five-dimensional digital twin concept includes this component.
+        \item He Zhang et al. introduce the updating method for digital twin models in yet another insightful article. Once more, the accuracy and coherence of the model concepts were addressed.
+        \item Selch et al.
+work is the only one that discusses the quality of the digital twin.
+The paper presents a machine-learning approach based on Bayesian networks to track the quality of the digital twin.
+The unique aspect of this study is that the author, rather than just analyzing the digital twin as a single system, determines the contributions of subsystems to forecast the overall quality of the digital twin.
+The digital couplings, which are linkages between the subsystems, are also mentioned by Selch et al.
+as a source of extra uncertainty.
+        Since only one digital twin has been used in practice, multiple subsystem digital twins have not been validated.
+    \end{itemize}
 
@@
     \subsubsection{Definition}
-    Effort to adapt the digital twin to new circumstances (e.g.\ add new machine, replace machine, etc.)
+    Efforts to adapt the digital twin to new circumstances (e.g.\ add a new machine, replace the machine, etc.)
 
@@
     TODO
-
-    \begin{comment}
-        \section{Whatever}
-
-        \subsection{Grieves Information Mirroring Model}
-
-        \subsubsection{How it is defined?}
-
-        His conceptual model is an ideal Product Lifecycle Management (PLM), has just one important goal which is to gather as much information about the actual space as feasible to minimize the waste of energy, time, and materials.
-        It is composed primarily of four parts. Real or physical space, virtual space, connections between real and virtual space, and virtual simulations.
-
-        As we can see, it shares almost all of the same components as the digital twins of today.
-Virtual simulation is an optional component that Grieves subsequently removed to simplify the model.
-[GrievesEliminateForthElement]
-        The simple model version is indicated by the fact that only the first three (Physical System, Virtual System, and Connection Between Them) will be taken into account. 
-        It should be mentioned that we shall define these three components in our own words using previous definitions of each component.  Additionally, by using the consortium's definition, we are simply improving the grieves IM model as a reference.
-        The physical space is where we start first.
-
-        \begin{figure}[htbp]
-            \includegraphics[width=\columnwidth]{Grieves Information Mirroring Model.png}
-            \caption{Information Mirroring Model}
-            \label{IM}
-        \end{figure}
-
-        \subsubsection{Why it is problematic?}
-
-        TODO
-
-        \subsection{Real System}
-        We shall refer to a real system instead of calling it a real space. 
-        Why? Because everything is an open system according to the system theory, 
-        with the upper bound of the universe and lower bound as subatomic particles.
-        As a result, the universe and subatomic particles can be viewed as closed systems, 
-        simplifying definitions and facilitating the analysis of entities as systems. 
-        In the literature, we see most of the time a notion called " entity" and sometimes an "artifact". 
-        For instance, the digital twin framework developed by (TAO et al.) has both a physical and virtual entity.
-        An entity is any separate and independent system, whether it be real or abstract.
-        On the other hand, an artifact is a thing that humans have created or constructed. 
-        Therefore, when we speak of entities, we really mean systems. 
-        And when we discuss artifacts, we are still discussing physical systems but with the caveat of human interaction. 
-        Automobiles, engines, software, artwork, food, and telephones are a few examples of artifacts.
-
-        Above, we established the term "entity," but what about the physical connection of an entity? 
-        Because an entity could be a physical system or an abstract system. 
-        We won't go into further depth about these two distinct ideas, but just so you know, 
-        when we talk about physical systems, we do not include abstract systems that require a
-        media to exist, such as ideas, texts, diagrams, and mathematics, which are nothing more than abstractions.
-
-        The term "real system" in the context of digital twins refers to a system that is a tangible thing and also has 
-        the characteristics of a system. The usage of various artifacts by Grieves in a system he referred to as `real space' 
-        can be seen in figure X. 
-        For convenience, we'll refer to this system as a "real system" or, as Mobus prefers to say, a `system of interest.'. 
-        Instead of using black-and-white images, we instead created subsystems out of circles, each of which represented an artifact. 
-        It is clear to see that every subsystem (artifact) includes smaller subsystems as well. 
-        Once more using Grieves' example, an automobile(an element of the real space according to figure 1), 
-        which is an artifact, that includes several parts, including a radio, a motor, wheels, etc. 
-        Additionally, these subsystems (artifacts) can be further broken down into even smaller subsystems, 
-        down to subatomic particles, which, as we mentioned above, is the lowest we can go in terms of the system theory. 
-        But the question is, should we break things down to the level of subatomic particles to comprehend the system? Considering digital twins, 
-        the answer is a resounding no.
-
-        Consequently, why bother to define these terms? Because the granularity of the digital twin is determined by the complexity of the real system. 
-        In the end, a System of Interest is what we'll be twinning! Of course, the system of interest is not as simple to define as in figure X. 
-        One crucial component and stage of the digital twin is to comprehend how the real system, or more precisely the system of interest, 
-        actually functions. How can one know what to twin if it is not well understood?
-        The system of interest can be analyzed in three different ways. If we don't have the opportunity to examine the inner workings of the system, 
-        we can use the black boxing technique, which focuses primarily on the mathematical (and frequently statistical) 
-        relationships between inputs and outputs. This method doesn't provide insight into the inner workings of the system, but it still provides 
-        a basic grasp of how a system operates. If the system exhibits linear behavior, it works great.
-
-        The second method, known as the gray box method, examines the inner workings of comparable systems that should be `like' 
-        the system of interest to understand how the inner workings of a similar system react when various inputs are applied and the results of the system are monitored. 
-        This method is used for the majority of biological work, such as the experiments medical students conduct on cadavers to learn how the human body functions.
-
-        The final method, known as the `white box method,' is better than the others since it examines every system's component. 
-        The interesting thing to realize is that the system's integrity(Objectiveness) shouldn't be impaired.
-        What objectiveness means is that while the system functions as a whole, we should also study the relationships 
-        between the subsystems in addition to the subsystems themselves. 
-        Observing our galaxy is a fantastic example. Telescopes allow us to individually assess the condition of the subsystems (planets, solar systems) 
-        without affecting the overall system.
-
-        Physical space, as a whole, is a physical system (which we refer to as the system of interest),
-        with subsystems and linkages between them. Depending on the SOI's context, we can use black box, gray box, or white box methodologies to study the system.
-        In addition, I wish to draw attention to the fact that the SOI's details are not fully depicted in figure 2. 
-        For additional details on the system theory, we strongly advise reading `von Bertalanffy 2003'.
-
-        \begin{figure}[htbp]
-            \includegraphics[width=\columnwidth]{SOI.png}
-            \caption{System Of Interest}
-            \label{SOI}
-        \end{figure}
-
-        \subsection{Virtual System(Digital Twin)}
-
-        First of all, what does the term `virtual' mean? Virtual refers to an existence (or entity?) that exists in a computer system as opposed to a physical system. 
-        Therefore, we made sure to note that we are not speaking of abstract systems when we described physical systems. 
-        We also discussed the distinction between an entity and an artifact. The term `abstract systems'  refers to systems that have had their set of variables and functions 
-        `abstracted'  so that they may be computed by a solver, which in this case could be either the human brain or a computer.
-        Additionally, just because a system is abstract doesn't mean it lacks a physical body; rather, as we previously established, 
-        it is abstracted. Computers, symbolic language, and the human mind all can contain these abstract systems.
-        Symbolic text in this sense covers not only text on the sheet but also mathematical symbols, logic, etc.
-
-        Virtual systems can't exist on their own since, like abstract systems, they require a medium to exist.
-        Computer systems, a higher system of virtual systems, are an ideal medium for virtual systems.
-
-        \begin{figure}[htbp]
-            \includegraphics[width=\columnwidth]{DT SOI.png}
-            \caption{Digital Twin SOI}
-            \label{DTSOI}
-        \end{figure}
-
-        Recall that Grieves referred to the virtual system as a virtual space in figure 1. 
-        We refer to it as a virtual system because it can only exist inside a computer system. 
-        Additionally, we refer to the entities he depicted in the virtual space as virtual subsystems rather than the virtual entities he used. In figure 3, 
-        we were creative and wrote `digital twin'  rather than `virtual system.'  Where does this digital twin emerge from?
-
-        We must first understand what digital implies to comprehend the concept of a digital twin.  
-        The term `digital has been in use since the late 14th century and is derived from the Latin word `digitus, ' 
-        which means `finger'  or `toe.'. It gained popularity after digitalization in the 20th century and refers to the use of discrete digits to represent data. 
-        Digital images, for instance, are represented by a matrix of pixels, which are nothing more than 8-bit integer values between 0 and 255 which represent the intensity 
-        of the pixel. 
-        We will therefore have digital models if we can digitally model our models. 
-        Therefore, we will have digital models if we can digitally model our models. Where are these digital models being created? Throughout the digital system! 
-        This system is referred to as a `digital twin'  since it is a digital twin of the SOI that is represented in the computer system.
-
-        The reader will quickly and easily comprehend that a computer system may have several digital twins, 
-        and that these systems may also be connected in some way, 
-        creating yet another system that is also referred to as a digital twin. 
-        Another immediate realization is that perhaps we won't have our SOI yet, 
-        so how can we twin something that doesn't exist? Although the term we preferred was the best definition (for us), 
-        it does not directly address the second question. In reality, most of the time, 
-        the physical product will not be ready or not present to make a digital twin out of it. 
-        But if we could have some data about the physical system, for example how it should look, 
-        how much weight it should have, approximate dimensions and so on,  we can start constructing our system abstractly, 
-        within the computer systems, with diagrams, or with using symbolic language. 
-        But the important point is that everyone, who works on this abstract system should have a singular reference so that it can be constructed. Also after the construction, 
-        still a real system is needed to validate and verify. Most frequently, this viewpoint is referred to as a prototype digital twin. And if the SOI is present its called instance digital twin.
-
-        So far, we inspected the real system (system of interest), and virtual system. 
-        As we talked about above, there is a third part which is a connection between the real system and the virtual system, which we will explain next.
-
-        \subsection{Connection Between the Systems}
-
-        \subsection{Possibility of States}
-        \subsection{Context of Digital Twin}
-        \subsection{Quality of Digital Twin}
-    \end{comment}
-
-    \begin{comment}
-        \section{Literature review}
-        \label{section: literature}
-        Literature analysis was executed, to analyze current DT literature within the concept of digital twin quality. The analysis especially focused on 
-        how the digital twin quality is mentioned and assessed within the academic dissertations.
-
-        Methodology (see Section~\ref{section:liteature_methodology}), Result (see Section~\ref{section:liteature_result}), and Summary (See Section~\ref{section:liteature_summary})...
-
-        \subsection{Methodology}
-        \label{section:liteature_methodology}
-        Google Scholar (GS), Scopus (SCP) and Research Rabbit (RR) tools are used to fulfill our requirements for the literature review. 
-        Since there is a great number of digital twin publications in academics, 
-        narrowing the research is necessary, so the following algorithm which can be seen in Figure \ref{fig:literaturesearchalgorithm} with several levels of filtering will be applied.
-
-        First filtering will be done with the following criteria:
-        \begin{itemize}
-            \item Dissertations should be written in English and published in a journal/conference.
-            \item Dissertations should not be older than 2018
-            \item Search term should be exactly searched.
-        \end{itemize}
-
-        Filtering query calls for the GS and SCP are the following:
-        \begin{itemize}
-            \item Google Scholar = "search term"
-            \item Scopus = ALL ( "digital twin quality" ) AND PUBYEAR > 2018 AND PUBYEAR < 2023 AND ( LIMIT-TO (LANGUAGE , "English" )) 
-        \end{itemize}
-
-        Also want to note that, in the GS, there isn't a function that filters the dates, instead the user should click the Since 2018 option to filter the dates.
-
-        Second filtering will be done to eliminate the duplications and even though authors already filtered the search for the English language,
-        still some results without the English language will appear. Again, language filtering should be done to clean the results.
-        \begin{itemize}
-            \item Remove Duplications
-            \item Remove the dissertations which are not English manually
-        \end{itemize}
-
-        After the second filtration, the third filtering which is a manual investigation should occur with the following filtering criteria:
-        \begin{itemize}
-            \item Proper literature review should be present in the selected dissertation
-            \item Abstract and conclusion should be relevant to the search term
-        \end{itemize}
-
-        If an interesting dissertation(s) would be found during the reading, it will be checked again with the first filter.
-        \begin{figure}
-            \centering
-            \includegraphics[width =0.45\textwidth]{LRMethod.png}
-            \caption{Literature Search Algorithm}
-            \label{fig:literaturesearchalgorithm}
-        \end{figure} 
-        \begin{figure}
-            \centering
-            \includegraphics[width =0.45\textwidth]{LRMethodLegacy.png}
-            \caption{Literature Search Algorithm Legend}
-            \label{fig:literaturesearchalgorithmlegend}
-        \end{figure}
-
-        \subsection{Result}
-        \label{section:liteature_result}
-        The following results were achieved by selecting several search terms.
-
-        \subsubsection*{Digital Twin Quality}
-        \label{subsection:DigitalTwinQuality}
-        First filtering was done for the search term "digital twin quality", meanwhile GS gave 41 different results, and SCP gave only 3 results.
-        After the second filtering process, 3 duplications and 31 different results were found. 10 dissertations were not in English.
-        After the third filtering process, 9 dissertations passed and the rest is rejected.
-
-        \subsubsection*{Digital Twin Model Verification}
-        \label{subsection:DigitalTwinVerification}
-
-        \subsubsection*{Digital Twin Model Validation}
-        \label{subsection:DigitalTwinValidation}
-        %What is the existing literature?
-
-        \subsection{Summary}~\label{section:liteature_summary}
-        What do we learn from existing literature?
-
-        He Zhang et al.introduced a consistency evaluation method for digital twin models, which can be used to assess the quality of the digital twin ~\cite{Jones2020}.
-        (Existing literature does at most partially solve our problem!)
-    \end{comment}
 
@@
 
-    \begin{comment}
-        \section{Case study (FELICE)}\label{section:case}
-        TODO (Explain the limitations of the FELICE digital twin! It is not a complete digital twin according to literature! It includes this, it is missing this.)
-
-        \subsection{Methodology}~\label{section:case_methodology}
-        TODO
-
-        \subsection{Result}~\label{section:case_result}
-        TODO
-
-        \subsection{Summary}~\label{section:case_summary}
-        TODO
-    \end{comment}
-
     \section{Conclusion}~\label{section:conclusion}

### 2023-02-11 manuscripts/paper-1/main.tex
Simulation quality added

@@
 
-    \subsection{Product quality and Management}
+    \subsection*{Product quality and Management}
     A product is a tangible or intangible system that satisfies the needs or wants of a customer. It could be a physical system like a car, or an abstract system, like a digital twin. 
@@
 
-    \subsection{Software quality}
+    \subsection*{Software quality}
     Software is a  virtual system, which has a set of instructions, data or programs used to perform a specific task. 
@@
     Software quality management techniques come from already used manufacturing techniques in the industries.
-    For example, the quality assurance which we mentioned above, also has been used as a software quality management activity with some differences. 
+    For example, the quality assurance that we mentioned above, also has been used as a software quality management activity with some differences. 
     In manufacturing, products will never exactly meet a specification, due to errors in the machining so there should be some tolerance for the manufacturing. 
@@
 
-    \subsection{Digital twin quality}
+    \subsection*{Simulation Quality}
+    Simulation models are not merely virtual systems; they are also abstracted systems, which are nothing more than imitations or, to be more precise, abstractions of real systems. 
+    We are simulating every day when we are trying to predict the future outcome or abstractly thinking about the past state of some occurred event. 
+    An important element to remember is that we mentally model the event before executing the simulation. However, most of the simulation processes we see today, 
+    are computer-based, with software programs.
+These programs include ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic}, as examples.
+Consequently, the idea of simulation software programs emerges.
+
+    Validation and verification can be used to evaluate the quality characteristics of the simulation model \cite{StewartSimulation} \cite{VerificationValidationSergent} \cite{OsmanBalci}. 
+    Validation is the process of evaluating the simulation quality of the model in comparison to the real system from the perspective of the model's intended applications. 
+    On the other hand, verification is a procedure to evaluate a simulation model's implementation and its associated data concerning the conceptual description and specifications of the model developer.
+
+    \subsection*{Digital twin quality}
     To analyze current DT literature within the concept of digital twin quality literature analysis was executed. 
@@
     Important findings are the following;
-
     \begin{itemize}
@@
 Tao's five-dimensional digital twin concept includes this component.
-        \item He Zhang et al. introduce the updating method for digital twin models in yet another insightful article. Once more, the accuracy and coherence of the model concepts were addressed.
+        \item He Zhang et al. introduces the updating method for digital twin models in yet another insightful article. Once more, the accuracy and coherence of the model concepts were addressed.
         \item Selch et al.
@@
     \subsection{First criterion: Correctness}
-
     \subsubsection{Definition}
+    Correctness, 
     Car vs airplane (with nice pictures!)

### 2023-02-13 manuscripts/paper-1/main.tex
Added the definitions for the criterions

@@
     \subsection{First criterion: Correctness}
-    \subsubsection{Definition}
-    Correctness, 
+    Correctness is a  derived word from the adjective correct, which means that something is error-free regarding a fact or truth~\cite{OxfordDictionary}. 
+    In the context of the digital twins, our fact or truth is a real system hence, 
+    correctness is a grade of quality, that indicates an error between the real system and a digital twin system.
+    Meanwhile, the quality of being correct is described by the term accuracy. Another important word is precision, 
+    which refers to the ability to be precise and accurate\cite{OxfordDictionary}. 
+    From a technical standpoint, we use precision in mathematics by the number of provided digits. 
+    For instance, binary64 has 53 significant digits while binary32 has 24, displaying the precision of the structure \cite{IEE754}.  
     Car vs airplane (with nice pictures!)
-
-    \subsubsection{Motivation}
-    TODO
 
@@
     \subsection{Second criterion: Completeness}
-
-    \subsubsection{Definition}
-    Car vs engine (with nice pictures!)
-
-    \subsubsection{Motivation}
-    TODO
+    Complete can be used as an adjective, attribute, or verb with an object. Completeness is a word that is derived from complete \cite{OxfordDictionary}.
+    We'll use the adjectival form which describes the word "complete" as having all the necessary or appropriate parts.
+    One should first analyze and synthesize the real system to identify the subsystems and related systems in the supra-system before evaluating the completeness of the digital twin. 
+    Completeness can be assessed after analysis and synthesis by contrasting the subsystems of the real world with those in the digital twin.
 
@@
     \subsection{Third criterion: Fidelity}
-
-    \subsubsection{Definition}
-    Linear vs differential (with nice pictures!)
-
-    \subsubsection{Motivation}
-    TODO
+    The concept of fidelity has garnered significant attention in recent years and continues to be an important area of research in digital twins.
+    In the context of digital twins, Fidelity refers to the degree of exactness with which the real system is copied and represented.
+    Low-fidelity indicates a simplified representation, while high-fidelity refers to an accurate and detailed representation of the real system.
+    This quality attribute plays a crucial role in evaluating the effectiveness of digital twins in accurately capturing the behavior and properties of real-world systems. 
+    \subsubsection*{Fidelity vs Correctness}
+    Correctness is a functional quality attribute, which assesses the behavior of the digital twin systems, by how accurately the results with the given precision match the behavior of the real system or more
+    specifically outputs with the same given inputs. 
+    This quality attribute focuses on the behavior of the system.
+    On the other hand, fidelity is another quality attribute to consider. 
+    It deals with the level of exactness and detail in the digital twin system's representation. 
+    Fidelity concerns itself, with how the digital-twin system is exactly relative to the real system with a certain level of detail, which is more to do with the depiction or representation of the digital twin systems, rather than their behavior of them.
 
@@
     \subsection{Fourth criterion: Efficiency}
-
-    \subsubsection{Definition}
-    1ms vs 1min (with nice pictures!)
-
-    \subsubsection{Motivation}
-    TODO
+    Efficiency refers to the quality of being efficient, and efficiency can be explained as achieving maximum productivity with minimum wasted effort or expense. 
+    The concept of efficiency is tightly coupled with productivity, which refers to the quality of being productive.
+The word productive can be explained as producing or being able to produce large amounts of goods \cite{OxfordDictionary}.
+    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired.
+Goods of the digital twin are nothing but information,
+    which Grieves first indicated with this Information Mirror Model \cite{GrievesPLMBook}.
+So to assess the efficiency, one should inspect the sinks and sources of the digital twin system, to identify the waste, expense and productivity.
 
@@
     \subsection{Fifth criterion: Evolvability}
-
-    \subsubsection{Definition}
-    Efforts to adapt the digital twin to new circumstances (e.g.\ add a new machine, replace the machine, etc.)
-
-    \subsubsection{Motivation}
-    TODO
+    TODO CITE
+    A system's capability to enhance its suitability to its environment through alterations to both its internal and functional structure is referred to as evolvability.
+Another term used to describe the response to changes in the environment is adaptability.
+    However, this concept differs from evolvability in that it only affects a system's internal or functional structure temporarily.
+In contrast, evolvable systems undergo definite changes in their structures.
+    For instance, a digital twin, which is a virtual system, can be designed to be more flexible and scalable, allowing for easy updates and the addition of new features. 
+    These updates and new features will result in definite changes to the structure of the system.
+On the other hand, a responsive web design is an adaptable system, capable of adjusting its size and layout depending on the user's hardware.
+    As we have seen in CITE, the update method shows that digital twins are evolvable systems,
+    hence this attribute should be considered when the digital twin's quality is inspected.
+To assess the evolvability attribute, scalability analysis, reusability analysis, modifiability analysis, testability analysis, and maintainability analysis can be performed.
 

### 2023-02-13 manuscripts/paper-1/main.tex
Bibtex and Citiations are arranged

@@
         \includegraphics[width =0.45\textwidth]{GrievesInformationMirroringModel.png}
-        \caption{Grieves Information Mirroring Model}
-        \label{fig:GrievesInformationMirroringModel}
+        \caption{Grieves Information Mirroring Model}\label{fig:GrievesInformationMirroringModel}
         \cite{GrievesPLMBook}
@@
     \subsection*{Literature Result}
-    First filtering was done for the search term "digital twin quality", meanwhile GS gave 41 different results, and SCP gave only 3 results.
+    First filtering was done for the search term `digital twin quality', meanwhile GS gave 41 different results, and SCP gave only 3 results.
 After the second filtering process, 3 duplications and 31 different results were found and 10 dissertations were not in English.
@@
 center their attention on the model quality, which is an observation for a digital twin subsystem.
-Despite being a crucial component of the digital twin, models alone cannot be used to assess the quality of the digital twin.
-        \item A consistency evaluation approach for digital twin models was developed by He Zhang et al.
-and can be used to assess the quality of the models.
-Additionally, the authors discuss crucial ideas like consistency between real and virtual systems and ultra-fidelity models.
+Despite being a crucial component of the digital twin, models alone cannot be used to assess the quality of the digital twin~\cite{Shcherba}.
+        \item A consistency evaluation approach for digital twin models was developed by He Zhang et al. and can be used to assess the quality of the models. Additionally, 
+        the authors discuss crucial ideas like consistency between real and virtual systems and ultra-fidelity models.
 The improvement of the service component is the primary emphasis of this article.
-Tao's five-dimensional digital twin concept includes this component.
-        \item He Zhang et al. introduces the updating method for digital twin models in yet another insightful article. Once more, the accuracy and coherence of the model concepts were addressed.
+Tao's five-dimensional digital twin concept includes this component~\cite{ZHANGEVALUATIONMETHOD}.
+        \item He Zhang et al.
+introduces the updating method for digital twin models in yet another insightful article.
+Once more, the accuracy and coherence of the model concepts were addressed~\cite{ZHANGUPDATEMETHOD}.
         \item Selch et al.
@@
 as a source of extra uncertainty.
-        Since only one digital twin has been used in practice, multiple subsystem digital twins have not been validated.
+        Since only one digital twin has been used in practice, multiple subsystem digital twins have not been validated~\cite{QualityMonitoringofCoupledDigitalTwins}.
     \end{itemize}
@@
     \subsection{Second criterion: Completeness}
-    Complete can be used as an adjective, attribute, or verb with an object. Completeness is a word that is derived from complete \cite{OxfordDictionary}.
-    We'll use the adjectival form which describes the word "complete" as having all the necessary or appropriate parts.
+    Complete can be used as an adjective, attribute, or verb with an object. Completeness is a word that is derived from complete~\cite{OxfordDictionary}.
+    We'll use the adjectival form which describes the word `complete' as having all the necessary or appropriate parts.
     One should first analyze and synthesize the real system to identify the subsystems and related systems in the supra-system before evaluating the completeness of the digital twin. 
@@
     The concept of efficiency is tightly coupled with productivity, which refers to the quality of being productive.
-The word productive can be explained as producing or being able to produce large amounts of goods \cite{OxfordDictionary}.
+The word productive can be explained as producing or being able to produce large amounts of goods~\cite{OxfordDictionary}.
     For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired.
 Goods of the digital twin are nothing but information,
-    which Grieves first indicated with this Information Mirror Model \cite{GrievesPLMBook}.
+    which Grieves first indicated with this Information Mirror Model~\cite{GrievesPLMBook}.
 So to assess the efficiency, one should inspect the sinks and sources of the digital twin system, to identify the waste, expense and productivity.
@@
     \subsection{Fifth criterion: Evolvability}
-    TODO CITE
     A system's capability to enhance its suitability to its environment through alterations to both its internal and functional structure is referred to as evolvability.
@@
 On the other hand, a responsive web design is an adaptable system, capable of adjusting its size and layout depending on the user's hardware.
-    As we have seen in CITE, the update method shows that digital twins are evolvable systems,
+    As we have seen in~\cite{ZHANGUPDATEMETHOD}, the update method shows that digital twins are evolvable systems,
     hence this attribute should be considered when the digital twin's quality is inspected.

### 2023-02-14 manuscripts/paper-1/main.tex
LR DT  verification and validation added

@@
     \subsection*{Connection Between the Real and Virtual System}
-    If we step back and observe the consortium's definition in~\ref{section:introduction}, which we told is the best definition we could find, 
+    If we step back and observe the consortium's definition in Section~\ref{section:introduction}, which we told is the best definition we could find, 
     it talks about synchronization, fidelity and some specified frequency. As can be guessed these terms are attributes of the real-virtual connection.
@@
 Since there is a great number of digital twin publications in academics,
-    narrowing the research is necessary, so the following algorithm with several levels of filtering will be applied.
+    narrowing the research is necessary, so the following algorithm with two levels of filtering will be applied.
 
-    First filtering will be done with the following criteria
-
+    Initial filtering will be done with the following criteria
     \begin{itemize}
         \item  Dissertations should be written in English and published in a journal/conference.
-        \item  Dissertations should not be older than 2016
         \item  Search term should be exactly searched
@@
         \item Google Scholar = `search term'
-        \item Scopus = ALL (`digital twin quality') AND PUBYEAR > 2016 AND PUBYEAR < 2023 AND (LIMIT-TO (LANGUAGE, `English'))
+        \item Scopus = ALL (`digital twin quality') AND (LIMIT-TO (LANGUAGE, `English'))
     \end{itemize}
-    Also want to note that, in the GS, there isn't a function that filters the dates, instead the user should click the Since 2016 option to filter the dates.
-
-    Second filtering will be done to eliminate the duplications and even though authors already filtered the search for the English language, 
-    still some results without the English language will appear. Again, language filtering should be done to clean the results.
+    After the initial filtration, the second filtering which is a manual investigation should occur with the following filtering criteria:
     \begin{itemize}
@@
         \item  Remove the dissertations which are not English manually
-    \end{itemize}
-
-    After the second filtration, the third filtering which is a manual investigation should occur with the following filtering criteria:
-    \begin{itemize}
         \item  Proper literature review should be present in the selected dissertation
@@
 
-    If an interesting dissertation(s) would be found during the reading, it will be checked again with the first filter.
+    If an interesting dissertation(s) would be found during the reading, it will be checked again with the initial filter.
 
     \subsection*{Literature Result}
-    First filtering was done for the search term `digital twin quality', meanwhile GS gave 41 different results, and SCP gave only 3 results.
-After the second filtering process, 3 duplications and 31 different results were found and 10 dissertations were not in English.
-    After the third filtering process, 9 dissertations passed and the rest is rejected.
+    The search term `digital twin quality' initially yielded 41 results on Google Scholar and three on Scopus. 
+    After the second filtering stage, six duplicate dissertations were removed, along with ten dissertations that were not in English.
+As a result, only nine dissertations passed all the criteria and were inspected, while the remainder were rejected.
 
-    \subsection*{Important Findings}
+    The search term `digital twin verification' initially yielded, resulting in nineteen hits on Google Scholar and zero on Scopus.
+After the second filtering stage, one duplicate dissertation was removed, along with two dissertations that were not in English.
+    As a result, all dissertations were rejected.
 
-    Important findings are the following;
+    The search term `digital twin validation' was filtered initially, resulting in fifty-nine hits on Google Scholar and zero on Scopus.
+After the second filtering stage, four duplicate dissertations were removed, along with 4 dissertations that were not in English.
+    As a result, eight dissertations passed all the criteria and were inspected while the remainder were rejected.
+
+    \subsection*{Findings}
+
+    The findings are the following;
     \begin{itemize}
@@
         Since only one digital twin has been used in practice, multiple subsystem digital twins have not been validated~\cite{QualityMonitoringofCoupledDigitalTwins}.
+        \item The stability of the digital twin models was assessed using the Kolmogorov-Smirnov statistical test, which measures the degree of similarity between the probability distribution of the model's predictions and the distribution of the actual data~\cite{RadarDigitalTwin}.
+        \item Edward Y.
+Hua et al.
+identify five open problems with digital twin model validation, including modeling realism, data uncertainty, system dynamics, use-case alignment, and reporting invalid modes.
+To address these challenges, the authors propose a digital-twin model validation framework.
+Additionally, the paper highlights three areas for future research,
+        including uncertainty and sensitivity analysis, model validation of system-of-systems, and combining expert knowledge and collected data~\cite{ValidationofDigitalTwins}.
+        \item Shotaro Hamato et al.
+demonstrated real-time anomaly detection was successfully demonstrated using the Unscented Kalman Filter with the digital twin model, but determining the appropriate threshold for anomaly detection remains an issue~\cite{JapeneseKalmanFilterCorrectness}.
     \end{itemize}
@@
     From a technical standpoint, we use precision in mathematics by the number of provided digits. 
-    For instance, binary64 has 53 significant digits while binary32 has 24, displaying the precision of the structure \cite{IEE754}.  
-    Car vs airplane (with nice pictures!)
+    For instance, binary64 has 53 significant digits while binary32 has 24, displaying the precision of the structure~\cite{IEE754}.
 
@@
     \subsection{Second criterion: Completeness}
-    Complete can be used as an adjective, attribute, or verb with an object. Completeness is a word that is derived from complete~\cite{OxfordDictionary}.
-    We'll use the adjectival form which describes the word `complete' as having all the necessary or appropriate parts.
-    One should first analyze and synthesize the real system to identify the subsystems and related systems in the supra-system before evaluating the completeness of the digital twin. 
-    Completeness can be assessed after analysis and synthesis by contrasting the subsystems of the real world with those in the digital twin.
+    According to the Oxford Dictionary, `complete'  can function as an adjective, attribute, or verb with an object\cite{OxfordDictionary}. When used as an adjective, it describes something 
+    as having all the necessary or appropriate parts. To evaluate the completeness of a digital twin, 
+    one must first analyze and synthesize the real system to identify subsystems and their relations with related systems in the supra-system. 
+    After this initial analysis, completeness can be assessed by comparing the subsystems and relations of the real world with those of the digital twin.
 
@@
 Goods of the digital twin are nothing but information,
-    which Grieves first indicated with this Information Mirror Model~\cite{GrievesPLMBook}.
+    which Grieves first indicated with his Information Mirror Model~\cite{GrievesPLMBook}.
 So to assess the efficiency, one should inspect the sinks and sources of the digital twin system, to identify the waste, expense and productivity.

### 2023-02-26 manuscripts/paper-1/main.tex
PreCorrection

@@
     What is the quality of digital twins?
+    What is the state art of digital twin quality?
 
@@
     \section{Initial approach in the FELICE project}
-    Inspired by ISO 25010...
+    FELICE addresses a critical problem in robotics which is the effective integration of human and robot abilities in a collaborative setting.
+This challenge requires the development of sophisticated algorithms and techniques that facilitate seamless communication,
+    cooperation, and coordination between humans and robotic agents. By addressing this issue, FELICE tries to represent a 
+    significant advancement in the field of robotics and has the potential to enhance the effectiveness and efficiency of a wide range of human-robot collaborative tasks with the consideration of safety~\cite{FELICE}.
+
+    In the present study, we inspected several artifacts to evaluate the quality of the digital twin for the FELICE project, which is currently in the design phase.
+These artifacts included process videos showing the current assembly procedure, a scope definition, a requirements specification, a general and operational conceptual model,
+    and a discrete event simulation module. We assessed the quality of these artifacts based on four crucial quality attributes: correctness, completeness, fidelity, efficiency, and evolvability.
 
@@
     Correctness is a  derived word from the adjective correct, which means that something is error-free regarding a fact or truth~\cite{OxfordDictionary}. 
-    In the context of the digital twins, our fact or truth is a real system hence, 
-    correctness is a grade of quality, that indicates an error between the real system and a digital twin system.
+    In the context of the digital twins, our fact or truth is a real system hence, correctness is a grade of quality, that indicates an error between the real system and a digital twin system.
     Meanwhile, the quality of being correct is described by the term accuracy. Another important word is precision, 
@@
     For instance, binary64 has 53 significant digits while binary32 has 24, displaying the precision of the structure~\cite{IEE754}.
-
-    \subsubsection{Findings from FELICE}
-    TODO
 
@@
     After this initial analysis, completeness can be assessed by comparing the subsystems and relations of the real world with those of the digital twin.
-
-    \subsubsection{Findings from FELICE}
-    TODO
 
@@
 
-    \subsubsection{Findings from FELICE}
-    TODO
-
     \subsection{Fourth criterion: Efficiency}
@@
 So to assess the efficiency, one should inspect the sinks and sources of the digital twin system, to identify the waste, expense and productivity.
-
-    \subsubsection{Findings from FELICE}
-    TODO
 
@@
 
-    \subsubsection{Findings from FELICE}
-    TODO
+    \begin{figure}[htbp]
+        \includegraphics[width=\columnwidth]{quality_inspection_results.png}
+        \caption{Overall Quality Inspection Results}
+        \label{fig:QualityInspectonResults}
 
-    \section{Future approach in the FELICE project}
-    \label{section:framework_1}
-    TODO
-
-    \begin{figure}[htbp]
-        \includegraphics[width=\columnwidth]{Digital Twin Deviation.png}
-        \caption{TODO}
-        \label{todo-2}
+    \end{figure}\begin{figure}[htbp]
+        \includegraphics[width=\columnwidth]{quality_inspection_results_with_artifacts.png}
+        \caption{ Quality Inspection Results Categorized with Artifacts}
+        \label{fig:QualityInspectonResultsWithArtifacts}
     \end{figure}
 
-    \begin{figure}[htbp]
-        \includegraphics[width=\columnwidth]{Digital Twin.png}
-        \caption{TODO}
-        \label{todo-1}
-    \end{figure}
+    As can be seen in Figures ~\ref{fig:QualityInspectonResults} and ~\ref{fig:QualityInspectonResultsWithArtifacts}, based on our inspection of the given artifacts,
+    we have identified a total of seven correctness issues, eleven completeness issues, and two fidelity issues. 
+    It is important to note that we were unable to inspect for efficiency as the project is still in the design phase, 
+    and we do not have enough data to make estimations for this attribute. Additionally, all of our inspections were conducted manually, 
+    which is susceptible to human error and inspector bias.
 
-    \begin{figure}[htbp]
-        \includegraphics[width=\columnwidth]{Continuous Quality Control.png}
-        \caption{TODO}
-        \label{todo-3}
-    \end{figure}
+    \subsection{Future approach in the FELICE project}
+    \label{section:framework_1}
+    To mitigate potential human bias and enhance the data-driven approach for quality assurance, ongoing research aims to address these issues. 
+    Furthermore, the assessment of digital twin quality can be significantly improved by obtaining data from real systems, thereby enabling better visibility and a more robust evaluation.
+As such, the use of empirical data in combination with machine learning techniques can offer a more objective and reliable means of evaluating the correctness, completeness, fidelity, efficiency, and evolvability of digital twins.
+Additionally, given the manual nature of the current inspections, it is important to acknowledge the potential for inspector bias, which may impact the accuracy of the assessments.
+    By leveraging technology to automate certain aspects of the evaluation process, it is possible to reduce the potential for such biases and improve the overall quality of digital twin assessments.
 
     \section{Conclusion}~\label{section:conclusion}
-    TODO
-
+    The success of the digital twin system depends on its quality, which requires careful evaluation based on several crucial quality attributes.
+The correctness of the system is measured by how accurately it behaves compared to the real system.
+    Completeness assesses whether the digital twin's subsystems and relations match those of the real system. 
+    Fidelity refers to the degree of exactness with which the real system is copied and represented.
+    Efficiency measures the productivity of the system and the minimum waste during the process. 
+    Evolvability is the system's ability to enhance its suitability to its environment through alterations to both its internal and functional structure. 
+    Evaluating these quality attributes of the FELICE digital twin system will help ensure its success in effectively integrating human and robot abilities in a collaborative setting, leading to enhanced efficiency and safety in various human-robot collaborative tasks.
     \section*{Acknowledgements}

### 2023-02-27 manuscripts/paper-1/main.tex
Update after some corrections

@@
     A popular but highly misunderstood notion with fuzzy boundaries is the `digital twin.' 
-    The misunderstanding began with the Apollo 13 mission, which many authors claim, had a first digital twin The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilized in the physical simulations.
+    The misunderstanding began with the Apollo 13 mission, which many authors claim, had a first digital twin.
+The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilized in physical simulations.
 Even though the `digital' aspect was expected to be present,
@@
 
-    What makes that definition the best?
+    Why do we assume this definition to be the best?
 Because it provides the highest abstraction level among the definitions of digital twins that we discovered during our literature analysis.
@@
 We want to stress that NASA's definition of a  digital twin is accurate since digital twins are systems that are `context' centered.
-    This definition, therefore, is appropriate in the context of NASA's use case and is thus accurate, but the abstraction level is not sufficiently high to allow for a thorough understanding of digital twins.
+    Therefore, this definition is appropriate in the context of NASA's use case and is thus accurate, but the abstraction level is not sufficiently high to allow for a thorough understanding of digital twins.
 
-    In addition, we would want to emphasize the significance of Grieves' 2006 description of digital twins in the PLM book,
+    In addition, we emphasize the significance of Grieves' 2006 description of digital twins in the PLM book,
     which traces the origins of the concept. Although it featured the same components as a digital twin at the time, it was known as an Information Mirroring Model (IM)~\cite{GrievesPLMBook}. 
@@
 Depending on the system's context, we can use black-box, gray-box, or white-box methodologies to study the system.
-    The usage of various artifacts by Grieves in a system he referred to as `real space' can be seen in Figure~\ref{fig:GrievesInformationMirroringModel}.
+    The use of various artifacts by Grieves in a system he referred to as `real space' can be seen in Figure~\ref{fig:GrievesInformationMirroringModel}.
 
     \subsection*{Virtual System}
-    Virtual refers to an existence that exists in a computer system as opposed to a physical system.
+    Virtual refers to an existence that exists in a computer system, as opposed to a physical system.
 Therefore, virtual systems are abstract systems, which are nothing but an abstraction of the real system.
-    The term `abstract systems' refers to systems that have had their set of variables and functions `abstracted' so that they may be computed by a solver, which in this case solver could be either the human brain or a computer.
+    The term `abstract systems' refers to systems that have had their set of variables and functions `abstracted' so that they may be computed by a solver, which in this case, a solver could be either the human brain or a computer.
     Additionally, just because a system is an abstract system doesn't mean it lacks a physical body; rather, it is abstracted. 
@@
     \subsection*{Connection Between the Real and Virtual System}
-    If we step back and observe the consortium's definition in Section~\ref{section:introduction}, which we told is the best definition we could find, 
-    it talks about synchronization, fidelity and some specified frequency. As can be guessed these terms are attributes of the real-virtual connection.
+    If we step back and observe the consortium's definition in Section~\ref{section:introduction}, which we assumed, was the best definition we could find, 
+    it mentions synchronization, fidelity and some specified frequency. As can be guessed these terms are attributes of the real-virtual connection.
     Synchronization is used here instead of twinning, mirroring and connecting. 
@@
     Simulation models are not merely virtual systems; they are also abstracted systems, which are nothing more than imitations or, to be more precise, abstractions of real systems. 
-    We are simulating every day when we are trying to predict the future outcome or abstractly thinking about the past state of some occurred event. 
+    We are simulating something every day when we are trying to predict the future outcome or abstractly thinking about the past state of some occurred event. 
     An important element to remember is that we mentally model the event before executing the simulation. However, most of the simulation processes we see today, 
@@
     \subsection*{Digital twin quality}
-    To analyze current DT literature within the concept of digital twin quality literature analysis was executed. 
+    To analyze the state of the digital twin quality, a literature analysis was executed. 
     The analysis especially focused on how the digital twin quality is mentioned and assessed within the academic dissertations.
@@
 
-    Initial filtering will be done with the following criteria
+    Initial filtering has been done with the following criteria
     \begin{itemize}
@@
     \end{itemize}
-
     Filtering query calls for the GS and SCP are the following
@@
         \item  Remove Duplications
-        \item  Remove the dissertations which are not English manually
+        \item  Remove the dissertations which are not English
         \item  Proper literature review should be present in the selected dissertation

### 2023-02-28 manuscripts/paper-1/main.tex
Made the new template work

@@
-\documentclass[9pt,conference]{IEEEtran}
-
+%%\documentclass[9pt,conference]{IEEEtran}
+\documentclass{llncs}
 \usepackage[colorlinks,allcolors=blue]{hyperref}
+\usepackage[T1]{fontenc}
 \usepackage{listings}
@@
 \usepackage{verbatim}
+
 \graphicspath{{./images/}}
@@
     \title{Quality assurance of digital twins -- An experience report in the automotive industry}
-    \author{
-        \IEEEauthorblockN{
-            Georg Hackenberg
+
+    \author{Georg Hackenberg\inst{1}
+    \and
+    Alican Tüzün\inst{1}
     }
-        \IEEEauthorblockA{
-            School of Engineering\\
+    \institute{School of Engineering\\
     University of Applied Sciences Upper Austria\\
     4600 Wels, Upper Austria, Austria\\
-            \href{mailto:georg.hackenberg@fh-wels.at}{georg.hackenberg@fh-wels.at}
-        }
-        \and
-        \IEEEauthorblockN{
-            Alican Tüzün
-        }
-        \IEEEauthorblockA{
-            School of Engineering\\
-            University of Applied Sciences Upper Austria\\
-            4600 Wels, Upper Austria, Austria\\
-            \href{mailto:alican.tuezuen@fh-wels.at}{alican.tuezuen@fh-wels.at}
-        }
-    }
+    \email{lncs@springer.com}}
+
     \maketitle
@@
     \bibliography{main}
-    \bibliographystyle{plain}
+    \bibliographystyle{splncs04}
 

### 2023-02-28 manuscripts/paper-1/main.tex
Introduction is written TODO 2,3,4 Organize

@@
     \section{Introduction}\label{section:introduction}
-    A popular but highly misunderstood notion with fuzzy boundaries is the `digital twin.' 
-    The misunderstanding began with the Apollo 13 mission, which many authors claim, had a first digital twin.
-The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilized in physical simulations.
-Even though the `digital' aspect was expected to be present,
-    it wasn't~\cite{GrievesApollo13}.
-The historic D-day map (also known as the Big Board) in Southwick House England, which was used simultaneously before and during operation, can be argued to be similar.
-    The board was a twin of the operation, and it included models of battalions and ships that reflected the actual locations of the corresponding formations. 
-    Furthermore, synchronization was implemented with radio communication to give directives from the real system to control the operation flow and also to update the twin's state~\cite{AMRC}.
 
-    To begin analyzing `the digital twin' and its quality, authors needed to come up with a concrete description that involved a great level of abstraction. 
-    The definition of a digital twin given by the digital twin consortium, according to the authors, is the best one currently available: `A digital twin is a virtual representation of real-world entities and processes, synchronized at
-    a specified frequency and fidelity.'~\cite{digitaltwinconsortium2022}.
+    The notion of the digital twin, which has gained popularity in 
+    recent years, is often subject to vague and ambiguous envisions\cite{Review1}.
+    The mispresenting this notion began with the physical twin of the Apollo 13 spacecraft. 
+    The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilised in the physical simulations. 
+    Even though the digital aspect was expected to be present, there wasn't\cite{GrievesApollo13}.
+    Another physical twin is the historic D-day map (also known as the Big Board) in Southwick House England, 
+    which was used simultaneously before and during operation, can be argued to be similar. 
+    The board was a twin of the operation, and it included model of battalions and ships that reflected the actual 
+    locations of the corresponding formations. Furthermore, synchronisation was 
+    implemented to give directives from the real system to control the operation 
+    flow and to update the physical twin state\cite{AMRC}.
+    In contrast, a digital twin is a virtual counterpart of a real system, which should 
+    be synchronized with a selected frequency and fidelity\cite{Review1}\cite{Review2}\cite{digitaltwinconsortium2022}.
 
-    Why do we assume this definition to be the best?
-Because it provides the highest abstraction level among the definitions of digital twins that we discovered during our literature analysis.
-The following is a poor example of abstraction taken from the initial definition of a digital twin from NASA's roadmap from 2010: `A digital twin is an integrated multi-physics, multi-scale, probabilistic simulation of a
-    vehicle or system that uses the best available physical models, sensor updates, fleet history, etc., to mirror the life of its flying twin~\cite{NASA}.'
-    The digital twins that we encounter nowadays don't typically fall under NASA's definition.
-We want to stress that NASA's definition of a  digital twin is accurate since digital twins are systems that are `context' centered.
-    Therefore, this definition is appropriate in the context of NASA's use case and is thus accurate, but the abstraction level is not sufficiently high to allow for a thorough understanding of digital twins.
+    The envision of digital twin emerged from Grieves'es conceptual model, which was called mirrored spaces model in 2002~\cite{Originsofdigitaltwinconcept},
+    and later referenced in 2005 journal article~\cite{2005JournayArticle}. 
+    Furthermore, he introduced the information mirroring model, which was his ideal product lifecycle management tool with only one goal. 
+    The goal was to gather as much as  information about the real system to minimize the waste of system's sources such as energy, 
+    time and material. Initially this model had four main parts with real system, 
+    virtual system, connection between the real and virtual system and virtual simulations\cite{GrievesPLMBook}. 
+    Later, Grieves removed the latter, in order to simplify the model\cite{Originsofdigitaltwinconcept}.Furthermore, after co-authoring with the Vicker's in 2010, 
+    Grieves decided to use the NASA invented Digital Twin word, instead of information mirroring model\cite{Originsofdigitaltwinconcept}.
 
-    In addition, we emphasize the significance of Grieves' 2006 description of digital twins in the PLM book,
-    which traces the origins of the concept. Although it featured the same components as a digital twin at the time, it was known as an Information Mirroring Model (IM)~\cite{GrievesPLMBook}. 
-    They decided to use NASA's Digital Twin rather than IM after co-authoring the article with Vickers.
+    %%//TODO MAYBE BETTER FORMATING HERE
+    Digital twins are complex evolvable systems, that are not only adapting to the changes in the environment, 
+    also are able to change their internal structure \cite{ZHANGUPDATEMETHOD}\cite{MobusSystemTheory}. 
+    To making sure that these complex evolvable systems can provide a certain quality is a mere challange whom wants to construct a digital twin.
 
-    \begin{figure}
-        \centering
-        \includegraphics[width =0.45\textwidth]{GrievesInformationMirroringModel.png}
-        \caption{Grieves Information Mirroring Model}\label{fig:GrievesInformationMirroringModel}
-       \cite{GrievesPLMBook}
-    \end{figure}
+    FELICE is a complex system which  addresses a critical problem in robotics which is the effective integration of human and robot abilities in a collaborative setting. 
+    This challenge requires the development of sophisticated algorithms and techniques that facilitate seamless communication, cooperation, and coordination between humans and robotic agents. 
+    By addressing this issue, FELICE tries to represent a significant advancement in the field of robotics and has the potential to enhance the effectiveness and efficiency of a wide range of 
+    human-robot collaborative tasks with the consideration of safety~\cite{FELICE}.
 
-    \subsection*{Real System}
+    Main purpose of this study is to identify the quality attributes and inspect several artifacts 
+    with these to evaluate the quality of the digital twin for the FELICE project, 
+    which is currently in the design phase~\cite{FELICE}. These artifacts included process videos showing the current 
+    assembly procedure, a scope definition, a requirements specification, a general and operational conceptual model, 
+    and a discrete event simulation module. We assessed the quality of these artifacts 
+    based on five crucial quality attributes: correctness, completeness, fidelity, efficiency, and evolvability.
 
-    The term `real system' in the context of digital twins refers to a system that is a tangible thing that has the characteristics of a system.
-Depending on the system's context, we can use black-box, gray-box, or white-box methodologies to study the system.
-    The use of various artifacts by Grieves in a system he referred to as `real space' can be seen in Figure~\ref{fig:GrievesInformationMirroringModel}.
-
-    \subsection*{Virtual System}
-    Virtual refers to an existence that exists in a computer system, as opposed to a physical system.
-Therefore, virtual systems are abstract systems, which are nothing but an abstraction of the real system.
-    The term `abstract systems' refers to systems that have had their set of variables and functions `abstracted' so that they may be computed by a solver, which in this case, a solver could be either the human brain or a computer.
-    Additionally, just because a system is an abstract system doesn't mean it lacks a physical body; rather, it is abstracted. 
-    Virtual systems can't exist on their own since, like abstract systems, they require a medium to exist.
-Computer systems, a higher system of virtual systems, are an ideal medium for virtual systems.
-
-    \subsection*{Connection Between the Real and Virtual System}
-    If we step back and observe the consortium's definition in Section~\ref{section:introduction}, which we assumed, was the best definition we could find, 
-    it mentions synchronization, fidelity and some specified frequency. As can be guessed these terms are attributes of the real-virtual connection.
-    Synchronization is used here instead of twinning, mirroring and connecting. 
-    Real-time is a time value, which is most of the time a constant value and defines the update frequency of the state of the virtual system of interest relative to the system of interest.
-    Fidelity is the degree of precision and accuracy of our digital twin, relative to the system of interest.
-    These words are highly dependent on the context of the digital twin.
     \subsection{Research objective}
@@
     \section{State of the art on quality}
-    In the Oxford English Dictionary, the word `quality' is described as a noun as well as an adjective. The Adjective form indicates, a high standard or excellence. 
-    For example, the phrase `quality products' implies that quality adds a high standard state to the product. 
-    There are several meanings for the noun, but the one that interests us in this situation is `the standard of something as measured against other things of a similar kind. \cite{OxfordDictionary}'
-    This definition shows the relativity of quality.
+    Oxford English Dictionary describes the word quality  either as a noun or as an adjective. 
+    The adjective form indicates, a high standard or excellence. For example, the phrase quality products implies 
+    that quality adds a high standard state to the product. There are several definitions which describes a quality 
+    as a noun,however the impactful definition is the quality as a standard of an entity which is measured against the 
+    different or the similar entities\cite{OxfordDictionary}.This definition clearly shows the relativity of quality.In addition, quality be defined 
+    as the degree to which a set of inherent properties of an entity fulfills the given requirements~\cite{ISO9000}.
 
-    According to ISO 9000:2015, quality is the degree to which a set of inherent characteristics of an object fulfills requirements~\cite{ISO9000}.
-Several words need to be expanded, to understand this definition.
-
-    First, the standard also explains characteristics as distinguishing features such as physical, sensory, behavioral, temporal, ergonomic and functional. 
-    Instead of an object, a system can be used for more generalization.
-    As for the requirements, the standard also explains as a requirement is a need or expectation that is stated, generally implied or obligatory.~\cite{ISO9000}
-
-    Thus, when these definitions are combined, we obtain the following: `Quality is a degree to which a set of inherent distinguishing features of a system fulfills a need or expectation that is stated, generally implied or obligatory'.
-    It should be highlighted that there are various quality definitions by so-called `Quality Gurus', but the authors decided to expand the standard definition of ISO 9000.
-
-    \subsection*{Product quality and Management}
+    \subsection{Product quality and Management}
     A product is a tangible or intangible system that satisfies the needs or wants of a customer. It could be a physical system like a car, or an abstract system, like a digital twin. 
@@
 
-    Quality management systems(QMS) are being used to plan and execute the organization's quality policies and goals. 
-    Examples of such systems can be a standard like ISO 9001 which can provide a framework for an organization, or a data-driven methodology 
-    such as Six Sigma to reduce defects and improve efficiency. These concepts are not new, for example, ISO 9001 standard has been established in 1987, 
-    and is still being regularly updated~\cite{ISO9001DebunkingtheMyth}.
+    Quality management systems(QMS) are functioning to plan and execute the organizations quality policies and goals. 
+    Examples of such systems can be a standard like ISO 9001 which can provide a framework for an organization, or a data-driven methodology such  as Six-Sigma to reduce defects and improve efficiency.
+    This concepts  are not new, for example ISO 9001 standard has been established in 1987, and still being regularly updated ~\cite{ISO9001DebunkingtheMyth}.
 
-    \subsection*{Software quality}
-    Software is a  virtual system, which has a set of instructions, data or programs used to perform a specific task. 
-    All virtual systems, which we described above, need a medium to live on, hence these systems can be found in a computer or other electronic device.  
-    Software quality according to IEEE 730-2014, is: 
-    `The degree to which a software product meets established requirements; however, 
-    quality depends upon the degree to which those established requirements accurately represent stakeholder needs, wants, and expectations'~\cite{IEE730-2014}. 
-    As can be seen, it's a generic explanation of a quality, which doesn't differ much from the explanation we gave above.
+    \subsection{Software quality}
+    Software is a combination of programs and data which can be used by the virtual 
+    systems as well as  a physical system like a computer system. In contrast a hardware 
+    is a physical subsystem of a computer system\cite{OxfordDictionary}.
 
-    Software quality management techniques come from already used manufacturing techniques in the industries.
-    For example, the quality assurance that we mentioned above, also has been used as a software quality management activity with some differences. 
-    In manufacturing, products will never exactly meet a specification, due to errors in the machining so there should be some tolerance for the manufacturing. 
-    But in the software systems, or more precisely in the virtual systems, it's most of the time, not the case. 
-    Also its nearly impossible to conclude that, the software product fully meets its specifications\cite{SoftwareEngineering}.
+    Software Quality is determined by how well software fulfill the requirements that were set. However, those requirements  
+    not always reflect what the stakeholders actually need, hence the quality depends how accurately this requirements were set \cite{IEE730-2014}. 
+    As a result, functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability 
+    and portability are the standartized  eight attributes that measure software quality \cite{ISO/IEC:25010}.
 
-    According to ISO/IEC:25010:2011, there are eight software quality attributes. Functional Suitability, 
-    Performance efficiency, compatibility, usability, reliability, security, maintainability and portability.\cite{ISO/IEC:25010}
-    Of course, not all aspects can be inspected and the person, who is responsible for the quality of the product, should choose the critical aspects of the software product and further the process according to that decision.
+    Software quality management techniques comes from already used manufacturing techniques in the  industries.
+For example the  product quality assurance has been used as a software quality management activity with some modifications.
+For example, in the manufacturing, products will never exactly meet a specification, due to errors in the machining which results in some tolerance area.
+But in the software systems, or more precise in the virtual systems, it's most of the time not the case.
+Also its nearly imposible to conclude that,
+    the software product is fully meet its speficiations. 
+    Hence, most of the quality assesments are subjective process and as a result, the quality attributes should be inspected subjectively \cite{SoftwareEngineering}.
 
-    \subsection*{Simulation Quality}
-    Simulation models are not merely virtual systems; they are also abstracted systems, which are nothing more than imitations or, to be more precise, abstractions of real systems. 
-    We are simulating something every day when we are trying to predict the future outcome or abstractly thinking about the past state of some occurred event. 
-    An important element to remember is that we mentally model the event before executing the simulation. However, most of the simulation processes we see today, 
-    are computer-based, with software programs.
-These programs include ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic}, as examples.
-Consequently, the idea of simulation software programs emerges.
+    \subsection{Simulation Quality}
+    Simulation models are not merely virtual systems; 
+    they are also abstracted systems, which are nothing more than imitations or, 
+    to be more precise, abstractions of real systems. 
+    We are simulating something every day when we are trying 
+    to predict the future outcome or abstractly thinking about the past state of some occurred event. 
+    An important element to remember is that we mentally model the 
+    event before executing the simulation. However, most of the simulation processes we see today, 
+    are computer-based, with software programs. These programs 
+    include ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and 
+    AnyLogic\cite{AnyLogic}, as examples. Consequently, the idea of simulation software programs emerges.
 
@@
 
-    \subsection*{Digital twin quality}
+    \subsection{Digital twin quality}
     To analyze the state of the digital twin quality, a literature analysis was executed. 
@@
 
-    \subsection*{Literature Result}
+    \subsubsection*{Literature Result}
     The search term `digital twin quality' initially yielded 41 results on Google Scholar and three on Scopus. 
@@
 
-    \subsection*{Findings}
+    \subsubsection*{Findings}
 
@@
 
-    \section{Initial approach in the FELICE project}
-    FELICE addresses a critical problem in robotics which is the effective integration of human and robot abilities in a collaborative setting.
-This challenge requires the development of sophisticated algorithms and techniques that facilitate seamless communication,
-    cooperation, and coordination between humans and robotic agents. By addressing this issue, FELICE tries to represent a 
-    significant advancement in the field of robotics and has the potential to enhance the effectiveness and efficiency of a wide range of human-robot collaborative tasks with the consideration of safety~\cite{FELICE}.
-
-    In the present study, we inspected several artifacts to evaluate the quality of the digital twin for the FELICE project, which is currently in the design phase.
-These artifacts included process videos showing the current assembly procedure, a scope definition, a requirements specification, a general and operational conceptual model,
-    and a discrete event simulation module. We assessed the quality of these artifacts based on four crucial quality attributes: correctness, completeness, fidelity, efficiency, and evolvability.
+    \section{Digital Twin Quality Attributes and Inspection Results}
 
@@
     \subsection{Second criterion: Completeness}
-    According to the Oxford Dictionary, `complete'  can function as an adjective, attribute, or verb with an object\cite{OxfordDictionary}. When used as an adjective, it describes something 
+    According to the Oxford Dictionary, complete can be an adjective, an attribute, or  a verb with an object\cite{OxfordDictionary}. When used as an adjective, it describes something 
     as having all the necessary or appropriate parts. To evaluate the completeness of a digital twin, 

### 2023-02-28 manuscripts/paper-1/main.tex
Literature Research is revised

@@
 \usepackage{verbatim}
+\usepackage{cite}
 
@@
     In contrast, a digital twin is a virtual counterpart of a real system, which should 
-    be synchronized with a selected frequency and fidelity\cite{Review1}\cite{Review2}\cite{digitaltwinconsortium2022}.
+    be synchronized with a selected frequency and fidelity\cite{Review1,Review2,digitaltwinconsortium2022}.
 
@@
 
-    %%//TODO MAYBE BETTER FORMATING HERE
-    Digital twins are complex evolvable systems, that are not only adapting to the changes in the environment, 
-    also are able to change their internal structure \cite{ZHANGUPDATEMETHOD}\cite{MobusSystemTheory}. 
-    To making sure that these complex evolvable systems can provide a certain quality is a mere challange whom wants to construct a digital twin.
+    Digital twins are highly intricate and adaptable systems that possess the capability to not only respond to environmental 
+    changes but also modify their internal structure \cite{ZHANGUPDATEMETHOD,MobusSystemTheory}. Therefore, ascertaining a 
+    requisite level of quality for the construction of a digital twin is an arduous undertaking.
 
@@
     assembly procedure, a scope definition, a requirements specification, a general and operational conceptual model, 
-    and a discrete event simulation module. We assessed the quality of these artifacts 
-    based on five crucial quality attributes: correctness, completeness, fidelity, efficiency, and evolvability.
+    and a discrete event simulation module. We assessed the quality of these artifacts based on five crucial quality attributes: correctness, completeness, fidelity, efficiency, and evolvability.
 
-    \subsection{Research objective}
-    Find an approach to assess the quality of Digital twins~\cite{Jones2020}
+    %%
+    %%\subsection{Research objective}
+    %%Find an approach to assess the quality of Digital twins~\cite{Jones2020}
 
-    \subsection{Research question}\label{section: Research Questions}
-    What is the quality of digital twins?
-    What is the state art of digital twin quality?
+    %%\subsection{Research question}\label{section: Research Questions}
+    %%What is the quality of digital twins?
+    %%What is the state art of digital twin quality?
 
-    \subsection{Research methodology}
-    TODO
+    %%\subsection{Research methodology}
+    %%TODO
 
@@
     \subsection{Simulation Quality}
-    Simulation models are not merely virtual systems; 
-    they are also abstracted systems, which are nothing more than imitations or, 
-    to be more precise, abstractions of real systems. 
-    We are simulating something every day when we are trying 
-    to predict the future outcome or abstractly thinking about the past state of some occurred event. 
-    An important element to remember is that we mentally model the 
-    event before executing the simulation. However, most of the simulation processes we see today, 
-    are computer-based, with software programs. These programs 
-    include ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and 
-    AnyLogic\cite{AnyLogic}, as examples. Consequently, the idea of simulation software programs emerges.
+    Simulation models are not merely virtual systems; they are also abstracted systems, 
+    which are nothing more than imitations or, to be more precise, abstractions of the real systems. 
+    In fact, everyday, simulation of the real systems occurs in the human brain when prediction of the future outcome or  about the 
+    past state of some occured event required\cite{MobusSystemTheory}. However, most of the simulation processeses are computer 
+    based with software programs. Consequently, the idea of simulation software programs emerges. 
+    For example, ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} are examples of these simulation software programs.
 
-    Validation and verification can be used to evaluate the quality characteristics of the simulation model \cite{StewartSimulation} \cite{VerificationValidationSergent} \cite{OsmanBalci}. 
-    Validation is the process of evaluating the simulation quality of the model in comparison to the real system from the perspective of the model's intended applications. 
-    On the other hand, verification is a procedure to evaluate a simulation model's implementation and its associated data concerning the conceptual description and specifications of the model developer.
+    Validation and verification is used to evaluate the quality characteristics of the simulation 
+    model \cite{StewartSimulation,VerificationValidationSergent,OsmanBalci}. 
+    Validation is the process of evaluating the simulation quality of the model in comparison to 
+    the real system from the perspective of the model's intended applications.
+    On the other hand, verification is a procedure to 
+    evaluate a simulation model's implementation and its associated 
+    data concerning the conceptual description and specifications of the 
+    model developer\cite{StewartSimulation,VerificationValidationSergent}.
 
@@
     \subsubsection*{Literature Search Methodology}
-    Google Scholar (GS), Scopus (SCP) and Research Rabbit (RR) tools are used to fulfill our requirements for the literature review.
-Since there is a great number of digital twin publications in academics,
-    narrowing the research is necessary, so the following algorithm with two levels of filtering will be applied.
+    To conduct a thorough literature review on digital twin publications, tools such as Google Scholar and Scopus are utilized.
+Due to the vast amount of available literature, it is necessary to narrow down the scope of the research.
+    Therefore, a multi-level filtering algorithm is employed to refine the search results.
 
-    Initial filtering has been done with the following criteria
+    The first level of filtering for the literature review on digital twin publications involves specific criteria. These include that dissertations must be written in English and 
+    published in a journal or conference, and that the search term must be an exact match. To execute this initial filtration, 
+    the following queries are used for Google Scholar and Scopus respectively: "search term" and ALL ("digital twin quality") AND (LIMIT-TO (LANGUAGE, "English")).
+
+    After the initial filtering, a second level of manual investigation is necessary. The following criteria are used for this level of filtering:    
     \begin{itemize}
-        \item  Dissertations should be written in English and published in a journal/conference.
-        \item  Search term should be exactly searched
-    \end{itemize}
-    Filtering query calls for the GS and SCP are the following
-    \begin{itemize}
-        \item Google Scholar = `search term'
-        \item Scopus = ALL (`digital twin quality') AND (LIMIT-TO (LANGUAGE, `English'))
-    \end{itemize}
-    After the initial filtration, the second filtering which is a manual investigation should occur with the following filtering criteria:
-    \begin{itemize}
-        \item  Remove Duplications
-        \item  Remove the dissertations which are not English
-        \item  Proper literature review should be present in the selected dissertation
-        \item  Abstract and conclusion should be relevant to the search term
+        \item  Eliminating duplicates
+        \item  Removing dissertations that are not in English
+        \item  Ensuring that selected dissertations have a proper literature review
+        \item  Ensuring that abstract and conclusion are relevant to the search term
     \end{itemize}
@@
 
-    \subsubsection*{Literature Result}
-    The search term `digital twin quality' initially yielded 41 results on Google Scholar and three on Scopus. 
-    After the second filtering stage, six duplicate dissertations were removed, along with ten dissertations that were not in English.
-As a result, only nine dissertations passed all the criteria and were inspected, while the remainder were rejected.
+    \subsubsection*{Literature Search Result}
+    The search for "digital twin quality" initially resulted in 41 hits on Google Scholar and 3 on Scopus. 
+    After the second level of filtering, 6 duplicate dissertations were removed and 10 dissertations that were not in English were also eliminated. 
+    This left only 9 dissertations that met all the criteria and were reviewed.
 
-    The search term `digital twin verification' initially yielded, resulting in nineteen hits on Google Scholar and zero on Scopus.
-After the second filtering stage, one duplicate dissertation was removed, along with two dissertations that were not in English.
-    As a result, all dissertations were rejected.
+    The search for "digital twin verification" initially resulted in 19 hits on Google Scholar and none on Scopus. 
+    After the second level of filtering, one duplicate dissertation was removed and two dissertations that were not in 
+    English were also eliminated. As a result, all dissertations were rejected.
 
-    The search term `digital twin validation' was filtered initially, resulting in fifty-nine hits on Google Scholar and zero on Scopus.
-After the second filtering stage, four duplicate dissertations were removed, along with 4 dissertations that were not in English.
-    As a result, eight dissertations passed all the criteria and were inspected while the remainder were rejected.
+    The search for "digital twin validation" initially resulted in 59 hits on Google Scholar and none on Scopus. 
+    After the second level of filtering, 4 duplicate dissertations were removed and 4 
+    dissertations that were not in English were also eliminated. This left only 8 dissertations that met all the criteria and were reviewed.
 
-    \subsubsection*{Findings}
+    After a thorough review of 17 research papers, a number of significant findings were revealed.
 
-    The findings are the following;
-    \begin{itemize}
-        \item Shcherba et al.
-center their attention on the model quality, which is an observation for a digital twin subsystem.
-Despite being a crucial component of the digital twin, models alone cannot be used to assess the quality of the digital twin~\cite{Shcherba}.
-        \item A consistency evaluation approach for digital twin models was developed by He Zhang et al. and can be used to assess the quality of the models. Additionally, 
-        the authors discuss crucial ideas like consistency between real and virtual systems and ultra-fidelity models.
-The improvement of the service component is the primary emphasis of this article.
-Tao's five-dimensional digital twin concept includes this component~\cite{ZHANGEVALUATIONMETHOD}.
-        \item He Zhang et al.
-introduces the updating method for digital twin models in yet another insightful article.
+    First, it was noted that Shcherba et al.  focus on the importance of model quality as an observation for a digital twin subsystem. 
+    However, they acknowledged that the quality assessment of the digital twin cannot solely rely on models~\cite{Shcherba}.
+
+    He Zhang et al.  developed a consistency evaluation approach for digital twin models, which can be used to assess their quality. 
+    The authors also discuss essential concepts, such as consistency between real and virtual systems and ultra-fidelity models. 
+    This article emphasizes the improvement of the service component of the digital twin~\cite{ZHANGEVALUATIONMETHOD}.
+
+    He Zhang et al. introduced the updating method for digital twin models in yet another insightful article.
     Once more, the accuracy and coherence of the model concepts were addressed~\cite{ZHANGUPDATEMETHOD}.
-        \item Selch et al.
-work is the only one that discusses the quality of the digital twin.
-The paper presents a machine-learning approach based on Bayesian networks to track the quality of the digital twin.
-The unique aspect of this study is that the author, rather than just analyzing the digital twin as a single system, determines the contributions of subsystems to forecast the overall quality of the digital twin.
-The digital couplings, which are linkages between the subsystems, are also mentioned by Selch et al.
-as a source of extra uncertainty.
-        Since only one digital twin has been used in practice, multiple subsystem digital twins have not been validated~\cite{QualityMonitoringofCoupledDigitalTwins}.
-        \item The stability of the digital twin models was assessed using the Kolmogorov-Smirnov statistical test, which measures the degree of similarity between the probability distribution of the model's predictions and the distribution of the actual data~\cite{RadarDigitalTwin}.
-        \item Edward Y.
+
+    Selch et al.  present a machine-learning approach based on Bayesian networks to track the quality of the digital twin. 
+    The unique aspect of this study is that the authors determine the contributions of subsystems to forecast the overall quality of the digital twin, 
+    rather than just analyzing it as a single system. The digital couplings, which are linkages between the subsystems, are also identified as a source of extra uncertainty. 
+    However, since only one digital twin has been used in practice, multiple subsystem digital twins have not been validated~\cite{QualityMonitoringofCoupledDigitalTwins}.
+
+    Additionally, the stability of digital twin models was assessed by another study using the Kolmogorov-Smirnov statistical test, 
+    which measures the degree of similarity between the probability distribution of the model's predictions and the distribution of the actual data~\cite{RadarDigitalTwin}.
+
+    Edward Y.
 Hua et al.
@@
 To address these challenges, the authors propose a digital-twin model validation framework.
-Additionally, the paper highlights three areas for future research,
-        including uncertainty and sensitivity analysis, model validation of system-of-systems, and combining expert knowledge and collected data~\cite{ValidationofDigitalTwins}.
-        \item Shotaro Hamato et al.
-demonstrated real-time anomaly detection was successfully demonstrated using the Unscented Kalman Filter with the digital twin model, but determining the appropriate threshold for anomaly detection remains an issue~\cite{JapeneseKalmanFilterCorrectness}.
-    \end{itemize}
+The paper also highlights three areas for future research,
+    including uncertainty and sensitivity analysis, model validation of system-of-systems, and combining expert knowledge and collected data ~\cite{ValidationofDigitalTwins}.
+
+    Finally, Shotaro Hamato et al.  demonstrated successful real-time anomaly detection using the Unscented Kalman Filter with the digital twin model. 
+    However, determining the appropriate threshold for anomaly detection remains an issue~\cite{JapeneseKalmanFilterCorrectness}.
+
+    Overall, these studies provide valuable insights into various aspects of digital twin quality assessment, 
+    including model consistency, stability, and validation, as well as machine learning-based approaches and real-time anomaly detection. 
+    However, the identified open problems, including modeling realism, data uncertainty, system dynamics, use-case alignment, and reporting invalid modes, 
+    call for further research in the field to improve the quality and reliability of digital twins. Moreover, 
+    the lack of well-defined quality parameters for digital twins poses a significant challenge in ensuring their quality,
+    which necessitates the development of appropriate quality metrics and standards for digital twins.
 

### 2023-03-01 manuscripts/paper-1/main.tex
Method added, but must be improved

@@
 
-    \section{Digital Twin Quality Attributes and Inspection Results}
+    \section{Methods}
+    Based on the theoretical background, we have opted for a methodology that comprises two components: 
+    \begin{itemize}
+        \item Manual Reviews
+        \item Utilization of quality standards in conjunction with dictionary definitions of the quality attributes that will be employed
+    \end{itemize}
 
-    \subsection{First criterion: Correctness}
+    \subsection{Manual Reviews}
+    We presented the results of the comprehensive manual reviews 
+    conducted to evaluate the quality of digital twin artifacts during 
+    the initial stages of the FELICE project. The current stage of review 
+    encompasses five key artifacts, including process videos displaying the 
+    current assembly procedure without an adaptive workstation and cobot, 
+    a scope definition outlining the objects on the shop floor requiring tracking or twinning, 
+    a requirements specification summarizing functional and non-functional requirements for the digital twin, 
+    a general and an operational conceptual model elucidating the high-level structure of the assembly procedure, 
+    and a discrete event simulation module that implements the structures prescribed by the conceptual models.
+
+    \subsection{Quality Standards and Dictionary}
+    We consolidated our findings from various standards, including ISO/IEC:25010, 
+    IEE730-2014, ISO9000, ISO9001, and the Oxford dictionary, in order to establish clear 
+    and precise definitions for the attributes used in assessing digital twin quality.\cite{ISO9000,ISO90012015,ISO/IEC:25010,IEE730-2014,OxfordDictionary}.
+
+    \section{Digital Twin Quality Attributes and Results}
+
+    \subsection*{First criterion: Correctness}
     Correctness is a  derived word from the adjective correct, which means that something is error-free regarding a fact or truth~\cite{OxfordDictionary}. 
@@
 
-    \subsection{Second criterion: Completeness}
-    According to the Oxford Dictionary, complete can be an adjective, an attribute, or  a verb with an object\cite{OxfordDictionary}. When used as an adjective, it describes something 
+    \subsection*{Second criterion: Completeness}
+    According to the Oxford Dictionary, complete can be an adjective, an attribute, or  a verb with an object\cite{OxfordDictionary}. 
+    When used as an adjective, it describes something 
     as having all the necessary or appropriate parts. To evaluate the completeness of a digital twin, 
@@
 
-    \subsection{Third criterion: Fidelity}
+    \subsection*{Third criterion: Fidelity}
     The concept of fidelity has garnered significant attention in recent years and continues to be an important area of research in digital twins.
@@
     Low-fidelity indicates a simplified representation, while high-fidelity refers to an accurate and detailed representation of the real system.
-    This quality attribute plays a crucial role in evaluating the effectiveness of digital twins in accurately capturing the behavior and properties of real-world systems. 
+    This quality attribute plays a crucial role in evaluating the effectiveness of digital twins in accurately capturing the behavior and properties 
+    of real-world systems.
+
     \subsubsection*{Fidelity vs Correctness}
-    Correctness is a functional quality attribute, which assesses the behavior of the digital twin systems, by how accurately the results with the given precision match the behavior of the real system or more
+    Correctness is a functional quality attribute, which assesses the behavior of the digital twin systems, 
+    by how accurately the results with the given precision match the behavior of the real system or more
     specifically outputs with the same given inputs. 
@@
 
-    \subsection{Fourth criterion: Efficiency}
+    \subsection*{Fourth criterion: Efficiency}
     Efficiency refers to the quality of being efficient, and efficiency can be explained as achieving maximum productivity with minimum wasted effort or expense. 
@@
 
-    \subsection{Fifth criterion: Evolvability}
+    \subsection*{Fifth criterion: Evolvability}
     A system's capability to enhance its suitability to its environment through alterations to both its internal and functional structure is referred to as evolvability.
@@
     \begin{figure}[htbp]
-        \includegraphics[width=\columnwidth]{quality_inspection_results.png}
+        \includegraphics[scale=0.75]{quality_inspection_results.png}
         \caption{Overall Quality Inspection Results}
@@
     \end{figure}\begin{figure}[htbp]
-        \includegraphics[width=\columnwidth]{quality_inspection_results_with_artifacts.png}
+        \includegraphics[scale = 0.45]{quality_inspection_results_with_artifacts.png}
         \caption{ Quality Inspection Results Categorized with Artifacts}
@@
     which is susceptible to human error and inspector bias.
+
+    \section{Discussion}
 

### 2023-03-01 manuscripts/paper-1/main.tex
Section 1-2 Finished. 3-4-5 Remaining

@@
-%%\documentclass[9pt,conference]{IEEEtran}
 \documentclass{llncs}
@@
 
-    \subsection{Future approach in the FELICE project}
     \label{section:framework_1}
@@
 
-    \section{Conclusion}~\label{section:conclusion}
     The success of the digital twin system depends on its quality, which requires careful evaluation based on several crucial quality attributes.

### 2023-03-01 manuscripts/paper-1/main.tex
Method is done. 4-5 Missing

@@
 
+    Various validation and verification techniques can be employed, which can be broadly categorized into six areas: informal, static, dynamic, symbolic, constraint, and formal techniques \cite{balcicategories}\cite{balcitechniques}.
+Formal techniques involve mathematical formality, whereas informal techniques rely on human intervention and reasoning.
+Although mathematical techniques are more precise, informal techniques
+    are more commonly used \cite{balcicategories}.
+Also, the use of informal techniques does not imply a lack of structure, but rather a reliance on human expertise and interpretation \cite{balcitechniques}.
+
     \subsection{Digital twin quality}
@@
 
-    \section{Methods}
-    Based on the theoretical background, we have opted for a methodology that comprises two components: 
-    \begin{itemize}
-        \item Manual Reviews
-        \item Utilization of quality standards in conjunction with dictionary definitions of the quality attributes that will be employed
-    \end{itemize}
+    \section{Methods and Artifacts}
+    The methodology consists of two components:Manual reviews of the artifacts, expand and clarify the digital twin quality attributes with the use of quality standards along with corresponding dictionary definitions.
 
-    \subsection{Manual Reviews}
-    We presented the results of the comprehensive manual reviews 
-    conducted to evaluate the quality of digital twin artifacts during 
-    the initial stages of the FELICE project. The current stage of review 
-    encompasses five key artifacts, including process videos displaying the 
-    current assembly procedure without an adaptive workstation and cobot, 
-    a scope definition outlining the objects on the shop floor requiring tracking or twinning, 
-    a requirements specification summarizing functional and non-functional requirements for the digital twin, 
-    a general and an operational conceptual model elucidating the high-level structure of the assembly procedure, 
+    \subsection{Artifacts}
+    The current stage of review encompasses five key artifacts, including process videos displaying the current assembly procedure without an adaptive workstation and cobot, a scope definition outlining the objects on the shop floor requiring tracking or twinning, a requirements specification summarizing functional and non-functional requirements for the digital twin, a general and an operational conceptual model elucidating the high-level structure of the assembly procedure,
     and a discrete event simulation module that implements the structures prescribed by the conceptual models.
 
-    \subsection{Quality Standards and Dictionary}
+    \subsubsection*{Process Videos}
+    Project partner provided three videos initially to explain the manual assembly procedures performed at each of the three workstations. From the videos,  
+    the sequence of assembly steps were extracted  at least for one product variant.
+The tools and the parts needed for each assembly operation was observed.
+Additionally, an approximate duration of each assembly step were estimated, and some ergonomic characteristics of each operation was derived.
+    The derivable ergonomic characteristics mainly included the poses and motions performed by the operators.
+
+    \subsubsection*{Scope Definition}
+    To better understand the context and focus of the digital twin, 
+    project partner used a methodology based on hierarchical task analysis and the process videos. 
+    This resulted in a scope definition that identified entities to be twinned, entities to be tracked, and important areas in the scene. 
+    Entities to be twinned needed to be represented accurately in the simulation models, including their position, pose, speed, fatigue, and other state variables. 
+    Entities to be tracked, on the other hand, only required position information.
+The scope definition was based on a floor plan of the production facility, with the three workstations marked as gray rectangles.
+    The human workers, cobot, and adaptive workstation were identified as entities to be twinned, and therefore required accurate representation, 
+    monitoring, and simulation. Other entities, such as an AGV, carts with doors, and screwdrivers used for assembly operations, were designated as entities to be tracked.
+    \subsubsection*{Requirements Specification}
+    Each requirement for the digital twin was defined with a unique ID, a natural language description, an origin, a category, a priority, and a rationale.
+The ID was used as a reference point for other project artifacts, while the specification described the requirement in a way that allowed for testing of the digital twin implementation.
+The origin of the requirement was noted to identify the project partner responsible for its creation.
+The category distinguished between functional and non-functional requirements, as well as constraints and standards.
+The priority of each requirement was classified into four levels
+    (must-, should-, could-, and would-have) to help prioritize development efforts. 
+    Finally, the rationale provided a clear explanation for each requirement's inclusion in the specification.
+    \subsubsection*{Conceptual Model}
+    The conceptual model was comprised of two parts:  a general conceptual model and an operational conceptual model.
+Both models provided a description of the assembly line processes, but the operational conceptual model focused on the specific steps of the assembly process, while the general conceptual model focused on higher-level processes and workflows.
+    The conceptual model was represented using a general flow chart notation that distinguished between a root node, activity nodes, and decision nodes.
+    The operational conceptual model consisted of three spreadsheets, each displaying the sequence of assembly operations performed at one workstation.
+The assembly operations were divided into macro- and micro-operations, with each macro-operation referring to one part of the final product being assembled, and the micro-operations referring to the individual steps needed to complete the respective macro-operation.
+    \subsubsection*{Simulation Model}
+    The discrete event simulation model consisted of seven sections, including two animation sections, two input sections, one output section, one process logic section, and a database section.
+The animation sections provided a two-dimensional and a three-dimensional representation of the system, which aided in understanding the simulation and for debugging purposes.
+The input sections allowed for the management of inputs to the simulation model, and the output section displayed summary performance indicators about the simulation run.
+    The process logic section contained the process building blocks, such as queues and assembly operations. The database section provided an interface to data sources and sinks.
+
+    \subsection{Digital Twin Quality Attribute Identification}
     We consolidated our findings from various standards, including ISO/IEC:25010, 
-    IEE730-2014, ISO9000, ISO9001, and the Oxford dictionary, in order to establish clear 
-    and precise definitions for the attributes used in assessing digital twin quality.\cite{ISO9000,ISO90012015,ISO/IEC:25010,IEE730-2014,OxfordDictionary}.
+    IEE730-2014, ISO9000, ISO9001, as well as consulted the  Oxford dictionary to synthesize our findings\cite{ISO9000,ISO90012015,ISO/IEC:25010,IEE730-2014,OxfordDictionary}..
+
+    %%Based on this analysis, we established unambiguous and well-defined definitions for quality attributes of the digital twin. These definitions were subsequently utilized in our manual reviews.
+    \subsection{Manual Artifact Reviews and Evaluation}
+    During the initial stages of the project, when the target system was not yet available, there was a lack of observable data about system behavior that could be utilized for validation. 
+    Instead, informal and potentially incomplete, inconsistent, or incorrect system descriptions had to be relied upon.
+Therefore, manual reviews were deemed the most suitable tool to account for the characteristics
+    of this situation. After doing manual reviews, the results were manually evaluated and categorized with the identified digital twin quality attributes.
 
@@
 
+    \subsection{Manual Review Result}
+
+    \subsection{Quality Inspection with Quality Attributes}
+
     As can be seen in Figures ~\ref{fig:QualityInspectonResults} and ~\ref{fig:QualityInspectonResultsWithArtifacts}, based on our inspection of the given artifacts,

### 2023-03-01 manuscripts/paper-1/main.tex
Method is done, 4-5 missing

@@
     as the degree to which a set of inherent properties of an entity fulfills the given requirements~\cite{ISO9000}.    
-
     \subsection{Product quality and Management}
@@
     Examples of such systems can be a standard like ISO 9001 which can provide a framework for an organization, or a data-driven methodology such  as Six-Sigma to reduce defects and improve efficiency.
-    This concepts  are not new, for example ISO 9001 standard has been established in 1987, and still being regularly updated ~\cite{ISO9001DebunkingtheMyth}.
-
+    This concepts  are not new, for example ISO 9001 standard has been established in 1987, and still being regularly updated ~\cite{ISO90012015}. 
     \subsection{Software quality}
@@
 Also, the use of informal techniques does not imply a lack of structure, but rather a reliance on human expertise and interpretation \cite{balcitechniques}.
-
     \subsection{Digital twin quality}
@@
     \end{itemize}
-
     If an interesting dissertation(s) would be found during the reading, it will be checked again with the initial filter.
-
     \subsubsection*{Literature Search Result}
@@
     which necessitates the development of appropriate quality metrics and standards for digital twins.
+    \subsection{Digital Twin Quality Attributes}
+    We consolidated our findings from various standards, including ISO/IEC:25010, IEE730-2014, ISO9000, ISO9001, as well as consulted the  Oxford dictionary to synthesize our findings\cite{ISO9000,ISO90012015,ISO/IEC:25010,IEE730-2014,OxfordDictionary}.
 
-    \section{Methods and Artifacts}
-    The methodology consists of two components:Manual reviews of the artifacts, expand and clarify the digital twin quality attributes with the use of quality standards along with corresponding dictionary definitions.
+    \textbf{Correctness} is a  derived word from the adjective correct, which means that something is error-free in regard to fact or truth.
+In the context of the digital twins, our fact or truth is a real system hence, correctness is a grade of quality, that indicates an error between the real system and a digital twin system.
+    Meanwhile, the quality of being correct is described by the term accuracy \cite{OxfordDictionary}.
 
+    \textbf{Completeness} is a derived word from the word complete, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
+    The adjectival form of complete is a state of having all the neccesary or appropriate parts\cite{OxfordDictionary}.
+
+    \textbf{Fidelity}
+    Fidelity refers to the degree of exactness with which the real system is copied and represented.Low-fidelity indicates a simplified representation, 
+    while high-fidelity refers to an accurate and detailed representation of the real system \cite{Review2}. 
+    The concept of fidelity has garnered significant attention in recent years and continues to be an important area of research in digital twins\cite{Review2}\cite{Review1}.
+
+    \textbf{Efficiency}
+    Efficiency refers to the  quality of  being efficient, and efficient is achieving
+    maximum productivity with minimum wasted effort or expense. The concept of efficiency is tightly coupled to productivity, which  refers to a quality of being productive,
+    also  the word productive can be explained as producing or able to produce large amounts of goods\cite{OxfordDictionary}.  
+    For example time efficiency indicates that,  with the less amount of time as an input, more output with the minimum 
+    waste during the process is desired . Goods of the  digital twin is nothing but an information, which Grieves first 
+    indicated with this Information Mirror Model\cite{GrievesPLMBook}.
+
+    \textbf{Evolvability}
+    A system's capability to enhance its suitability to its environment through alterations to both its internal and functional 
+    structure is referred to as evolvability\cite{MobusSystemTheory}. Another term used to describe the response to changes in the environment is adaptability.
+    However, this concept differs from evolvability in that it only affects a system's internal or functional structure temporarily. 
+    For instance, a digital twin, which is a virtual system, can be designed to be more flexible and scalable, 
+    allowing for easy updates and the addition of new features. 
+    These updates and new features will result in definite changes to the structure of the system. 
+    On the other hand, a responsive web design is an adaptable system, capable of adjusting its size and layout 
+    depending on the user's hardware. As we have seen in \cite{ZHANGUPDATEMETHOD}, the update method shows that digital twins are evolvable systems, 
+    hence this attribute should be considered when the digital twin's quality is inspected. To assess the evolvability attribute, scalability analysis,
+    reusability analysis, modifiability analysis, testability analysis, and maintainability analysis can be performed. 
+    \section{Artifacts and Methods}
+    The used methodology consists of manual artifact reviews and evaluation of the results according to the digital twin quality attributes.    
     \subsection{Artifacts}
@@
 
-    \subsubsection*{Process Videos}
+    \textbf{Process Videos:}
     Project partner provided three videos initially to explain the manual assembly procedures performed at each of the three workstations. From the videos,  
@@
 
-    \subsubsection*{Scope Definition}
+    \textbf{Scope Definition:}
     To better understand the context and focus of the digital twin, 
@@
     monitoring, and simulation. Other entities, such as an AGV, carts with doors, and screwdrivers used for assembly operations, were designated as entities to be tracked.
-    \subsubsection*{Requirements Specification}
-    Each requirement for the digital twin was defined with a unique ID, a natural language description, an origin, a category, a priority, and a rationale.
+
+    \textbf{Requirements Specification} for the digital twin was defined with a unique ID, a natural language description, an origin, a category, a priority, and a rationale.
 The ID was used as a reference point for other project artifacts, while the specification described the requirement in a way that allowed for testing of the digital twin implementation.
@@
     Finally, the rationale provided a clear explanation for each requirement's inclusion in the specification.
-    \subsubsection*{Conceptual Model}
-    The conceptual model was comprised of two parts:  a general conceptual model and an operational conceptual model.
+
+    \textbf{Conceptual Model} was comprised of two parts:  a general conceptual model and an operational conceptual model.
 Both models provided a description of the assembly line processes, but the operational conceptual model focused on the specific steps of the assembly process, while the general conceptual model focused on higher-level processes and workflows.
-    The conceptual model was represented using a general flow chart notation that distinguished between a root node, activity nodes, and decision nodes.
+    The general conceptual model was represented using a general flow chart notation that distinguished between a root node, activity nodes, and decision nodes.
     The operational conceptual model consisted of three spreadsheets, each displaying the sequence of assembly operations performed at one workstation. 
-The assembly operations were divided into macro- and micro-operations, with each macro-operation referring to one part of the final product being assembled, and the micro-operations referring to the individual steps needed to complete the respective macro-operation.
-    \subsubsection*{Simulation Model}
-    The discrete event simulation model consisted of seven sections, including two animation sections, two input sections, one output section, one process logic section, and a database section.
+    The assembly operations were divided into macro- and micro-operations, with each macro-operation referring 
+    to one part of the final product being assembled, and the micro-operations referring to the individual steps needed to complete the respective macro-operation.
+
+    \textbf{Discrete Event Simulation Model} consisted of seven sections, including two animation sections, two input sections, one output section, one process logic section, and a database section.
 The animation sections provided a two-dimensional and a three-dimensional representation of the system, which aided in understanding the simulation and for debugging purposes.
@@
 
-    \subsection{Digital Twin Quality Attribute Identification}
-    We consolidated our findings from various standards, including ISO/IEC:25010, 
-    IEE730-2014, ISO9000, ISO9001, as well as consulted the  Oxford dictionary to synthesize our findings\cite{ISO9000,ISO90012015,ISO/IEC:25010,IEE730-2014,OxfordDictionary}..
-
-    %%Based on this analysis, we established unambiguous and well-defined definitions for quality attributes of the digital twin. These definitions were subsequently utilized in our manual reviews.
-    \subsection{Manual Artifact Reviews and Evaluation}
+    \subsection{Manual Artifact Reviews and Evoluation}
     During the initial stages of the project, when the target system was not yet available, there was a lack of observable data about system behavior that could be utilized for validation. 
     Instead, informal and potentially incomplete, inconsistent, or incorrect system descriptions had to be relied upon.
-Therefore, manual reviews were deemed the most suitable tool to account for the characteristics
-    of this situation. After doing manual reviews, the results were manually evaluated and categorized with the identified digital twin quality attributes.
+Therefore, manual reviews were deemed the most suitable tool to account for the characteristics of this situation.
+Manul review inclueded, audits, inspections, reviews, structural analysis
+    and walkthroughs with the project partners which was inspiered from the Balci's manual review works \cite{balcitechniques}.
+Lastly, identified issuess after the reviews were mapped to the quality attributes.
 
-    \section{Digital Twin Quality Attributes and Results}
-
-    \subsection*{First criterion: Correctness}
-    Correctness is a  derived word from the adjective correct, which means that something is error-free regarding a fact or truth~\cite{OxfordDictionary}. 
-    In the context of the digital twins, our fact or truth is a real system hence, correctness is a grade of quality, that indicates an error between the real system and a digital twin system.
-    Meanwhile, the quality of being correct is described by the term accuracy. Another important word is precision, 
-    which refers to the ability to be precise and accurate\cite{OxfordDictionary}. 
-    From a technical standpoint, we use precision in mathematics by the number of provided digits. 
-    For instance, binary64 has 53 significant digits while binary32 has 24, displaying the precision of the structure~\cite{IEE754}.
-
-    \subsection*{Second criterion: Completeness}
-    According to the Oxford Dictionary, complete can be an adjective, an attribute, or  a verb with an object\cite{OxfordDictionary}. 
-    When used as an adjective, it describes something 
-    as having all the necessary or appropriate parts. To evaluate the completeness of a digital twin, 
-    one must first analyze and synthesize the real system to identify subsystems and their relations with related systems in the supra-system. 
-    After this initial analysis, completeness can be assessed by comparing the subsystems and relations of the real world with those of the digital twin.
-
-    \subsection*{Third criterion: Fidelity}
-    The concept of fidelity has garnered significant attention in recent years and continues to be an important area of research in digital twins.
-    In the context of digital twins, Fidelity refers to the degree of exactness with which the real system is copied and represented.
-    Low-fidelity indicates a simplified representation, while high-fidelity refers to an accurate and detailed representation of the real system.
-    This quality attribute plays a crucial role in evaluating the effectiveness of digital twins in accurately capturing the behavior and properties 
-    of real-world systems.
-
-    \subsubsection*{Fidelity vs Correctness}
-    Correctness is a functional quality attribute, which assesses the behavior of the digital twin systems, 
-    by how accurately the results with the given precision match the behavior of the real system or more
-    specifically outputs with the same given inputs. 
-    This quality attribute focuses on the behavior of the system.
-    On the other hand, fidelity is another quality attribute to consider. 
-    It deals with the level of exactness and detail in the digital twin system's representation. 
-    Fidelity concerns itself, with how the digital-twin system is exactly relative to the real system with a certain level of detail, which is more to do with the depiction or representation of the digital twin systems, rather than their behavior of them.
-
-    \subsection*{Fourth criterion: Efficiency}
-    Efficiency refers to the quality of being efficient, and efficiency can be explained as achieving maximum productivity with minimum wasted effort or expense. 
-    The concept of efficiency is tightly coupled with productivity, which refers to the quality of being productive.
-The word productive can be explained as producing or being able to produce large amounts of goods~\cite{OxfordDictionary}.
-    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired.
-Goods of the digital twin are nothing but information,
-    which Grieves first indicated with his Information Mirror Model~\cite{GrievesPLMBook}.
-So to assess the efficiency, one should inspect the sinks and sources of the digital twin system, to identify the waste, expense and productivity.
-
-    \subsection*{Fifth criterion: Evolvability}
-    A system's capability to enhance its suitability to its environment through alterations to both its internal and functional structure is referred to as evolvability.
-Another term used to describe the response to changes in the environment is adaptability.
-    However, this concept differs from evolvability in that it only affects a system's internal or functional structure temporarily.
-In contrast, evolvable systems undergo definite changes in their structures.
-    For instance, a digital twin, which is a virtual system, can be designed to be more flexible and scalable, allowing for easy updates and the addition of new features. 
-    These updates and new features will result in definite changes to the structure of the system.
-On the other hand, a responsive web design is an adaptable system, capable of adjusting its size and layout depending on the user's hardware.
-    As we have seen in~\cite{ZHANGUPDATEMETHOD}, the update method shows that digital twins are evolvable systems,
-    hence this attribute should be considered when the digital twin's quality is inspected.
-To assess the evolvability attribute, scalability analysis, reusability analysis, modifiability analysis, testability analysis, and maintainability analysis can be performed.
+    \section{Results}
 
@@
         \label{fig:QualityInspectonResults}
-
     \end{figure}\begin{figure}[htbp]
@@
     \end{figure}
-
     \subsection{Manual Review Result}
-
     \subsection{Quality Inspection with Quality Attributes}
-
     As can be seen in Figures ~\ref{fig:QualityInspectonResults} and ~\ref{fig:QualityInspectonResultsWithArtifacts}, based on our inspection of the given artifacts,
@@
     which is susceptible to human error and inspector bias.
-
     \section{Discussion}
-
     \label{section:framework_1}

### 2023-03-02 manuscripts/paper-1/main.tex
New image added

@@
     recent years, is often subject to vague and ambiguous envisions\cite{Review1}.
-    The mispresenting this notion began with the physical twin of the Apollo 13 spacecraft. 
-    The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilised in the physical simulations. 
+    The mispresenting of this notion began with the physical twin of the Apollo 13 spacecraft. 
+    The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilized in physical simulations. 
     Even though the digital aspect was expected to be present, there wasn't\cite{GrievesApollo13}.
     Another physical twin is the historic D-day map (also known as the Big Board) in Southwick House England, 
-    which was used simultaneously before and during operation, can be argued to be similar. 
-    The board was a twin of the operation, and it included model of battalions and ships that reflected the actual 
-    locations of the corresponding formations. Furthermore, synchronisation was 
+    which was used simultaneously before and during the operation, and can be argued to be similar. 
+    The board was a twin of the operation, and it included models of battalions and ships that reflected the actual 
+    locations of the corresponding formations. Furthermore, synchronization was 
     implemented to give directives from the real system to control the operation 
@@
 
-    The envision of digital twin emerged from Grieves'es conceptual model, which was called mirrored spaces model in 2002~\cite{Originsofdigitaltwinconcept},
-    and later referenced in 2005 journal article~\cite{2005JournayArticle}. 
+    The envision of a digital twin emerged from Grieves'es conceptual model, which was called mirrored spaces model in 2002~\cite{Originsofdigitaltwinconcept},
+    and later referenced in a 2005 journal article~\cite{2005JournayArticle}. 
     Furthermore, he introduced the information mirroring model, which was his ideal product lifecycle management tool with only one goal. 
-    The goal was to gather as much as  information about the real system to minimize the waste of system's sources such as energy, 
-    time and material. Initially this model had four main parts with real system, 
+    The goal was to gather as much information about the real system to minimize the waste of the system's sources such as energy, 
+    time and material. Initially, this model had four main parts of a real system, 
     virtual system, connection between the real and virtual system and virtual simulations\cite{GrievesPLMBook}. 
-    Later, Grieves removed the latter, in order to simplify the model\cite{Originsofdigitaltwinconcept}.Furthermore, after co-authoring with the Vicker's in 2010, 
-    Grieves decided to use the NASA invented Digital Twin word, instead of information mirroring model\cite{Originsofdigitaltwinconcept}.
+    Later, Grieves removed the latter, to simplify the model\cite{Originsofdigitaltwinconcept}. Furthermore, after co-authoring with Vicker in 2010, 
+    Grieves decided to use the NASA-invented Digital Twin word, instead of the information mirroring model\cite{Originsofdigitaltwinconcept}.
 
@@
 
-    FELICE is a complex system which  addresses a critical problem in robotics which is the effective integration of human and robot abilities in a collaborative setting. 
+    FELICE is a complex system that addresses a critical problem in robotics which is the effective integration of human and robot abilities in a collaborative setting. 
     This challenge requires the development of sophisticated algorithms and techniques that facilitate seamless communication, cooperation, and coordination between humans and robotic agents. 
@@
 
-    Main purpose of this study is to identify the quality attributes and inspect several artifacts 
+    The main purpose of this study is to identify the quality attributes and inspect several artifacts 
     with these to evaluate the quality of the digital twin for the FELICE project, 
@@
     \section{State of the art on quality}
-    Oxford English Dictionary describes the word quality  either as a noun or as an adjective. 
-    The adjective form indicates, a high standard or excellence. For example, the phrase quality products implies 
-    that quality adds a high standard state to the product. There are several definitions which describes a quality 
-    as a noun,however the impactful definition is the quality as a standard of an entity which is measured against the 
-    different or the similar entities\cite{OxfordDictionary}.This definition clearly shows the relativity of quality.In addition, quality be defined 
+    Oxford English Dictionary describes the word quality either as a noun or an adjective. 
+    The adjective form indicates, a high standard or excellence. For example, the phrase quality products imply 
+    that quality adds a high standard state to the product. Several definitions describe quality 
+    as a noun, however, the impactful definition is the quality as a standard of an entity which is measured against the 
+    different or the similar entities\cite{OxfordDictionary}. This definition clearly shows the relativity of quality. In addition, quality is defined 
     as the degree to which a set of inherent properties of an entity fulfills the given requirements~\cite{ISO9000}.    
@@
     Regarding product quality, there are two different aspects~\cite{GrievesPLMBook}.
-    First, quality is an attribute of a product, which meets product specifications.
-Specifications are mostly defined by the supra-systems subsystems, such as by the stakeholders within the supra-system,  If the stakeholders' expectations, or needs, are met, we can consider high quality.
-    The ability to execute to a specific usage standard is the second facet of product quality.
-Since this standardization is usually not controllable, unlike the first, the system's quality will be determined by how the implied or obligatory standards are fulfilled.
+    First, quality is an attribute of a product, which meets product specifications. Specifications are mostly defined by the supra-systems subsystems, 
+    such as by the stakeholders within the supra-system,  If the stakeholders' expectations, or needs, are met, we can consider high quality.
+    The ability to execute to a specific usage standard is the second facet of product quality. Since this standardization is usually not controllable, 
+    unlike the first, the system's quality will be determined by how the implied or obligatory standards are fulfilled.
 
-    Quality management is a management type, which has an interest in Quality, and quality assurance is one of the parts of quality management, 
-    which focuses on providing fidelity that quality requirements will be fulfilled. This means that quality assurance is a subsystem of quality management.
-
-    Quality management systems(QMS) are functioning to plan and execute the organizations quality policies and goals. 
-    Examples of such systems can be a standard like ISO 9001 which can provide a framework for an organization, or a data-driven methodology such  as Six-Sigma to reduce defects and improve efficiency.
-    This concepts  are not new, for example ISO 9001 standard has been established in 1987, and still being regularly updated ~\cite{ISO90012015}. 
+    Quality management systems(QMS) function to plan and execute the organization's quality policies and goals. 
+    Examples of such systems can be a standard like ISO 9001 which can provide a framework for an organization, or a data-driven methodology such as Six Sigma to reduce defects and improve efficiency.
+    These concepts are not new, for example, ISO 9001 standard has been established in 1987, and is still being regularly updated ~\cite{ISO90012015}. 
     \subsection{Software quality}
-    Software is a combination of programs and data which can be used by the virtual 
-    systems as well as  a physical system like a computer system. In contrast a hardware 
+    Software is a combination of programs and data which can be used by virtual 
+    systems as well as a physical system like a computer system. In contrast, hardware 
     is a physical subsystem of a computer system\cite{OxfordDictionary}.
 
-    Software Quality is determined by how well software fulfill the requirements that were set. However, those requirements  
-    not always reflect what the stakeholders actually need, hence the quality depends how accurately this requirements were set \cite{IEE730-2014}. 
+    Software Quality is determined by how well software fulfills the requirements that were set. However, those requirements  
+    not always reflect what the stakeholders need, hence the quality depends on how accurately these requirements were set \cite{IEE730-2014}. 
     As a result, functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability 
-    and portability are the standartized  eight attributes that measure software quality \cite{ISO/IEC:25010}.
+    and portability is the standardized eight attributes that measure software quality \cite{ISO/IEC:25010}.
 
-    Software quality management techniques comes from already used manufacturing techniques in the  industries.
-For example the  product quality assurance has been used as a software quality management activity with some modifications.
-For example, in the manufacturing, products will never exactly meet a specification, due to errors in the machining which results in some tolerance area.
-But in the software systems, or more precise in the virtual systems, it's most of the time not the case.
-Also its nearly imposible to conclude that,
-    the software product is fully meet its speficiations. 
-    Hence, most of the quality assesments are subjective process and as a result, the quality attributes should be inspected subjectively \cite{SoftwareEngineering}.
+    Software quality management techniques come from already used manufacturing techniques in the industries. For example, product quality assurance has been used as a 
+    software quality management activity with some modifications.
+For example, in manufacturing, products will never exactly meet a specification, due to errors in the machining which results in some tolerance area.
+    But in the software systems, or more precisely in the virtual systems, it's most of the time, not the case. Also, it's nearly impossible to conclude that, 
+    the software product fully meets its specifications. 
+    Hence, most of the quality assessments are subjective processes and as a result, the quality attributes should be inspected subjectively \cite{SoftwareEngineering}.
 
@@
     Simulation models are not merely virtual systems; they are also abstracted systems, 
-    which are nothing more than imitations or, to be more precise, abstractions of the real systems. 
-    In fact, everyday, simulation of the real systems occurs in the human brain when prediction of the future outcome or  about the 
-    past state of some occured event required\cite{MobusSystemTheory}. However, most of the simulation processeses are computer 
-    based with software programs. Consequently, the idea of simulation software programs emerges. 
+    which are nothing more than imitations or, to be more precise, abstractions of real systems. 
+    Every day, simulation of the real systems occurs in the human brain when the prediction of the future outcome or about the 
+    past state of some occurred event required\cite{MobusSystemTheory}.
+However, most of the simulation processes are computer-based with software programs.
+Consequently, the idea of simulation software programs emerges.
     For example, ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} are examples of these simulation software programs.
 
-    Validation and verification is used to evaluate the quality characteristics of the simulation 
+    Validation and verification are used to evaluate the quality characteristics of the simulation 
     model \cite{StewartSimulation,VerificationValidationSergent,OsmanBalci}. 
@@
 
-    Various validation and verification techniques can be employed, which can be broadly categorized into six areas: informal, static, dynamic, symbolic, constraint, and formal techniques \cite{balcicategories}\cite{balcitechniques}.
-Formal techniques involve mathematical formality, whereas informal techniques rely on human intervention and reasoning.
-Although mathematical techniques are more precise, informal techniques
+    Various validation and verification techniques can be employed, which can be broadly categorized into six areas: informal, static, dynamic, symbolic, constraint, 
+    and formal techniques \cite{balcicategories}\cite{balcitechniques}. Formal techniques involve mathematical formality, whereas informal techniques rely on human intervention 
+    and reasoning. Although mathematical techniques are more precise, informal techniques 
     are more commonly used \cite{balcicategories}.
@@
 
-    The first level of filtering for the literature review on digital twin publications involves specific criteria. These include that dissertations must be written in English and 
-    published in a journal or conference, and that the search term must be an exact match. To execute this initial filtration, 
+    The first level of filtering for the literature review on digital twin publications involves specific criteria. These include that dissertation must be written in English and 
+    published in a journal or conference and that the search term must be an exact match. To execute this initial filtration, 
     the following queries are used for Google Scholar and Scopus respectively: "search term" and ALL ("digital twin quality") AND (LIMIT-TO (LANGUAGE, "English")).
@@
     After the second level of filtering, one duplicate dissertation was removed and two dissertations that were not in 
-    English were also eliminated. As a result, all dissertations were rejected.
+    English was also eliminated. As a result, all dissertations were rejected.
 
@@
 
-    After a thorough review of 17 research papers, a number of significant findings were revealed.
+    After a thorough review of 17 research papers, several significant findings were revealed.
 
-    First, it was noted that Shcherba et al.  focus on the importance of model quality as an observation for a digital twin subsystem. 
+    First, it was noted that Shcherba et al. focuses on the importance of model quality as an observation for a digital twin subsystem. 
     However, they acknowledged that the quality assessment of the digital twin cannot solely rely on models~\cite{Shcherba}.
@@
     \subsection{Digital Twin Quality Attributes}
-    We consolidated our findings from various standards, including ISO/IEC:25010, IEE730-2014, ISO9000, ISO9001, as well as consulted the  Oxford dictionary to synthesize our findings\cite{ISO9000,ISO90012015,ISO/IEC:25010,IEE730-2014,OxfordDictionary}.
+    We consolidated our findings from various standards, including ISO/IEC:25010, IEE730-2014, ISO9000, and ISO9001, as well as consulted the  Oxford dictionary to 
+    synthesize our findings\cite{ISO9000,ISO90012015,ISO/IEC:25010,IEE730-2014, OxfordDictionary}.
 
-    \textbf{Correctness} is a  derived word from the adjective correct, which means that something is error-free in regard to fact or truth.
+    \textbf{Correctness} is a  derived word from the adjective correct, which means that something is error-free regarding fact or truth.
 In the context of the digital twins, our fact or truth is a real system hence, correctness is a grade of quality, that indicates an error between the real system and a digital twin system.
@@
     \textbf{Completeness} is a derived word from the word complete, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
-    The adjectival form of complete is a state of having all the neccesary or appropriate parts\cite{OxfordDictionary}.
+    The adjectival form of complete is a state of having all the necessary or appropriate parts\cite{OxfordDictionary}.
 
     \textbf{Fidelity}
-    Fidelity refers to the degree of exactness with which the real system is copied and represented.Low-fidelity indicates a simplified representation, 
+    Fidelity refers to the degree of exactness with which the real system is copied and represented. Low fidelity indicates a simplified representation, 
     while high-fidelity refers to an accurate and detailed representation of the real system \cite{Review2}. 
@@
     \textbf{Efficiency}
-    Efficiency refers to the  quality of  being efficient, and efficient is achieving
-    maximum productivity with minimum wasted effort or expense. The concept of efficiency is tightly coupled to productivity, which  refers to a quality of being productive,
-    also  the word productive can be explained as producing or able to produce large amounts of goods\cite{OxfordDictionary}.  
-    For example time efficiency indicates that,  with the less amount of time as an input, more output with the minimum 
-    waste during the process is desired . Goods of the  digital twin is nothing but an information, which Grieves first 
+    Efficiency refers to the quality of being efficient, and efficiency is achieving
+    maximum productivity with minimum wasted effort or expense. The concept of efficiency is tightly coupled to productivity, which refers to the quality of being productive,
+    also the word productive can be explained as producing or being able to produce large amounts of goods\cite{OxfordDictionary}.  
+    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum 
+    waste during the process is desired. Goods of the digital twin are nothing but information, which Grieves first 
     indicated with this Information Mirror Model\cite{GrievesPLMBook}.
@@
     \textbf{Process Videos:}
-    Project partner provided three videos initially to explain the manual assembly procedures performed at each of the three workstations. From the videos,  
-    the sequence of assembly steps were extracted  at least for one product variant.
-The tools and the parts needed for each assembly operation was observed.
-Additionally, an approximate duration of each assembly step were estimated, and some ergonomic characteristics of each operation was derived.
+    The project partner provided three videos initially to explain the manual assembly procedures performed at each of the three workstations. From the videos,  
+    the sequence of assembly steps was extracted at least for one product variant.
+The tools and the parts needed for each assembly operation were observed.
+Additionally, the approximate duration of each assembly step
+    was estimated, and some ergonomic characteristics of each operation were derived. 
     The derivable ergonomic characteristics mainly included the poses and motions performed by the operators.
@@
     To better understand the context and focus of the digital twin, 
-    project partner used a methodology based on hierarchical task analysis and the process videos. 
+    the project partner used a methodology based on hierarchical task analysis and the process videos. 
     This resulted in a scope definition that identified entities to be twinned, entities to be tracked, and important areas in the scene. 
@@
     \textbf{Conceptual Model} was comprised of two parts:  a general conceptual model and an operational conceptual model.
-Both models provided a description of the assembly line processes, but the operational conceptual model focused on the specific steps of the assembly process, while the general conceptual model focused on higher-level processes and workflows.
+Both models described the assembly line processes, but the operational conceptual model focused on the specific steps of the assembly process, while the general conceptual model focused on higher-level processes and workflows.
     The general conceptual model was represented using a general flow chart notation that distinguished between a root node, activity nodes, and decision nodes.
@@
 Therefore, manual reviews were deemed the most suitable tool to account for the characteristics of this situation.
-Manul review inclueded, audits, inspections, reviews, structural analysis
-    and walkthroughs with the project partners which was inspiered from the Balci's manual review works \cite{balcitechniques}.
-Lastly, identified issuess after the reviews were mapped to the quality attributes.
+    The manual review included, audits, inspections, reviews, structural analysis 
+    and walkthroughs with the project partners which was inspired by Balci's manual review works \cite{balcitechniques}.
+Lastly, identified issues after the reviews were mapped to the quality attributes.
 
@@
     \begin{figure}[htbp]
-        \includegraphics[scale=0.75]{quality_inspection_results.png}
-        \caption{Overall Quality Inspection Results}
-        \label{fig:QualityInspectonResults}
-    \end{figure}\begin{figure}[htbp]
-        \includegraphics[scale = 0.45]{quality_inspection_results_with_artifacts.png}
+        \includegraphics[scale = 0.40]{quality_inspection_results_with_artifacts.png}
         \caption{ Quality Inspection Results Categorized with Artifacts}
@@
     \end{figure}
+
     \subsection{Manual Review Result}
     \subsection{Quality Inspection with Quality Attributes}
-    As can be seen in Figures ~\ref{fig:QualityInspectonResults} and ~\ref{fig:QualityInspectonResultsWithArtifacts}, based on our inspection of the given artifacts,
+    As can be seen in Figures and ~\ref{fig:QualityInspectonResultsWithArtifacts}, based on our inspection of the given artifacts,
     we have identified a total of seven correctness issues, eleven completeness issues, and two fidelity issues. 

### 2023-03-02 manuscripts/paper-1/main.tex
Results and discussion is partly done

@@
 \usepackage{cite}
+\usepackage{booktabs}
+\usepackage{multirow}
 
@@
 
-    \textbf{Fidelity}
-    Fidelity refers to the degree of exactness with which the real system is copied and represented. Low fidelity indicates a simplified representation, 
+    \textbf{Fidelity} refers to the degree of exactness with which the real system is copied and represented. Low fidelity indicates a simplified representation, 
     while high-fidelity refers to an accurate and detailed representation of the real system \cite{Review2}. 
@@
 
-    \textbf{Efficiency}
-    Efficiency refers to the quality of being efficient, and efficiency is achieving
+    \textbf{Efficiency} refers to the quality of being efficient, and efficiency is achieving
     maximum productivity with minimum wasted effort or expense. The concept of efficiency is tightly coupled to productivity, which refers to the quality of being productive,
@@
 
-    \textbf{Evolvability}
-    A system's capability to enhance its suitability to its environment through alterations to both its internal and functional 
-    structure is referred to as evolvability\cite{MobusSystemTheory}. Another term used to describe the response to changes in the environment is adaptability.
+    \textbf{Evolvability} is a system's capability to enhance its suitability to its environment through alterations to both its internal and functional 
+    structure\cite{MobusSystemTheory}. Another term to describe the response to changes in the environment is adaptability.
     However, this concept differs from evolvability in that it only affects a system's internal or functional structure temporarily. 
@@
     \section{Results}
+    During the initial stages of the project, when the target system was not yet available, there was a 
+    lack of observable data about system behavior that could be utilized for validation.
+Instead, informal and potentially incomplete, inconsistent, or incorrect system descriptions had to be relied upon.
+    Therefore, manual reviews for each artifact were conducted and twenty-one issues were identified and mapped to the specific digital twin quality attributes. 
+    The analysis revealed that a total of thirty-eight digital twin quality attributes were lacking in these artifacts. \ref{fig:QualityInspectonResultsWithArtifacts}
+
+\textbf{Process Videos Review Results}
+
+F1  - Even though the videos are well suited for providing a first impression of the production facility and the current assembly process for one product variant, the other product variants include different assembly operations,
+which were not shown in the videos.
+Furthermore, the cobot and the adaptive workstation were not part of the assembly process yet, hence the videos do not provide a complete representation of the target system.
+
+\textbf{Scope Definition Review Results}
+
+F2 - The scope definition focuses on the physical entities of the shop floor and is consistent with the videos presented in the previous section. 
+However, the scope definition is incomplete.
+Several entities are only selected for the tracking, hence additional state information such as the failure status of these entities was missing in the digital twin.
+
+\textbf{Requirements Specification Review Results}
+
+F3-  Atypical categorization of the digital twin requirements as functional, non-functional, constraint and standard was introduced. 
+Also, standard categories were considered as a cause of requirements instead of a category of requirements. Furthermore, 
+the constraint category was considered a non-functional requirement which results in a significant misunderstanding between non-functional 
+requirements and constraints. Finally, some requirements were described as non-functional requirements instead of functional requirements.
+
+F4 - Imprecise and unclear statements were found in requirement specifications.
+
+F5 - Key design decisions were found in the requirement specifications, which results in a considerable decrease in maintainability.
+
+\textbf{Conceptual  Model Review Results}
+
+F6 - Conceptual models are not designed to react to unwanted situations.
+
+F7 - Conceptual model specification was not clear enough, which results in quite some room for interpretations by the stakeholders. 
+as the use of an unspecified flow chart model is prone to differing interpretations by different stakeholders and probable incorrect understanding of the relations between the sub-systems.
+
+F8 - The difference between the event triggers and decision nodes was not clear, which decreased the clarity and maintainability of the model considerably.
+
+F9 - Representation of the model is not great, hence understanding the interactions between the different subprocesses are not clear.
+
+F10 - The model were lacking great organization tools such as swim lanes and object flows.
+
+F11 - The assignment of the cobot to micro-operations was not regularly reviewed and updated as the project progresses.
+
+F12 - Even though the durations of the macro-operations were well-known and studied thoroughly before, the durations of the micro-operations were estimated based on a simple calculation scheme.
+
+\textbf{Simulation Model Review Results}
+
+F13:The input controls in the Discrete  Event Simulation module were not complete or aligned with the actual inputs that will be provided by another system.
+
+F14, F15:The ranges defined for some events were not validated.
+
+F16:Database structures were not updated automatically, instead done manually.
+
+F17:The duration of micro-, loading- and unloading-operations of the cobot were based on assumptions rather than actual measurements.
+
+F18:Discerete Event Simulation module does not support parallel execution of micro-operations.
+
+F19:Interruption mechanism of the assembly line was not considered within the DES module.
+
+F20:Number of micro-operations were hard coded, consequently, the DES module must be reprogrammed every time, when a new micro-operation is needed.
+
+F21:Edge-cases were not considered in the DES module.
 
@@
 
-    \subsection{Manual Review Result}
-    \subsection{Quality Inspection with Quality Attributes}
-    As can be seen in Figures and ~\ref{fig:QualityInspectonResultsWithArtifacts}, based on our inspection of the given artifacts,
-    we have identified a total of seven correctness issues, eleven completeness issues, and two fidelity issues. 
-    It is important to note that we were unable to inspect for efficiency as the project is still in the design phase, 
-    and we do not have enough data to make estimations for this attribute. Additionally, all of our inspections were conducted manually, 
-    which is susceptible to human error and inspector bias.
     \section{Discussion}

### 2023-03-02 manuscripts/paper-1/main.tex
Again grammer check, and mapping added

@@
     Digital twins are highly intricate and adaptable systems that possess the capability to not only respond to environmental 
-    changes but also modify their internal structure \cite{ZHANGUPDATEMETHOD,MobusSystemTheory}. Therefore, ascertaining a 
+    changes but also modify their internal structure \cite{ZHANGUPDATEMETHOD, MobusSystemTheory}. Therefore, ascertaining a 
     requisite level of quality for the construction of a digital twin is an arduous undertaking.
@@
     reusability analysis, modifiability analysis, testability analysis, and maintainability analysis can be performed. 
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%METHODS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     \section{Artifacts and Methods}
@@
 Lastly, identified issues after the reviews were mapped to the quality attributes.
-
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%RESULTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     \section{Results}
@@
 
-F3-  Atypical categorization of the digital twin requirements as functional, non-functional, constraint and standard was introduced. 
+    F3 - Atypical categorization of the digital twin requirements as functional, non-functional, constraint and standard was introduced. 
     Also, standard categories were considered as a cause of requirements instead of a category of requirements. Furthermore, 
@@
 
-F13:The input controls in the Discrete  Event Simulation module were not complete or aligned with the actual inputs that will be provided by another system.
+    F13 - The input controls in the discrete event simulation module was not complete or aligned with the actual inputs that will be provided by another system.
 
-F14, F15:The ranges defined for some events were not validated.
+    F14, F15 - The ranges defined for some events were not validated.
 
-F16:Database structures were not updated automatically, instead done manually.
+    F16 - Database structures were not updated automatically, instead done manually.
 
-F17:The duration of micro-, loading- and unloading-operations of the cobot were based on assumptions rather than actual measurements.
+    F17 - The duration of micro-, loading- and unloading-operations of the cobot were based on assumptions rather than actual measurements.
 
-F18:Discerete Event Simulation module does not support parallel execution of micro-operations.
+    F18 - Discrete event Simulation module does not support parallel execution of micro-operations.
 
-F19:Interruption mechanism of the assembly line was not considered within the DES module.
+    F19 - The interruption mechanism of the assembly line was not considered within the DES module.
 
-F20:Number of micro-operations were hard coded, consequently, the DES module must be reprogrammed every time, when a new micro-operation is needed.
+    F20 - The number of micro-operations was hard coded, consequently, the DES module must be reprogrammed every time, when a new micro-operation is needed.
 
-F21:Edge-cases were not considered in the DES module.
+    F21 - Edge cases were not considered in the DES module.
+
+    \subsection{Mapping Issues to Quality Attributes}
+
+    \begin{table}[h!]
+        \begin{center}
+          \caption{Mapping Findings to Quality Attributes}
+          \label{tab:Mapping}
+          \begin{tabular}{l@{\hspace{1cm}}l} 
+            \textbf{Findings} & \textbf{Quality Issues}\\
+            \hline
+            Finding 1 &     Completeness\\
+            Finding 2 &     Completeness\\
+            Finding 3 &     Correctness, Completeness\\
+            Finding 4 &     Correctness\\
+            Finding 5 &     Evolvability\\
+            Finding 6 &     Completeness\\
+            Finding 7 &     Correctness, Completeness, Fidelity, Efficiency, Evolvability\\
+            Finding 8 &     Completeness, Fidelity, Evolvability\\
+            Finding 9 &     Evolvability\\
+            Finding 10 &    Correctness, Completeness, Fidelity, Evolvability\\
+            Finding 11 &    Evolvability\\
+            Finding 12 &    Correctness, Completeness\\
+            Finding 13 &    Completeness, Evolvability\\
+            Finding 14 &    Correctness, Completeness\\
+            Finding 15 &    Correctness, Completeness\\
+            Finding 16 &    Evolvability \\
+      Finding 17&CorrectnessCompleteness \\
+      Finding 18&CorrectnessEfficiency \\
+      Finding 19&CompletenessEvolvability \\
+      Finding 20&Evolvability \\
+      Finding 21&Evolvability 
+    \end{tabular}
+    \end{center}
+    \end{table}
 

### 2023-03-02 manuscripts/paper-1/main.tex
Results are done

@@
 
-    \textbf{Simulation Model Review Results}
+    \textbf{Discrete Event Simulation Model Review Results}
 
-    F13 - The input controls in the discrete event simulation module was not complete or aligned with the actual inputs that will be provided by another system.
+    F13 - The input controls in the simulation module was not complete or aligned with the actual inputs that will be provided by another system.
 
@@
 
-    F18 - Discrete event Simulation module does not support parallel execution of micro-operations.
+    F18 - The simulation module does not support parallel execution of micro-operations.
 
-    F19 - The interruption mechanism of the assembly line was not considered within the DES module.
+    F19 - The interruption mechanism of the assembly line was not considered within the simulation module.
 
-    F20 - The number of micro-operations was hard coded, consequently, the DES module must be reprogrammed every time, when a new micro-operation is needed.
+    F20 - The number of micro-operations was hard coded, consequently, the simulation module must be reprogrammed every time, when a new micro-operation is needed.
 
-    F21 - Edge cases were not considered in the DES module.
+    F21 - Edge cases were not considered in the simulation module.
 
     \subsection{Mapping Issues to Quality Attributes}
+
+    To evaluate the quality of the FELICE digital twin, identified issues mapped to one or more relevant quality attributes(Table \ref{tab:Mapping}).
+    The assessment revealed that a significant portion of the identified issues
+     was quickly attributed to specific quality attributes.  Specifically, 24\% of the issues were related to correctness, 
+     which indicates an error between the real system and a digital twin system. 
+     35\% of the issues were related to completeness, proving that some necessary or appropriate parts were missing. 
+     8\% of the issues were related to fidelity, indicating a lack of detail. 
+     5\% of the issues were related to efficiency, indicating poor performance or excessive resource usage. 
+     Finally, 28\% of the issues were related to evolvability, indicating that the system was unresponsive to the environment 
+     and was not flexible or scalable.
 

### 2023-03-03 manuscripts/paper-1/main.tex
Discussion is partly done. Prof revision needed

--- 2023-03-02 manuscripts/paper-1/main.tex
@@
 
-    The main purpose of this study is to identify the quality attributes and inspect several artifacts 
-    with these to evaluate the quality of the digital twin for the FELICE project, 
-    which is currently in the design phase~\cite{FELICE}. These artifacts included process videos showing the current 
+    The main purpose of this study is to inspect several artifacts and map the found issues to quality attributes to evaluate the quality of the digital twin for the FELICE project, which is currently in the design phase.~\cite{FELICE}.
+These artifacts included process videos showing the current
     assembly procedure, a scope definition, a requirements specification, a general and operational conceptual model, 
@@
     which necessitates the development of appropriate quality metrics and standards for digital twins.
-    \subsection{Digital Twin Quality Attributes}
+    \subsection{Digital Twin Quality Attributes}\label{section:Digital Twin Quality Attributes}
     We consolidated our findings from various standards, including ISO/IEC:25010, IEE730-2014, ISO9000, and ISO9001, as well as consulted the  Oxford dictionary to 
@@
     reusability analysis, modifiability analysis, testability analysis, and maintainability analysis can be performed. 
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%METHODS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     \section{Artifacts and Methods}
     The used methodology consists of manual artifact reviews and evaluation of the results according to the digital twin quality attributes.    
-    \subsection{Artifacts}
+    \subsection{Artifacts}\label{section:Artifacts}
     The current stage of review encompasses five key artifacts, including process videos displaying the current assembly procedure without an adaptive workstation and cobot, a scope definition outlining the objects on the shop floor requiring tracking or twinning, a requirements specification summarizing functional and non-functional requirements for the digital twin, a general and an operational conceptual model elucidating the high-level structure of the assembly procedure,
@@
     The manual review included, audits, inspections, reviews, structural analysis 
-    and walkthroughs with the project partners which was inspired by Balci's manual review works \cite{balcitechniques}.
-Lastly, identified issues after the reviews were mapped to the quality attributes.
+    and walkthroughs with the project partners which was inspired by Balci's manual review works \cite{balcitechniques}. Lastly, observations after the reviews were mapped to the quality attributes. 
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%RESULTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    \section{Results}
+    %%TODO WRITE HERE ONCE AGAIN
 
-    \section{Results}
-    During the initial stages of the project, when the target system was not yet available, there was a 
-    lack of observable data about system behavior that could be utilized for validation.
-Instead, informal and potentially incomplete, inconsistent, or incorrect system descriptions had to be relied upon.
-    Therefore, manual reviews for each artifact were conducted and twenty-one issues were identified and mapped to the specific digital twin quality attributes. 
-    The analysis revealed that a total of thirty-eight digital twin quality attributes were lacking in these artifacts. \ref{fig:QualityInspectonResultsWithArtifacts}
+    \begin{table}[h!]
+        \begin{center}
+          \caption{Mapping findings to Quality Attributes: Results of the manual artifact reviews were mapped to quality attributes, which were discussed in \ref{section:Digital Twin Quality Attributes}}
+          \label{tab:Mapping}
+          \begin{tabular}{l@{\hspace{1cm}}l} 
+            \textbf{Findings} & \textbf{Missing Quality Attribute}\\
+            \hline
+            Findings 1, 2 and 6 &     Completeness\\
+            Findings 3, 12, 14,15 and 17  &     Correctness, Completeness\\
+            Findings 4 &     Correctness\\
+            Findings 5,9,11,16,20 and 21 &     Evolvability\\
+            Findings 7 &     Correctness, Completeness, Fidelity, Efficiency, Evolvability\\
+            Findings 8 &     Completeness, Fidelity, Evolvability\\
+            Findings 10 &    Correctness, Completeness, Fidelity, Evolvability\\
+            Findings 13 and 19 &    Completeness, Evolvability\\
+            Findings 18&Correctness, Efficiency \\
+    \end{tabular}
+    \end{center}
+    \end{table}
+
+    \begin{figure}[htbp]
+        \includegraphics[scale = 0.40]{quality_inspection_results_with_artifacts.png}
+        \caption{Quality Inspection Results Categorized with Artifacts: X-Axis represents artifacts in \ref{section:Artifacts}, Y-Axis represents the number of missing quality attributes found for each artifact,
+        and lastly, each digital twin quality attribute is shown by the colors.}
+        \label{fig:QualityInspectonResultsWithArtifacts}
+    \end{figure}
 
@@
 
-F1  - Even though the videos are well suited for providing a first impression of the production facility and the current assembly process for one product variant, the other product variants include different assembly operations,
+    Findings 1  - Even though the videos are well suited for providing a first impression of the production facility 
+    and the current assembly process for one product variant, the other product variants include different assembly operations, 
     which were not shown in the videos. 
-Furthermore, the cobot and the adaptive workstation were not part of the assembly process yet, hence the videos do not provide a complete representation of the target system.
+    Furthermore, the cobot and the adaptive workstation were not part of the assembly process yet,
+     hence the videos do not provide a complete representation of the target system.
 
@@
 
-F2 - The scope definition focuses on the physical entities of the shop floor and is consistent with the videos presented in the previous section. 
+    Findings 2 - The scope definition focuses on the physical entities of the shop floor and is consistent with the videos presented in the previous section. 
     However, the scope definition is incomplete.
@@
 
-F3-  Atypical categorization of the digital twin requirements as functional, non-functional, constraint and standard was introduced. 
+    Findings 3 - Atypical categorization of the digital twin requirements as functional, non-functional, constraint and standard was introduced. 
     Also, standard categories were considered as a cause of requirements instead of a category of requirements. Furthermore, 
@@
 
-F4 - Imprecise and unclear statements were found in requirement specifications.
+    Findings 4 - Imprecise and unclear statements were found in requirement specifications.
 
-F5 - Key design decisions were found in the requirement specifications, which results in a considerable decrease in maintainability.
+    Findings 5 - Key design decisions were found in the requirement specifications, which results in a considerable decrease in maintainability.
 
@@
 
-F6 - Conceptual models are not designed to react to unwanted situations.
+    Findings 6 - Conceptual models are not designed to react to unwanted situations.
 
-F7 - Conceptual model specification was not clear enough, which results in quite some room for interpretations by the stakeholders. 
+    Findings 7 - Conceptual model specification was not clear enough, which results in quite some room for interpretations by the stakeholders. 
     as the use of an unspecified flow chart model is prone to differing interpretations by different stakeholders and probable incorrect understanding of the relations between the sub-systems.
 
-F8 - The difference between the event triggers and decision nodes was not clear, which decreased the clarity and maintainability of the model considerably.
+    Findings 8 - The difference between the event triggers and decision nodes was not clear, which decreased the clarity and maintainability of the model considerably.
 
-F9 - Representation of the model is not great, hence understanding the interactions between the different subprocesses are not clear.
+    Findings 9 - The representation of the model is not great, hence understanding the interactions between the different subprocesses are not clear.
 
-F10 - The model were lacking great organization tools such as swim lanes and object flows.
+    Findings 10 - The model were lacking great organization tools such as swim lanes and object flows.
 
-F11 - The assignment of the cobot to micro-operations was not regularly reviewed and updated as the project progresses.
+    Findings 11 - The assignment of the cobot to micro-operations was not regularly reviewed and updated as the project progresses.
 
-F12 - Even though the durations of the macro-operations were well-known and studied thoroughly before, the durations of the micro-operations were estimated based on a simple calculation scheme.
+    Findings 12 - Even though the durations of the macro-operations were well-known and studied thoroughly before, the durations of the micro-operations were estimated based on a simple calculation scheme.
 
-\textbf{Simulation Model Review Results}
+    \textbf{Discrete Event Simulation Model Review Results}
 
-F13:The input controls in the Discrete  Event Simulation module were not complete or aligned with the actual inputs that will be provided by another system.
+    Findings 13 - The input controls in the simulation module was not complete or aligned with the actual inputs that will be provided by another system.
 
-F14, F15:The ranges defined for some events were not validated.
+    Findings 14, and 15 - The ranges defined for some events were not validated.
 
-F16:Database structures were not updated automatically, instead done manually.
+    Findings 16 - Database structures were not updated automatically, instead done manually.
 
-F17:The duration of micro-, loading- and unloading-operations of the cobot were based on assumptions rather than actual measurements.
+    Findings 17 - The duration of micro-, loading- and unloading-operations of the cobot were based on assumptions rather than actual measurements.
 
-F18:Discerete Event Simulation module does not support parallel execution of micro-operations.
+    Findings 18 - The simulation module does not support parallel execution of micro-operations.
 
-F19:Interruption mechanism of the assembly line was not considered within the DES module.
+    Findings 19 - The interruption mechanism of the assembly line was not considered within the simulation module.
 
-F20:Number of micro-operations were hard coded, consequently, the DES module must be reprogrammed every time, when a new micro-operation is needed.
+    Findings 20 - The number of micro-operations was hard coded, consequently, the simulation module must be reprogrammed every time, when a new micro-operation is needed.
 
-F21:Edge-cases were not considered in the DES module.
+    Findings 21 - Edge cases were not considered in the simulation module.
 
-    \begin{figure}[htbp]
-        \includegraphics[scale = 0.40]{quality_inspection_results_with_artifacts.png}
-        \caption{ Quality Inspection Results Categorized with Artifacts}
-        \label{fig:QualityInspectonResultsWithArtifacts}
-    \end{figure}
+    \subsection{Mapping the Issues to Quality Attributes}
+    The analysis revealed that a total of thirty-eight digital twin quality attributes were lacking in these artifacts. \ref{fig:QualityInspectonResultsWithArtifacts}
+    Therefore, to evaluate the quality of the FELICE digital twin, observations are mapped to one or more relevant quality attributes\ref{tab:Mapping}.
+    In addition, the assessment shows that every one of the identified issues was quickly attributed to a specific quality attribute.  
+    Specifically, 24\% of the issues were related to correctness, which indicates an error between the real system and a digital twin system.
+    35\% of the issues were related to completeness, proving that some necessary or appropriate parts are missing.
+    8\% of the issues were related to fidelity, indicating a lack of detail. 5\% of the issues were related to efficiency, indicating poor 
+    performance or excessive resource usage. Finally, 28\% of the issues were related to evolvability, indicating that the system has flexibility or scalability issues.
 
     \section{Discussion}
-    \label{section:framework_1}
-    To mitigate potential human bias and enhance the data-driven approach for quality assurance, ongoing research aims to address these issues. 
-    Furthermore, the assessment of digital twin quality can be significantly improved by obtaining data from real systems, thereby enabling better visibility and a more robust evaluation.
-As such, the use of empirical data in combination with machine learning techniques can offer a more objective and reliable means of evaluating the correctness, completeness, fidelity, efficiency, and evolvability of digital twins.
-Additionally, given the manual nature of the current inspections, it is important to acknowledge the potential for inspector bias, which may impact the accuracy of the assessments.
-    By leveraging technology to automate certain aspects of the evaluation process, it is possible to reduce the potential for such biases and improve the overall quality of digital twin assessments.
 
-    The success of the digital twin system depends on its quality, which requires careful evaluation based on several crucial quality attributes.
-The correctness of the system is measured by how accurately it behaves compared to the real system.
-    Completeness assesses whether the digital twin's subsystems and relations match those of the real system. 
-    Fidelity refers to the degree of exactness with which the real system is copied and represented.
-    Efficiency measures the productivity of the system and the minimum waste during the process. 
-    Evolvability is the system's ability to enhance its suitability to its environment through alterations to both its internal and functional structure. 
-    Evaluating these quality attributes of the FELICE digital twin system will help ensure its success in effectively integrating human and robot abilities in a collaborative setting, leading to enhanced efficiency and safety in various human-robot collaborative tasks.
+    The results of this study demonstrate that a manual review and mapping of quality attributes to issues is an effective approach for evaluating the quality of digital twins in the design phase.  
+    Therefore, systematic analysis of the identified issues in terms of their relevance to various quality attributes is an effective way to gain insight into the strengths and weaknesses of the digital twin system under development.
+    These insights can be used to guide further design decisions and improvements, ultimately leading to a higher-quality end product.
+
+    The quality assessment of the digital twin encountered some limitations due to the exility of information about the real system.
+Some artifacts provided less information, such as process videos, which only provide a limited perspective of the shopfloor based on the camera's field of view and the skills of the video maker.
+    In contrast, the simulation and conceptual model offer a plethora of aspects to examine and assess, which results in a higher probability of discovering the issues \ref{fig:QualityInspectonResultsWithArtifacts}.
+
     \section*{Acknowledgements}

### 2023-03-03 manuscripts/paper-1/main.tex
Method is proper

@@
     which necessitates the development of appropriate quality metrics and standards for digital twins.
-    \subsection{Digital Twin Quality Attributes}\label{section:Digital Twin Quality Attributes}
-    We consolidated our findings from various standards, including ISO/IEC:25010, IEE730-2014, ISO9000, and ISO9001, as well as consulted the  Oxford dictionary to 
-    synthesize our findings\cite{ISO9000,ISO90012015,ISO/IEC:25010,IEE730-2014, OxfordDictionary}.
 
-    \textbf{Correctness} is a  derived word from the adjective correct, which means that something is error-free regarding fact or truth.
-In the context of the digital twins, our fact or truth is a real system hence, correctness is a grade of quality, that indicates an error between the real system and a digital twin system.
-    Meanwhile, the quality of being correct is described by the term accuracy \cite{OxfordDictionary}.
-
-    \textbf{Completeness} is a derived word from the word complete, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
-    The adjectival form of complete is a state of having all the necessary or appropriate parts\cite{OxfordDictionary}.
-
-    \textbf{Fidelity} refers to the degree of exactness with which the real system is copied and represented. Low fidelity indicates a simplified representation, 
-    while high-fidelity refers to an accurate and detailed representation of the real system \cite{Review2}. 
-    The concept of fidelity has garnered significant attention in recent years and continues to be an important area of research in digital twins\cite{Review2}\cite{Review1}.
-
-    \textbf{Efficiency} refers to the quality of being efficient, and efficiency is achieving
-    maximum productivity with minimum wasted effort or expense. The concept of efficiency is tightly coupled to productivity, which refers to the quality of being productive,
-    also the word productive can be explained as producing or being able to produce large amounts of goods\cite{OxfordDictionary}.  
-    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum 
-    waste during the process is desired. Goods of the digital twin are nothing but information, which Grieves first 
-    indicated with this Information Mirror Model\cite{GrievesPLMBook}.
-
-    \textbf{Evolvability} is a system's capability to enhance its suitability to its environment through alterations to both its internal and functional 
-    structure\cite{MobusSystemTheory}. Another term to describe the response to changes in the environment is adaptability.
-    However, this concept differs from evolvability in that it only affects a system's internal or functional structure temporarily. 
-    For instance, a digital twin, which is a virtual system, can be designed to be more flexible and scalable, 
-    allowing for easy updates and the addition of new features. 
-    These updates and new features will result in definite changes to the structure of the system. 
-    On the other hand, a responsive web design is an adaptable system, capable of adjusting its size and layout 
-    depending on the user's hardware. As we have seen in \cite{ZHANGUPDATEMETHOD}, the update method shows that digital twins are evolvable systems, 
-    hence this attribute should be considered when the digital twin's quality is inspected. To assess the evolvability attribute, scalability analysis,
-    reusability analysis, modifiability analysis, testability analysis, and maintainability analysis can be performed. 
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%METHODS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \section{Artifacts and Methods}
-    The used methodology consists of manual artifact reviews and evaluation of the results according to the digital twin quality attributes.    
+    \section{Method}
+    The methodology consists of a set of artifacts, manual artifact reviews, mapping quality attributes to the   
+    and evaluation of the results according to the digital twin quality attributes.    
     \subsection{Artifacts}\label{section:Artifacts}
@@
 
-    \subsection{Manual Artifact Reviews and Evoluation}
-    During the initial stages of the project, when the target system was not yet available, there was a lack of observable data about system behavior that could be utilized for validation. 
+    \subsection{Manual Artifact Reviews}
+    During the initial stages of the project, when the target system was not yet available,
+    there was a lack of observable data about system behavior that could be utilized for validation. 
     Instead, informal and potentially incomplete, inconsistent, or incorrect system descriptions had to be relied upon. 
     Therefore, manual reviews were deemed the most suitable tool to account for the characteristics of this situation.
-    The manual review included, audits, inspections, reviews, structural analysis 
-    and walkthroughs with the project partners which was inspired by Balci's manual review works \cite{balcitechniques}. Lastly, observations after the reviews were mapped to the quality attributes. 
+    The manual review included, audits, inspections, reviews, structural analysis and walkthroughs 
+    with the project partners which was inspired by Balci's manual review works \cite{balcitechniques}.
+
+    \subsection{Digital Twin Quality Attributes}\label{section:Digital Twin Quality Attributes}
+    To identify the digital twin quality attributes, the following standards, including ISO/IEC:25010, IEE730-2014, ISO9000, and ISO9001, 
+    as well as the Oxford dictionary was consulted to 
+    synthesize our findings\cite{ISO9000,ISO90012015,ISO/IEC:25010,IEE730-2014, OxfordDictionary}.
+
+    \textbf{Correctness} is a  derived word from the adjective correct, which means that something is error-free regarding fact or truth. 
+    In the context of the digital twins, the fact or truth is the real system hence, correctness is a grade of quality, 
+    that indicates an error between the real system and a digital twin system.
+    Meanwhile, the quality of being correct is described by the term accuracy \cite{OxfordDictionary}.
+
+    \textbf{Completeness} is a derived word from the word complete, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
+    The adjectival form of complete is a state of having all the necessary or appropriate parts\cite{OxfordDictionary}.
+
+    \textbf{Fidelity} refers to the degree of exactness with which the real system is copied and represented. 
+    Low fidelity indicates a simplified representation, while high fidelity refers to an accurate and detailed representation of the real system \cite{Review2}. 
+    The concept of fidelity has garnered significant attention in recent
+    years and continues to be an important area of research in digital twins\cite{Review2}\cite{Review1}.
+
+    \textbf{Efficiency} refers to the quality of being efficient\cite{OxfordDictionary}. Therefore, efficiency is achieving
+    maximum productivity with minimum wasted effort or expense. The concept of efficiency is tightly coupled to productivity, which refers to the quality of being productive,
+    also the word productive can be explained as producing or being able to produce large amounts of goods\cite{OxfordDictionary}.  
+    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum 
+    waste during the process is desired.
+
+    \textbf{Evolvability} is a system's capability to enhance its suitability to its environment through alterations to both its internal and functional 
+    structure\cite{MobusSystemTheory}. Another term to describe the response to changes in the environment is adaptability.
+    However, this concept differs from evolvability in that it only affects a system's internal or functional structure temporarily. 
+    For instance, a digital twin, which is a virtual system, can be designed to be more flexible and scalable, 
+    allowing for easy updates and the addition of new features\cite{ZHANGUPDATEMETHOD}.
+
+    \subsection{Mapping Digital Twin Attributes to Results of the Manual Reviews}
+    To evaluate the quality of the artifact, the issues were mapped to digital twin attributes. 
+    To begin this process, the findings were collected from the manual review, followed by an inspection of the findings to determine which digital twin qualities were absent. 
+    Finally, the findings were mapped to the relevant missing quality attribute(s) and submitted for artifact quality evaluation.
+
+    subsection{Artifact Quality Evaluation}
+    To evaluate the quality of the digital twin artifacts, the mapped findings were scrutinized and evaluated. 
+    The process started by identifying which quality attribute(s) were mapped. 
+    Once identified, the missing attribute(s) was incremented by 1 to determine the quality percentage of the artifact.
+
+    \begin{figure}[htbp]
+        \includegraphics[scale = 0.35]{RequirementSpecifications.png}
+        \caption{Method for the evaluation of the digital twin artifact quality: Artifact. finding indicates that the finding belongs to the artifact, while -> indicates mapping}
+        \label{fig:Method}
+    \end{figure}
+
+    \subsection{Digital Twin Quality Evaluation}
+    To assess the quality of the digital twin, the values obtained from evaluating each artifact's quality are collected and summed. 
+    The resulting sum was assigned to the corresponding digital twin quality attribute. 
+    As a result, the digital twin quality was expressed as a percentage using the following equation:    
+    \begin{equation}
+        (totalnumberofselectedattribute/totalnumberofattributes)*100
+    \end{equation}
+
+    \begin{figure}[htbp]
+        \includegraphics[scale = 0.35]{DigitalTwinQuality.png}
+            \caption{Method for the evaluation of the digital twin quality:}
+        \label{fig:MethodforDigitalTwinQuality}
+    \end{figure}
+
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%RESULTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-03-06 manuscripts/paper-1/main.tex
Table added + some revisions

@@
     The goal was to gather as much information about the real system to minimize the waste of the system's sources such as energy, 
-    time and material. Initially, this model had four main parts of a real system, 
+    time and material. Initially, this model had four main parts. The real system, 
     virtual system, connection between the real and virtual system and virtual simulations\cite{GrievesPLMBook}. 
-    Later, Grieves removed the latter, to simplify the model\cite{Originsofdigitaltwinconcept}. Furthermore, after co-authoring with Vicker in 2010, 
-    Grieves decided to use the NASA-invented Digital Twin word, instead of the information mirroring model\cite{Originsofdigitaltwinconcept}.
+    Later, Grieves removed the latter, to simplify the model\cite{Originsofdigitaltwinconcept}. Lastly, after co-authoring with Vicker in 2010, 
+    Grieves decided to use the NASA-invented "Digital Twin" word, instead of the information mirroring model\cite{Originsofdigitaltwinconcept}.
 
-    Digital twins are highly intricate and adaptable systems that possess the capability to not only respond to environmental 
-    changes but also modify their internal structure \cite{ZHANGUPDATEMETHOD, MobusSystemTheory}. Therefore, ascertaining a 
-    requisite level of quality for the construction of a digital twin is an arduous undertaking.
+    These days, there is evidence that digital twins play a crucial role in the manufacturing industries, 
+    life sciences, healthcare, infrastructure and cities\cite{Review2}.
+    For example, a digital wind farm from General Electric is a good illustration of how building a digital twin helped to design a better turbine, 
+    and later is used to collect and analyze the data from the real system for making the process of the real system more efficient \cite{GeneralElectricWindTurbine}. 
+    Another fascinating example of the use of digital twins is Philips' virtual heart model. Twin of the heart evolves with the  data generated by ultrasonic sensors to calculate 
+    how well the real heart is pumping the blood This information can be used to predict a potential heart failure, allowing for early intervention and potentially life-saving treatment \cite{PhilipsHearth}.
+    Lastly, FELICE is another interesting example of a digital twin application in manufacturing. In the project, twin models of machines/equipment and 
+    agents are utilized to support real-time decision-making, to conduct what-if analyses and experiments.
+To ensure the quality of these digital twins, a specific Verification \& Validation process is implemented ~\cite{FELICE}.
 
-    FELICE is a complex system that addresses a critical problem in robotics which is the effective integration of human and robot abilities in a collaborative setting. 
-    This challenge requires the development of sophisticated algorithms and techniques that facilitate seamless communication, cooperation, and coordination between humans and robotic agents. 
-    By addressing this issue, FELICE tries to represent a significant advancement in the field of robotics and has the potential to enhance the effectiveness and efficiency of a wide range of 
-    human-robot collaborative tasks with the consideration of safety~\cite{FELICE}.
+    The previous studies predominantly focused on the design and implementation of digital twins\cite{Review1, Review2}. 
+    However, a crucial aspect that remains unclear is how to achieve quality in these highly intricate and evolvable systems.
+Therefore, ascertaining the requisite level of quality of a digital twin is an arduous undertaking that requires further research.
 
-    The main purpose of this study is to inspect several artifacts and map the found issues to quality attributes to evaluate the quality of the digital twin for the FELICE project, which is currently in the design phase.~\cite{FELICE}.
-These artifacts included process videos showing the current
-    assembly procedure, a scope definition, a requirements specification, a general and operational conceptual model, 
-    and a discrete event simulation module. We assessed the quality of these artifacts based on five crucial quality attributes: correctness, completeness, fidelity, efficiency, and evolvability.
-
-    %%
-    %%\subsection{Research objective}
-    %%Find an approach to assess the quality of Digital twins~\cite{Jones2020}
-
-    %%\subsection{Research question}\label{section: Research Questions}
-    %%What is the quality of digital twins?
-    %%What is the state art of digital twin quality?
-
-    %%\subsection{Research methodology}
-    %%TODO
+    This paper aims to review the digital twin artifacts utilized in the FELICE project and evaluate the quality issues associated with FELICE's digital twin system~\cite{FELICE}. 
+    The evaluation aims to enhance the scientific understanding of the quality of digital twins.
+The artifacts analyzed in this study include process videos showing the current assembly procedure, a scope definition, a requirements specification, a general and operational conceptual model, and a discrete event simulation module.
+    To evaluate these artifacts, we considered five crucial quality attributes: correctness, completeness, fidelity, efficiency, and evolvability.
 
@@
     \section{Method}
-    The methodology consists of a set of artifacts, manual artifact reviews, mapping quality attributes to the   
-    and evaluation of the results according to the digital twin quality attributes.    
+    The methodology consists of a set of artifacts, manual artifact reviews, mapping quality attributes to the findings, an evaluation of the artifact quality, and lastly, an evaluation of the digital twin quality.
     \subsection{Artifacts}\label{section:Artifacts}
@@
     As a result, the digital twin quality was expressed as a percentage using the following equation:
-    \begin{equation}
-        (totalnumberofselectedattribute/totalnumberofattributes)*100
-    \end{equation}
 
     \begin{figure}[htbp]
-        \includegraphics[scale = 0.35]{DigitalTwinQuality.png}
+        \includegraphics[scale = 0.25]{DigitalTwinQuality.png}
             \caption{Method for the evaluation of the digital twin quality:}
@@
     \section{Results}
-    %%TODO WRITE HERE ONCE AGAIN
-
     \begin{table}[h!]
     \begin{center}
-          \caption{Mapping findings to Quality Attributes: Results of the manual artifact reviews were mapped to quality attributes, which were discussed in \ref{section:Digital Twin Quality Attributes}}
-          \label{tab:Mapping}
-          \begin{tabular}{l@{\hspace{1cm}}l} 
-            \textbf{Findings} & \textbf{Missing Quality Attribute}\\
+    \label{tab:Table1}
+    \caption{Mapping of digital twin attributes to the results of the manual reviews: In cases where an attribute is mapped, the "artifact.qualityattribute.value" is incremented by 1. }
+    \renewcommand{\arraystretch}{1.25}
+    \scalebox{0.70}{
+    \begin{tabular}{l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l}
+        \textbf{Findings} & \textbf{Correctness} & \textbf{Completeness} & \textbf{Fidelity} & \textbf{Efficiency} & \textbf{Evolvability}\\
         \hline
-            Findings 1, 2 and 6 &     Completeness\\
-            Findings 3, 12, 14,15 and 17  &     Correctness, Completeness\\
-            Findings 4 &     Correctness\\
-            Findings 5,9,11,16,20 and 21 &     Evolvability\\
-            Findings 7 &     Correctness, Completeness, Fidelity, Efficiency, Evolvability\\
-            Findings 8 &     Completeness, Fidelity, Evolvability\\
-            Findings 10 &    Correctness, Completeness, Fidelity, Evolvability\\
-            Findings 13 and 19 &    Completeness, Evolvability\\
-            Findings 18&Correctness, Efficiency \\
+        \textbf{Finding 1}  &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
+        \textbf{Finding 2} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
+        \textbf{Finding 3} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
+        \textbf{Finding 4} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
+        \textbf{Finding 5} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
+        \textbf{Finding 6} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
+        \textbf{Finding 7} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
+        \textbf{Finding 8} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
+        \textbf{Finding 9} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
+        \textbf{Finding 10} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
+        \textbf{Finding 11} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
+        \textbf{Finding 12} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
+        \textbf{Finding 13} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
+        \textbf{Finding 14}&~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
+        \textbf{Finding 15} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
+        \textbf{Finding 16} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
+        \textbf{Finding 17} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
+        \textbf{Finding 18} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
+        \textbf{Finding 19} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
+        \textbf{Finding 20} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
+        \textbf{Finding 21} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
     \end{tabular}
+    }
     \end{center}

### 2023-03-06 manuscripts/paper-1/main.tex
Intro-State-Method  Verified

@@
     Furthermore, he introduced the information mirroring model, which was his ideal product lifecycle management tool with only one goal. 
-    The goal was to gather as much information about the real system to minimize the waste of the system's sources such as energy, 
+    The goal was to gather enhanced information about the real system to minimize the waste of the system's sources such as energy, 
     time and material. Initially, this model had four main parts. The real system, 
@@
     These days, there is evidence that digital twins play a crucial role in the manufacturing industries, 
-    life sciences, healthcare, infrastructure and cities\cite{Review2}.
+    life sciences, healthcare, infrastructure and smart cities\cite{Review2}.
     For example, a digital wind farm from General Electric is a good illustration of how building a digital twin helped to design a better turbine, 
@@
     Another fascinating example of the use of digital twins is Philips' virtual heart model. Twin of the heart evolves with the  data generated by ultrasonic sensors to calculate 
-    how well the real heart is pumping the blood This information can be used to predict a potential heart failure, allowing for early intervention and potentially life-saving treatment \cite{PhilipsHearth}.
+    how well the real heart is pumping the blood.
+This information can be used to predict a potential heart failure, allowing for early intervention and potentially life-saving treatment \cite{PhilipsHearth}.
     Lastly, FELICE is another interesting example of a digital twin application in manufacturing. In the project, twin models of machines/equipment and 
-    agents are utilized to support real-time decision-making, to conduct what-if analyses and experiments.
+    agents are utilized to support real-time decision-making and to conduct what-if analysis and experiments.
 To ensure the quality of these digital twins, a specific Verification \& Validation process is implemented ~\cite{FELICE}.
@@
     This paper aims to review the digital twin artifacts utilized in the FELICE project and evaluate the quality issues associated with FELICE's digital twin system~\cite{FELICE}. 
-    The evaluation aims to enhance the scientific understanding of the quality of digital twins.
-The artifacts analyzed in this study include process videos showing the current assembly procedure, a scope definition, a requirements specification, a general and operational conceptual model, and a discrete event simulation module.
+    The evaluation aims to enhance the scientific understanding of the quality of digital twins. The artifacts analyzed in this study include process videos showing the current assembly procedure, 
+    a scope definition, a requirements specification, a general and operational conceptual model, and a discrete event simulation module. 
     To evaluate these artifacts, we considered five crucial quality attributes: correctness, completeness, fidelity, efficiency, and evolvability.
@@
     \section{State of the art on quality}
-    Oxford English Dictionary describes the word quality either as a noun or an adjective. 
-    The adjective form indicates, a high standard or excellence. For example, the phrase quality products imply 
-    that quality adds a high standard state to the product. Several definitions describe quality 
-    as a noun, however, the impactful definition is the quality as a standard of an entity which is measured against the 
-    different or the similar entities\cite{OxfordDictionary}. This definition clearly shows the relativity of quality. In addition, quality is defined 
-    as the degree to which a set of inherent properties of an entity fulfills the given requirements~\cite{ISO9000}.    
-    \subsection{Product quality and Management}
-    A product is a tangible or intangible system that satisfies the needs or wants of a customer. It could be a physical system like a car, or an abstract system, like a digital twin. 
-    Regarding product quality, there are two different aspects~\cite{GrievesPLMBook}.
-    First, quality is an attribute of a product, which meets product specifications. Specifications are mostly defined by the supra-systems subsystems, 
-    such as by the stakeholders within the supra-system,  If the stakeholders' expectations, or needs, are met, we can consider high quality.
-    The ability to execute to a specific usage standard is the second facet of product quality. Since this standardization is usually not controllable, 
-    unlike the first, the system's quality will be determined by how the implied or obligatory standards are fulfilled.
+    The Oxford English Dictionary defines the word "quality" as a noun or an adjective form. The adjective form indicates, 
+    a high standard of excellence as in  "quality products" \cite{OxfordDictionary}. Even though the noun form is defined in multiple ways, the most impactful 
+    definition refers to a  standard of an entity that is measured relative to other entities, whether different or similar \cite{OxfordDictionary}.  
+    Additionally, quality is the degree to which a set of inherent properties of an entity fulfills the given requirements~\cite{ISO9000}.
+    Both of these definitions clearly show the relative aspect of quality, and the following subcategories are the specialization of these definitions.
+    \subsection{Product quality}
+    A product is a tangible or intangible system that satisfies the needs or wants of a customer. 
+    A product can be a physical system like a car, or an abstract system, like a digital twin. Furthermore, product quality is comprised of two aspects~\cite{GrievesPLMBook}.  
+    Firstly, quality is an attribute of a product, which refers to the degree to which a product meets its specifications.
+These product specifications are mostly defined by the supra-systems' subsystems, such as the stakeholders.
+    For this aspect, if the stakeholders' expectations or needs are met,  high quality is considered. The second aspect of product quality is the ability to execute to a specific usage standard.
+    Unlike the first aspect, standardization is not controllable. Therefore, the product's quality is determined by how well the implied or obligatory standards are met~\cite{GrievesPLMBook}.
 
-    Quality management systems(QMS) function to plan and execute the organization's quality policies and goals. 
-    Examples of such systems can be a standard like ISO 9001 which can provide a framework for an organization, or a data-driven methodology such as Six Sigma to reduce defects and improve efficiency.
-    These concepts are not new, for example, ISO 9001 standard has been established in 1987, and is still being regularly updated ~\cite{ISO90012015}. 
     \subsection{Software quality}
-    Software is a combination of programs and data which can be used by virtual 
-    systems as well as a physical system like a computer system. In contrast, hardware 
-    is a physical subsystem of a computer system\cite{OxfordDictionary}.
-
-    Software Quality is determined by how well software fulfills the requirements that were set. However, those requirements  
-    not always reflect what the stakeholders need, hence the quality depends on how accurately these requirements were set \cite{IEE730-2014}. 
-    As a result, functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability 
-    and portability is the standardized eight attributes that measure software quality \cite{ISO/IEC:25010}.
-
-    Software quality management techniques come from already used manufacturing techniques in the industries. For example, product quality assurance has been used as a 
-    software quality management activity with some modifications.
-For example, in manufacturing, products will never exactly meet a specification, due to errors in the machining which results in some tolerance area.
-    But in the software systems, or more precisely in the virtual systems, it's most of the time, not the case. Also, it's nearly impossible to conclude that, 
-    the software product fully meets its specifications. 
-    Hence, most of the quality assessments are subjective processes and as a result, the quality attributes should be inspected subjectively \cite{SoftwareEngineering}.
+    Software is a combination of programs and data that can be utilized by both virtual and physical systems, 
+    such as computer systems\cite{OxfordDictionary}. Its quality is determined by how well it fulfills the requirements that were set. However, 
+    those requirements may not always reflect the needs of the stakeholders, hence the quality depends on how accurately these requirements were set \cite{IEE730-2014}. 
+    As an example, ISO/IEC:25010 has standardized eight attributes, 
+    including functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability, and portability, to measure software quality.
 
     \subsection{Simulation Quality}
-    Simulation models are not merely virtual systems; they are also abstracted systems, 
-    which are nothing more than imitations or, to be more precise, abstractions of real systems. 
-    Every day, simulation of the real systems occurs in the human brain when the prediction of the future outcome or about the 
-    past state of some occurred event required\cite{MobusSystemTheory}.
-However, most of the simulation processes are computer-based with software programs.
-Consequently, the idea of simulation software programs emerges.
-    For example, ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} are examples of these simulation software programs.
+    The human brain simulates real systems abstractly either to predict the future state of the system or to gather information about the past state of the system 
+    \cite{MobusSystemTheory}.
+However, these days, many simulation processes are done by virtual systems.
+For example,  software programs such as ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} enable users
+    to build a simulation model to make predictions and get information about the past - as well as the current state - of the system.  
+    Quality characteristics of these simulation models must be evaluated by the validation and verification techniques \cite{StewartSimulation} \cite{VerificationValidationSergent} \cite{OsmanBalci}.
 
-    Validation and verification are used to evaluate the quality characteristics of the simulation 
-    model \cite{StewartSimulation,VerificationValidationSergent,OsmanBalci}. 
-    Validation is the process of evaluating the simulation quality of the model in comparison to 
-    the real system from the perspective of the model's intended applications.
-    On the other hand, verification is a procedure to 
-    evaluate a simulation model's implementation and its associated 
-    data concerning the conceptual description and specifications of the 
-    model developer\cite{StewartSimulation,VerificationValidationSergent}.
+    Validation is the process of evaluating the simulation quality in comparison to the real system from the perspective of its intended applications. 
+    On the other hand, verification is a procedure to evaluate the implementation of the simulation model and 
+    its associated data concerning the conceptual description and specifications of the model developer\cite{StewartSimulation}\cite{VerificationValidationSergent}. 
+    These techniques are broadly categorized into six areas: informal, static, dynamic, 
+    symbolic, constraint, and formal techniques \cite{balcicategories}\cite{balcitechniques}. Formal techniques involve mathematical formality, whereas informal techniques rely on 
+    human intervention and reasoning. Although mathematical techniques are more precise, informal techniques are more commonly used \cite{balcicategories}.
 
-    Various validation and verification techniques can be employed, which can be broadly categorized into six areas: informal, static, dynamic, symbolic, constraint, 
-    and formal techniques \cite{balcicategories}\cite{balcitechniques}. Formal techniques involve mathematical formality, whereas informal techniques rely on human intervention 
-    and reasoning. Although mathematical techniques are more precise, informal techniques 
-    are more commonly used \cite{balcicategories}.
-Also, the use of informal techniques does not imply a lack of structure, but rather a reliance on human expertise and interpretation \cite{balcitechniques}.
     \subsection{Digital twin quality}
     To analyze the state of the digital twin quality, a literature analysis was executed. 
-    The analysis especially focused on how the digital twin quality is mentioned and assessed within the academic dissertations.
+    The analysis especially focused on how the digital twin quality is mentioned and assessed within the academic dissertations. Therefore, various tools, such as Scopus and Google Scholar were 
+    used to perform an extensive literature analysis on digital twin publications.
+However, due to the vast amount of available literature, the scope of the research was narrowed down, resulting in the identification of
+    150 dissertations linked to digital twin quality, verification and validation.
+After a thorough review of these, only 17 were considered relevant for this paper, and as a result following findings were revealed.
 
-    \subsubsection*{Literature Search Methodology}
-    To conduct a thorough literature review on digital twin publications, tools such as Google Scholar and Scopus are utilized.
-Due to the vast amount of available literature, it is necessary to narrow down the scope of the research.
-    Therefore, a multi-level filtering algorithm is employed to refine the search results.
-
-    The first level of filtering for the literature review on digital twin publications involves specific criteria. These include that dissertation must be written in English and 
-    published in a journal or conference and that the search term must be an exact match. To execute this initial filtration, 
-    the following queries are used for Google Scholar and Scopus respectively: "search term" and ALL ("digital twin quality") AND (LIMIT-TO (LANGUAGE, "English")).
-
-    After the initial filtering, a second level of manual investigation is necessary. The following criteria are used for this level of filtering:    
-    \begin{itemize}
-        \item  Eliminating duplicates
-        \item  Removing dissertations that are not in English
-        \item  Ensuring that selected dissertations have a proper literature review
-        \item  Ensuring that abstract and conclusion are relevant to the search term
-    \end{itemize}
-    If an interesting dissertation(s) would be found during the reading, it will be checked again with the initial filter.
-    \subsubsection*{Literature Search Result}
-    The search for "digital twin quality" initially resulted in 41 hits on Google Scholar and 3 on Scopus. 
-    After the second level of filtering, 6 duplicate dissertations were removed and 10 dissertations that were not in English were also eliminated. 
-    This left only 9 dissertations that met all the criteria and were reviewed.
-
-    The search for "digital twin verification" initially resulted in 19 hits on Google Scholar and none on Scopus. 
-    After the second level of filtering, one duplicate dissertation was removed and two dissertations that were not in 
-    English was also eliminated. As a result, all dissertations were rejected.
-
-    The search for "digital twin validation" initially resulted in 59 hits on Google Scholar and none on Scopus. 
-    After the second level of filtering, 4 duplicate dissertations were removed and 4 
-    dissertations that were not in English were also eliminated. This left only 8 dissertations that met all the criteria and were reviewed.
-
-    After a thorough review of 17 research papers, several significant findings were revealed.
-
-    First, it was noted that Shcherba et al. focuses on the importance of model quality as an observation for a digital twin subsystem. 
-    However, they acknowledged that the quality assessment of the digital twin cannot solely rely on models~\cite{Shcherba}.
-
-    He Zhang et al. developed a consistency evaluation approach for digital twin models, which can be used to assess their quality. 
-    The authors also discuss essential concepts, such as consistency between real and virtual systems and ultra-fidelity models. 
-    This article emphasizes the improvement of the service component of the digital twin~\cite{ZHANGEVALUATIONMETHOD}.
+    First, He Zhang et al. developed a consistency evaluation approach for digital twin models, which can be used to assess their quality. 
+    The authors also discuss essential concepts, such as consistency between real and virtual systems and ultra-fidelity models~\cite{ZHANGEVALUATIONMETHOD}.
 
@@
 
-    Selch et al. present a machine-learning approach based on Bayesian networks to track the quality of the digital twin. 
-    The unique aspect of this study is that the authors determine the contributions of subsystems to forecast the overall quality of the digital twin, 
+    Selch et al. presented a machine-learning approach based on Bayesian networks to track the quality of the digital twin. 
+    The unique aspect of this study is that the authors determined the contributions of subsystems to forecast the overall quality of the digital twin, 
     rather than just analyzing it as a single system. The digital couplings, which are linkages between the subsystems, are also identified as a source of extra uncertainty. 
@@
 
-    Edward Y.
-Hua et al.
-identify five open problems with digital twin model validation, including modeling realism, data uncertainty, system dynamics, use-case alignment, and reporting invalid modes.
-To address these challenges, the authors propose a digital-twin model validation framework.
-The paper also highlights three areas for future research,
+    Edward Y. Hua et al. identify five open problems with digital twin model validation, including modeling realism, data uncertainty, system dynamics, use-case alignment, and reporting invalid modes.
+    To address these challenges, the authors propose a digital-twin model validation framework. The paper also highlights three areas for future research, 
     including uncertainty and sensitivity analysis, model validation of system-of-systems, and combining expert knowledge and collected data ~\cite{ValidationofDigitalTwins}.
@@
     Finally, Shotaro Hamato et al. demonstrated successful real-time anomaly detection using the Unscented Kalman Filter with the digital twin model. 
-    However, determining the appropriate threshold for anomaly detection remains an issue~\cite{JapeneseKalmanFilterCorrectness}.
+    However, determining the appropriate threshold for anomaly detection remains problematic~\cite{JapeneseKalmanFilterCorrectness}.
 
-    Overall, these studies provide valuable insights into various aspects of digital twin quality assessment, 
-    including model consistency, stability, and validation, as well as machine learning-based approaches and real-time anomaly detection. 
-    However, the identified open problems, including modeling realism, data uncertainty, system dynamics, use-case alignment, and reporting invalid modes, 
-    call for further research in the field to improve the quality and reliability of digital twins. Moreover, 
-    the lack of well-defined quality parameters for digital twins poses a significant challenge in ensuring their quality,
-    which necessitates the development of appropriate quality metrics and standards for digital twins.
+    These dissertations provide valuable insights into various aspects of digital twin quality assessment, including model consistency, stability, and validation, as well as machine learning-based approaches and real-time anomaly detection.
+    However, the identified open problems, including modeling realism, data uncertainty, system dynamics, use-case alignment, and reporting invalid modes, call for further research in the field to improve the quality and reliability of digital twins.
+Moreover,
+    the lack of well-defined quality parameters for digital twins puts forward a significant challenge in ensuring their quality, which necessitates the development of appropriate quality metrics and standards for digital twins.
 
@@
     \section{Results}
+
     \begin{table}[h!]

### 2023-03-07 manuscripts/paper-1/main.tex
New image, new table, revisions 1,2,3

@@
 \usepackage{multirow}
+\usepackage{cleveref}
+\usepackage{tabularray}
+\usepackage{dirtree,array}
 
@@
 
-    \textbf{Process Videos:}
-    The project partner provided three videos initially to explain the manual assembly procedures performed at each of the three workstations. From the videos,  
+    \textbf{Process Videos} have been utilized to explain the manual assembly procedures performed at each of the three workstations. From the three videos initially provided by the project partner,  
     the sequence of assembly steps was extracted at least for one product variant.
@@
 
-    \textbf{Scope Definition:}
-    To better understand the context and focus of the digital twin, 
-    the project partner used a methodology based on hierarchical task analysis and the process videos. 
+    \textbf{Scope Definition} was determined using a methodology based on hierarchical task analysis and process videos provided by the project partner, which aids in better understanding the context and focus of the digital twin.
     This resulted in a scope definition that identified entities to be twinned, entities to be tracked, and important areas in the scene. 
@@
 The origin of the requirement was noted to identify the project partner responsible for its creation.
-The category distinguished between functional and non-functional requirements, as well as constraints and standards.
-The priority of each requirement was classified into four levels
+     The category is distinguished between functional and non-functional requirements, as well as constraints and standards. The priority of each requirement was classified into four levels 
     (must-, should-, could-, and would-have) to help prioritize development efforts. 
-    Finally, the rationale provided a clear explanation for each requirement's inclusion in the specification.
+    Finally, the rationale provided a clear explanation for each requirement's implication in the specification.
 
     \textbf{Conceptual Model} was comprised of two parts: a general conceptual model and an operational conceptual model. 
-Both models described the assembly line processes, but the operational conceptual model focused on the specific steps of the assembly process, while the general conceptual model focused on higher-level processes and workflows.
-    The general conceptual model was represented using a general flow chart notation that distinguished between a root node, activity nodes, and decision nodes.
+    Both models described the assembly line processes however the operational conceptual model focused on the specific steps of the assembly process, while the general conceptual model focused on higher-level processes and workflows.
+    The general conceptual model was represented using a general flow chart notation which distinguishes a root node, activity nodes, and decision nodes.
     The operational conceptual model consisted of three spreadsheets, each displaying the sequence of assembly operations performed at one workstation. 
@@
     \textbf{Discrete Event Simulation Model} consisted of seven sections, including two animation sections, two input sections, one output section, one process logic section, and a database section. 
-The animation sections provided a two-dimensional and a three-dimensional representation of the system, which aided in understanding the simulation and for debugging purposes.
+    The animation sections provided a two-dimensional and a three-dimensional representation of the system, 
+    which aided in understanding the simulation and debugging purposes.
 The input sections allowed for the management of inputs to the simulation model, and the output section displayed summary performance indicators about the simulation run.
-    The process logic section contained the process building blocks, such as queues and assembly operations. The database section provided an interface to data sources and sinks.
+    The process logic section contained the process building blocks, such as queues and assembly operations. Lastly, the database section provided an interface to data sources and sinks.
 
@@
     \textbf{Completeness} is a derived word from the word complete, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
-    The adjectival form of complete is a state of having all the necessary or appropriate parts\cite{OxfordDictionary}.
+    The adjectival form used in the study denotes \textit{complete} as a state of having all the necessary or appropriate parts of both systems\cite{OxfordDictionary}.
 
@@
     The concept of fidelity has garnered significant attention in recent
-    years and continues to be an important area of research in digital twins\cite{Review2}\cite{Review1}.
+    years and continues to be an important focus in Digital Twin research\cite{Review2}\cite{Review1}.
 
     \textbf{Efficiency} refers to the quality of being efficient\cite{OxfordDictionary}. Therefore, efficiency is achieving
-    maximum productivity with minimum wasted effort or expense. The concept of efficiency is tightly coupled to productivity, which refers to the quality of being productive,
-    also the word productive can be explained as producing or being able to produce large amounts of goods\cite{OxfordDictionary}.  
-    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum 
-    waste during the process is desired.
+    maximum productivity with minimum wasted effort or expense. It is worth mentioning that the concept of efficiency is tightly intertwined with the concept of productivity, 
+    although it differs from the latter's definition, which is defined as the ability to produce large amounts of goods\cite{OxfordDictionary}.  
+    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired.
 
@@
     However, this concept differs from evolvability in that it only affects a system's internal or functional structure temporarily. 
-    For instance, a digital twin, which is a virtual system, can be designed to be more flexible and scalable, 
+    For instance, a digital twin, which is an evolvable virtual system, can be designed to be more flexible and scalable, 
     allowing for easy updates and the addition of new features\cite{ZHANGUPDATEMETHOD}.
 
-    \subsection{Mapping Digital Twin Attributes to Results of the Manual Reviews}
+    \subsection{Mapping Digital Twin Attributes to Manual Review Results}
     To evaluate the quality of the artifact, the issues were mapped to digital twin attributes. 
@@
 
-    subsection{Artifact Quality Evaluation}
+    \subsection{Artifact Quality Evaluation}
     To evaluate the quality of the digital twin artifacts, the mapped findings were scrutinized and evaluated. 
     The process started by identifying which quality attribute(s) were mapped. 
-    Once identified, the missing attribute(s) was incremented by 1 to determine the quality percentage of the artifact.
+    Once identified, the missing attribute(s) was incremented by 1 to determine the total quality missing attributes of the artifact.
 
@@
     The resulting sum was assigned to the corresponding digital twin quality attribute. 
-    As a result, the digital twin quality was expressed as a percentage using the following equation:
+    As a result, the digital twin quality was expressed with quality attribute values.
 
@@
         \includegraphics[scale = 0.25]{DigitalTwinQuality.png}
-            \caption{Method for the evaluation of the digital twin quality:}
+            \caption{Method for the evaluation of the digital twin quality}
         \label{fig:MethodforDigitalTwinQuality}
@@
 
+    First, to assess digital twin quality, manual reviews for each artifact were conducted (Figure~\ref{fig:QualityInspectonResultsWithArtifacts} ). 
+    As a result, a total of twenty-one quality issues were identified, listed and finally mapped to the digital twin quality attributes(Table~\ref{tab:Table1})(Table~\ref{tab:Table2})(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
+    The mapping process revealed that a total of thirty-eight digital twin quality attributes were lacking in the artifacts(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).  
+    Specifically, 24\% of the quality issues of the digital twin were related to the correctness, 35\%  were related to completeness, 8\%  were related to fidelity, 5\%  were related to efficiency,
+    and finally, 28\% were related to evolvability.
+
+    \begin{table}[h!]
+    \begin{center}
+    ~\label{tab:Table2}
+    ~\caption{Findings from each Artifact}
+    \begin{tabular}{lrr}
+        \toprule
+        \textbf{Artifact Tree}\\
+        \midrule
+        \DTsetlength{0.2em}{0.5em}{0.5em}{0.4pt}{1pt}
+        \begin{minipage}{5cm}\dirtree{%
+        .1 Artifacts.
+        .2 Process Videos.
+        .3 Finding 1.
+        .2 Scope Definition.
+        .3 Finding 2.
+        .2 Requirement Specification.
+        .3 Finding 3.
+        .3 Finding 4.
+        .3 Finding 5.
+        .3 Finding 6.
+        .2 Conceptual Model.
+        .3 Finding 7.
+        .3 Finding 8.
+        .3 Finding 9.
+        .3 Finding 10.
+        .3 Finding 11.
+        .3 Finding 12.
+        .2 Simulation Model.
+        .3 Finding 13.
+        .3 Finding 14.
+        .3 Finding 15.
+        .3 Finding 16.
+        .3 Finding 17.
+        .3 Finding 18.
+        .3 Finding 19.
+        .3 Finding 20.
+        .3 Finding 21.
+        }
+        \end{minipage}
+        \end{tabular}
+        \end{center}
+        \end{table}
+    %TODO BETTER TABLE
     \begin{table}[h!]
@@
         \textbf{Finding 21} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
+        \hline
+        \textbf{Total} &~~~~~~~~~9~~~~~~~~~ & ~~~~~~~~~13~~~~~~~~~ & ~~~~~~~~~3~~~~~~~~~ & ~~~~~~~~~2~~~~~~~~~ & ~~~~~~~~~11~~~~~~~~~ \\
     \end{tabular}
@@
 
-    \textbf{Process Videos Review Results}
-
-    Findings 1  - Even though the videos are well suited for providing a first impression of the production facility 
-    and the current assembly process for one product variant, the other product variants include different assembly operations, 
-    which were not shown in the videos. 
-    Furthermore, the cobot and the adaptive workstation were not part of the assembly process yet,
-     hence the videos do not provide a complete representation of the target system.
-
-    \textbf{Scope Definition Review Results}
-
-    Findings 2 - The scope definition focuses on the physical entities of the shop floor and is consistent with the videos presented in the previous section. 
-    However, the scope definition is incomplete.
-Several entities are only selected for the tracking, hence additional state information such as the failure status of these entities was missing in the digital twin.
-
-    \textbf{Requirements Specification Review Results}
-
-    Findings 3 - Atypical categorization of the digital twin requirements as functional, non-functional, constraint and standard was introduced. 
-    Also, standard categories were considered as a cause of requirements instead of a category of requirements. Furthermore, 
-    the constraint category was considered a non-functional requirement which results in a significant misunderstanding between non-functional 
-    requirements and constraints. Finally, some requirements were described as non-functional requirements instead of functional requirements.
-
-    Findings 4 - Imprecise and unclear statements were found in requirement specifications.
-
-    Findings 5 - Key design decisions were found in the requirement specifications, which results in a considerable decrease in maintainability.
-
-    \textbf{Conceptual  Model Review Results}
-
-    Findings 6 - Conceptual models are not designed to react to unwanted situations.
-
-    Findings 7 - Conceptual model specification was not clear enough, which results in quite some room for interpretations by the stakeholders. 
-    as the use of an unspecified flow chart model is prone to differing interpretations by different stakeholders and probable incorrect understanding of the relations between the sub-systems.
-
-    Findings 8 - The difference between the event triggers and decision nodes was not clear, which decreased the clarity and maintainability of the model considerably.
-
-    Findings 9 - The representation of the model is not great, hence understanding the interactions between the different subprocesses are not clear.
-
-    Findings 10 - The model were lacking great organization tools such as swim lanes and object flows.
-
-    Findings 11 - The assignment of the cobot to micro-operations was not regularly reviewed and updated as the project progresses.
-
-    Findings 12 - Even though the durations of the macro-operations were well-known and studied thoroughly before, the durations of the micro-operations were estimated based on a simple calculation scheme.
-
-    \textbf{Discrete Event Simulation Model Review Results}
-
-    Findings 13 - The input controls in the simulation module was not complete or aligned with the actual inputs that will be provided by another system.
-
-    Findings 14, and 15 - The ranges defined for some events were not validated.
-
-    Findings 16 - Database structures were not updated automatically, instead done manually.
-
-    Findings 17 - The duration of micro-, loading- and unloading-operations of the cobot were based on assumptions rather than actual measurements.
-
-    Findings 18 - The simulation module does not support parallel execution of micro-operations.
-
-    Findings 19 - The interruption mechanism of the assembly line was not considered within the simulation module.
-
-    Findings 20 - The number of micro-operations was hard coded, consequently, the simulation module must be reprogrammed every time, when a new micro-operation is needed.
-
-    Findings 21 - Edge cases were not considered in the simulation module.
-
-    \subsection{Mapping the Issues to Quality Attributes}
-    The analysis revealed that a total of thirty-eight digital twin quality attributes were lacking in these artifacts. \ref{fig:QualityInspectonResultsWithArtifacts}
-    Therefore, to evaluate the quality of the FELICE digital twin, observations are mapped to one or more relevant quality attributes\ref{tab:Mapping}.
-    In addition, the assessment shows that every one of the identified issues was quickly attributed to a specific quality attribute.  
-    Specifically, 24\% of the issues were related to correctness, which indicates an error between the real system and a digital twin system.
-    35\% of the issues were related to completeness, proving that some necessary or appropriate parts are missing.
-    8\% of the issues were related to fidelity, indicating a lack of detail. 5\% of the issues were related to efficiency, indicating poor 
-    performance or excessive resource usage. Finally, 28\% of the issues were related to evolvability, indicating that the system has flexibility or scalability issues.
-
     \section{Discussion}
@@
 
-    The quality assessment of the digital twin encountered some limitations due to the exility of information about the real system.
-Some artifacts provided less information, such as process videos, which only provide a limited perspective of the shopfloor based on the camera's field of view and the skills of the video maker.
+    The quality assessment of the digital twin encountered some limitations due to the exility of information about the real system. Some artifacts provided less information, 
+    such as process videos, which only provide a limited perspective of the shop floor based on the camera's field of view and the skills of the video maker. 
     In contrast, the simulation and conceptual model offer a plethora of aspects to examine and assess, which results in a higher probability of discovering the issues \ref{fig:QualityInspectonResultsWithArtifacts}.
+
+    The reason of why the  most of the issues are related to the evolvability, 
+    completeness and correctness, and less for fidelity and efficiency is due to the stage that the FELICE project is in.
+Not only the exility of the information is the limiting factor, also the visibility of the information
+    is also an interesting factor. Therefore, evolvability, completeness and correctness are easier to map and detect , rather than fidelity and efficiency.
+
+    Person dependent, also not everything is written, memory problem, completeness, 
+    issuee finding sometimes even though the issue is not there, still assesed as a issue, assuming that person is correct
+
+    The write a protocol, timing ,hard to cover everything,
 

### 2023-03-11 manuscripts/paper-1/main.tex
Better table, some modifications

@@
     The mapping process revealed that a total of thirty-eight digital twin quality attributes were lacking in the artifacts(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).  
-    Specifically, 24\% of the quality issues of the digital twin were related to the correctness, 35\%  were related to completeness, 8\%  were related to fidelity, 5\%  were related to efficiency,
+    Specifically, 24\% of the quality issues of the digital twin were related to correctness, 35\%  were related to completeness, 8\%  were related to fidelity, 5\%  were related to efficiency,
     and finally, 28\% were related to evolvability.
 
+    \subsection{Example Findings}
+
+    To Three examples illustrate the potential 
+    12 - Conceptual Model
+    17 - Simulation Model
+    20 - Simulation Model
+    First: the discrete event simulation model originally enforced a strictly sequential execution of operations.
+    However, the human and the cobot can work in parallel, and therefore execute operations also in parallel.
+    This issue has been solved already in a later version of the discrete event simulation model.
+
+    F12 - **Even though the durations of the macro-operations were well-known and studied throughly before, the durations of the micro-operations were estimated based on a simple calculation scheme.
+**Completeness, Correctness.****
+
+    This issue is related to the correctness and completeness of the operational conceptual model.
+While the durations of the macro-operations are well-known and derived from a previous study, the durations of the micro-operations are estimated based on a simple calculation scheme.
+This introduces a risk of inaccuracy and incompleteness in the model, which could affect the overall performance of the digital twin.
+Validating the durations of the micro-operations is necessary to ensure the correctness and completeness of the model, but this validation might not be feasible until the entire
+    FELICE system is operational and proper data can be collected. Therefore, this issue should be addressed in the future to ensure the accuracy of the digital twin.
+
+    **F17 - The duration of micro-, loading- and unloading-operations of the cobot were based on assumptions rather than actual measurements.
+    **Correctness, Completeness****
+
+    Second: The original discrete event simulation model originally enforced a fixed number of operations per workstation.
+    This might be okay for now, but what if the workstations and the workflows change in the future?
+    In such cases, adapting the discrete event simulation model might take a substantial some effort.
+
+    **This finding relates to the completeness and fidelity aspects of the DES module. The durations of micro-operations as well as the loading 
+    and unloading operations of the cobot are important factors that affect the accuracy of the simulation. The fact that these values are based 
+    on assumptions rather than actual measurements means that there is a risk of inaccuracy in the simulation results. In terms of completeness, 
+    the module is not able to provide a fully accurate simulation because it is based on assumptions that have not been validated. 
+    In terms of fidelity, the module may not accurately reflect the behavior of the real system due to the potential inaccuracy of these assumptions.
+    However, it should be noted that this issue is due to limitations in the data collection process rather than any shortcomings in the design of the DES module itself.**
+
+    F20 - **Number of micro-operations were hardcoded, consequently, the DES module must be reprogrammed everytime, when a new micro-operation is needed.** 
+    **Evolvability**
+
+    **Based on the given finding, the issue with the process logic section is related to its maintainability and adaptability. 
+    The DES module has a hardcoded number of micro-operations that can be performed at a single workstation, which means that the module must be reprogrammed every time 
+    a different number of micro-operations is required. This issue could impact the maintainability and adaptability of the DES module. It is suggested that the number of 
+    micro-operations per workstation can be configured instead to address this issue. However, it is also mentioned that the current number of micro- 
+    and macro-operations allows the generation of 272 workflows, which provides a solid base for look-ahead and optimization purposes and what-if analysis to be executed by a human end-user.**
+
+    Third: The different workflow variants, that can be executed on the assembly line, are managed entirely manually.
+    However, the workflow variants mostly differ in the assignment of operations to human and cobot.
+    Therefore, one can imagine a technique to generate workflow variants automatically, which would greatly improve evolvability.
     \begin{table}[h!]
     \begin{center}
-    ~\label{tab:Table2}
-    ~\caption{Findings from each Artifact}
-    \begin{tabular}{lrr}
-        \toprule
-        \textbf{Artifact Tree}\\
-        \midrule
-        \DTsetlength{0.2em}{0.5em}{0.5em}{0.4pt}{1pt}
-        \begin{minipage}{5cm}\dirtree{%
+    \label{tab:Table2}
+    \caption{adfasdfadf}
+    \scalebox{0.8}{
+        \begin{tabular}{llllll}
+            \multicolumn{1}{c} {Findings} & \multicolumn{1}{c} {\textbf{\textit{Correctness}}} & \multicolumn{1}{c}{\textbf{\textit{Completeness}}} 
+            & \multicolumn{1}{c}{\textbf{\textit{Fidelity}}} & \multicolumn{1}{c}{\textbf{\textit{Efficiency}}} & \multicolumn{1}{c}{\textbf{\textit{Evolvability}}} \\
+            \begin{minipage}{4cm}\dirtree{%
                 .1 Artifacts.
@@
                 .3 Finding 2.
-        .2 Requirement Specification.
+                .2 Requirement Spec.
                 .3 Finding 3.
@@
                 .3 Finding 21.
+            }\end{minipage}
+            &
+            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
+            \begin{minipage}{2cm}\dirtree{%
+                .1 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+            }\end{minipage}
+            &
+            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
+            \begin{minipage}{2cm}\dirtree{%
+                .1 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+            }\end{minipage}
+            &
+            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
+            \begin{minipage}{2cm}\dirtree{%
+                .1 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+            }\end{minipage}
+            &
+            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
+            \begin{minipage}{2cm}\dirtree{%
+                .1 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+            }\end{minipage}
+            &
+            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
+            \begin{minipage}{2cm}\dirtree{%
+                .1 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .2 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+                .3 ~~~~~x.
+            }\end{minipage}
+        \end{tabular}
     }
-        \end{minipage}
-        \end{tabular}
 \end{center}
@@
         \hline
+        \textbf{Process Videos}&~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ \\
         \textbf{Finding 1} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
+        \textbf{Scope Definition}&~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ \\
         \textbf{Finding 2} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
+        \textbf{Requirement Specification}&~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ \\
         \textbf{Finding 3} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
@@
         \textbf{Finding 6} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
+        \textbf{Conceptual Model}&~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ \\
         \textbf{Finding 7} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
@@
         \textbf{Finding 12} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
+        \textbf{Simulation Model} &~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ \\
         \textbf{Finding 13} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\

### 2023-03-15 manuscripts/paper-1/main.tex
Results are done

--- 2023-03-07 manuscripts/paper-1/main.tex
@@
 \usepackage{listings}
+\usepackage{float}
 \usepackage{graphicx}
@@
 \usepackage{dirtree,array}
+\usepackage{subcaption}
 
@@
     The manual review included, audits, inspections, reviews, structural analysis and walkthroughs 
-    with the project partners which was inspired by Balci's manual review works \cite{balcitechniques}.
+    with the project partners which was inspired by Balci's manual review works~\cite{balcitechniques}.
 
@@
 
-    \textbf{Correctness} is a  derived word from the adjective correct, which means that something is error-free regarding fact or truth. 
-    In the context of the digital twins, the fact or truth is the real system hence, correctness is a grade of quality, 
-    that indicates an error between the real system and a digital twin system.
-    Meanwhile, the quality of being correct is described by the term accuracy \cite{OxfordDictionary}.
+    \textbf{Correctness} is a  derived word from the adjective \textit{correct}, which means that the entity is error-free regarding fact or truth. 
+    In the context of the digital twins, the fact or truth is the real system hence, \textit{correctness} is a grade of quality, 
+    that indicates an error between the real system and a digital twin system (Figure~\ref{fig:CorrectnessAndCompleteness}). This 
+    Meanwhile, the quality of being \textit{correct} is described by the term accuracy \cite{OxfordDictionary}.
 
-    \textbf{Completeness} is a derived word from the word complete, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
-    The adjectival form used in the study denotes \textit{complete} as a state of having all the necessary or appropriate parts of both systems\cite{OxfordDictionary}.
+    \textbf{Completeness} is a derived word from the word  \textit{complete}, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
+    The adjectival form used in the study denotes \textit{complete} as a state of having all the necessary or appropriate parts according to the real system 
+    (Figure~\ref{fig:CorrectnessAndCompleteness}). Additionally, subaspects of completeness, which are \textit{incompleteness} and \textit{overcompleteness} 
+    were inspected but identified as a completeness issue.
+
+    \begin{figure}
+
+        \centering
+            \includegraphics[width = 1\textwidth]{Correctness and Completeness.png}
+            \caption{Correctness and Completeness}\label{fig:CorrectnessAndCompleteness}
+    \end{figure}
 
     \textbf{Fidelity} refers to the degree of exactness with which the real system is copied and represented. 
-    Low fidelity indicates a simplified representation, while high fidelity refers to an accurate and detailed representation of the real system \cite{Review2}. 
+    Low fidelity indicates a simplified representation, 
+    while high fidelity refers to an accurate and detailed representation of the real system~\cite{Review2} (Figure~\ref{fig:EfficiencyandFidelity}). 
     The concept of fidelity has garnered significant attention in recent
@@
 
-    \textbf{Efficiency} refers to the quality of being efficient\cite{OxfordDictionary}. Therefore, efficiency is achieving
-    maximum productivity with minimum wasted effort or expense. It is worth mentioning that the concept of efficiency is tightly intertwined with the concept of productivity, 
+    \textbf{Efficiency} refers to the quality of being efficient\cite{OxfordDictionary}. 
+    Therefore, efficiency is achieving maximum productivity with minimum wasted effort or expense (Figure~\ref{fig:EfficiencyandFidelity}). 
+    It is worth mentioning that the concept of efficiency is tightly intertwined with the concept of productivity, 
     although it differs from the latter's definition, which is defined as the ability to produce large amounts of goods\cite{OxfordDictionary}.  
     For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired.
+
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 1\textwidth]{Efficiency and Fidelity.png}
+        \caption{Efficiency and Fidelity}~\label{fig:EfficiencyandFidelity}
+    \end{figure}
 
@@
     allowing for easy updates and the addition of new features\cite{ZHANGUPDATEMETHOD}. 
+    Furthermore, the evolvability of the digital twin was assessed based on the quantity of effort, which is a neccessaryy resource to initiate transformation
+    within the system (Figure~\ref{fig:Evolvability}).
+
+    \begin{figure}[htbp]
+        \includegraphics[width = 1\textwidth]{Evolvability.png}
+        \caption{Evolvability}
+        ~\label{fig:Evolvability}
+    \end{figure}
 
@@
     \begin{figure}[htbp]
-        \includegraphics[scale = 0.35]{RequirementSpecifications.png}
+        \includegraphics[scale = 0.30]{RequirementSpecifications.png}
         \caption{Method for the evaluation of the digital twin artifact quality: Artifact. finding indicates that the finding belongs to the artifact, while -> indicates mapping}
@@
 
-    First, to assess digital twin quality, manual reviews for each artifact were conducted (Figure~\ref{fig:QualityInspectonResultsWithArtifacts} ). 
-    As a result, a total of twenty-one quality issues were identified, listed and finally mapped to the digital twin quality attributes(Table~\ref{tab:Table1})(Table~\ref{tab:Table2})(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
-    The mapping process revealed that a total of thirty-eight digital twin quality attributes were lacking in the artifacts(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).  
-    Specifically, 24\% of the quality issues of the digital twin were related to the correctness, 35\%  were related to completeness, 8\%  were related to fidelity, 5\%  were related to efficiency,
-    and finally, 28\% were related to evolvability.
+    %TODO REWRITE HERE FOR NOVELTY
+    First, to assess digital twin quality,
+    manual reviews for each artifact were conducted (Figure~\ref{fig:QualityInspectonResultsWithArtifacts} ). 
+    As a result, a total of twenty-one quality issues were identified,
+    listed and finally mapped to the digital twin quality attributes(Table~\ref{tab:Table1})(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
+    The mapping process 
+    revealed that a total of thirty-eight digital twin quality attributes were 
+    lacking in the artifacts(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).  
+    Specifically, 23\% of the quality issues of the digital twin were related to correctness, 
+    which indicates an error between the real- and digital twin system. 36\%  were related to completeness, 
+    proving that some necessary or appropriate parts were missing.
+    8\%  were related to fidelity, indicating a lack of detail. 
+    5\%  were related to efficiency, indicating poor performance or excessive resource usage.
+    and finally, 28\% were related to evolvability, indicating that the system was unresponsive to the environment and was not flexible or scalable.
+
+    \subsection{Example Findings}  
+    Two examples(Finding 12, Finding 18) are given to the reader o illustrate 
+    the results of the manual review as well as the mapping to the digital twin quality attributes.
+
+    \subsubsection{Conceptual Model-Finding 12}
+
+    The duration of the micro-operations in the conceptual model was calculated using a simple calculation 
+    scheme based on the duration of the corresponding macro-operations,
+     which were well-known from a prior well-conducted study. 
+    However, relying on estimated, 
+    simplified calculations for the micro-operation durations,
+    suggests that the digital twin conceptual model suffers from issues of correctness and completeness(Table~\ref{tab:Table1}) .
+
+    \subsubsection{Simulation Model-Finding 18 }
+        The discrete event simulation model enforced a strictly sequential execution of micro-operations,
+        which precludes the support of parallel execution. 
+        However, machine-human collaboration on a task, needs a parallel execution, especially when the cobot overtakes certain micro-operations. 
+        Thus, the exclusion of parallel executions indicates that the simulation model was incomplete,
+        at the same time using the wrong type of execution highlights its inaccuracies(Table~\ref{tab:Table1}) .
+
+    \begin{figure}[htbp]
+            \centering
+            \includegraphics[scale = 0.35]{quality_inspection_results_with_artifacts.png}
+            \caption{Quality Inspection Results Categorized with Artifacts: X-Axis represents artifacts in section~\ref{section:Artifacts}, 
+            Y-Axis represents the number of missing quality attributes found for each artifact, 
+            and lastly, each digital twin quality attribute is shown by the colors.}
+            \label{fig:QualityInspectonResultsWithArtifacts}
+    \end{figure}
 
@@
     \begin{center}
-    ~\label{tab:Table2}
-    ~\caption{Findings from each Artifact}
-    \begin{tabular}{lrr}
-        \toprule
-        \textbf{Artifact Tree}\\
-        \midrule
-        \DTsetlength{0.2em}{0.5em}{0.5em}{0.4pt}{1pt}
-        \begin{minipage}{5cm}\dirtree{%
+    \caption{Mapping of digital twin attributes to the results of the manual reviews: In cases where an attribute is mapped shown by `X'.}
+    \label{tab:Table1}
+    \scalebox{0.80}{
+        \begin{tabular}{llllll}
+            \multicolumn{1}{c}{\textbf{Findings}} & \multicolumn{1}{c} {\textbf{Correctness}} & \multicolumn{1}{c}{\textbf{Completeness}} 
+            & \multicolumn{1}{c}{\textbf{Fidelity}} & \multicolumn{1}{c}{\textbf{Efficiency}} & \multicolumn{1}{c}{\textbf{Evolvability}} \\
+            \hline
+            \begin{minipage}{4cm}\dirtree{%
                 .1 Artifacts.
@@
                 .3 Finding 2.
-        .2 Requirement Specification.
+                .2 Requirement Specs.
                 .3 Finding 3.
@@
                 .3 Finding 21.
-        }
-        \end{minipage}
-        \end{tabular}
-        \end{center}
-        \end{table}
-    %TODO BETTER TABLE
-    \begin{table}[h!]
-    \begin{center}
-    \label{tab:Table1}
-    \caption{Mapping of digital twin attributes to the results of the manual reviews: In cases where an attribute is mapped, the "artifact.qualityattribute.value" is incremented by 1. }
-    \renewcommand{\arraystretch}{1.25}
-    \scalebox{0.70}{
-    \begin{tabular}{l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l}
-        \textbf{Findings} & \textbf{Correctness} & \textbf{Completeness} & \textbf{Fidelity} & \textbf{Efficiency} & \textbf{Evolvability}\\
-        \hline
-        \textbf{Finding 1} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
-        \textbf{Finding 2} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
-        \textbf{Finding 3} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
-        \textbf{Finding 4} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
-        \textbf{Finding 5} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
-        \textbf{Finding 6} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
-        \textbf{Finding 7} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
-        \textbf{Finding 8} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
-        \textbf{Finding 9} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
-        \textbf{Finding 10} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
-        \textbf{Finding 11} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
-        \textbf{Finding 12} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
-        \textbf{Finding 13} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
-        \textbf{Finding 14}&~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
-        \textbf{Finding 15} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
-        \textbf{Finding 16} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
-        \textbf{Finding 17} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
-        \textbf{Finding 18} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
-        \textbf{Finding 19} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
-        \textbf{Finding 20} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
-        \textbf{Finding 21} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
-        \hline
-        \textbf{Total} &~~~~~~~~~9~~~~~~~~~ & ~~~~~~~~~13~~~~~~~~~ & ~~~~~~~~~3~~~~~~~~~ & ~~~~~~~~~2~~~~~~~~~ & ~~~~~~~~~11~~~~~~~~~ \\
+            }\end{minipage}
+            &
+            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
+            \begin{minipage}{2cm}\dirtree{%
+                .1 \empty.
+                .2 \empty.
+                .3 ~~~~~0.
+                .2 \empty.
+                .3 ~~~~~0.
+                .2 \empty.
+                .3 ~~~~~X.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .2 \empty.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .3 ~~~~~X.
+                .2 \empty.
+                .3 ~~~~~0.
+                .3 ~~~~~X.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .3 ~~~~~X.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+            }\end{minipage}
+            &
+            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
+            \begin{minipage}{2cm}\dirtree{%
+                .1 \empty.
+                .2 \empty.
+                .3 ~~~~~X.
+                .2 \empty.
+                .3 ~~~~~X.
+                .2 \empty.
+                .3 ~~~~~X.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .3 ~~~~~X.
+                .2 \empty.
+                .3 ~~~~~X.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .3 ~~~~~X.
+                .2 \empty.
+                .3 ~~~~~X.
+                .3 ~~~~~X.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+            }\end{minipage}
+            &
+            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
+            \begin{minipage}{2cm}\dirtree{%
+                .1 \empty.
+                .2 \empty.
+                .3 ~~~~~0.
+                .2 \empty.
+                .3 ~~~~~0.
+                .2 \empty.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .2 \empty.
+                .3 ~~~~~X.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .2 \empty.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+            }\end{minipage}
+            &
+            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
+            \begin{minipage}{2cm}\dirtree{%
+                .1 \empty.
+                .2 \empty.
+                .3 ~~~~~0.
+                .2 \empty.
+                .3 ~~~~~0.
+                .2 \empty.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .2 \empty.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .2 \empty.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+            }\end{minipage}
+            &
+            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
+            \begin{minipage}{2cm}\dirtree{%
+                .1 \empty.
+                .2 \empty.
+                .3 ~~~~~0.
+                .2 \empty.
+                .3 ~~~~~0.
+                .2 \empty.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .2 \empty.
+                .3 ~~~~~X.
+                .3 ~~~~~X.
+                .3 ~~~~~X.
+                .3 ~~~~~X.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .2 \empty.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~X.
+                .3 ~~~~~0.
+                .3 ~~~~~0.
+                .3 ~~~~~X.
+                .3 ~~~~~X.
+                .3 ~~~~~x.
+            }\end{minipage}
         \end{tabular}
@@
 \end{table}
-
-    \begin{figure}[htbp]
-        \includegraphics[scale = 0.40]{quality_inspection_results_with_artifacts.png}
-        \caption{Quality Inspection Results Categorized with Artifacts: X-Axis represents artifacts in \ref{section:Artifacts}, Y-Axis represents the number of missing quality attributes found for each artifact,
-        and lastly, each digital twin quality attribute is shown by the colors.}
-        \label{fig:QualityInspectonResultsWithArtifacts}
-    \end{figure}
 
@@
 
-    The quality assessment of the digital twin encountered some limitations due to the exility of information about the real system. Some artifacts provided less information, 
+    The quality assessment of the digital twin encountered limitations due to the exility of information about the real system. Some artifacts provided less information, 
     such as process videos, which only provide a limited perspective of the shop floor based on the camera's field of view and the skills of the video maker. 
-    In contrast, the simulation and conceptual model offer a plethora of aspects to examine and assess, which results in a higher probability of discovering the issues \ref{fig:QualityInspectonResultsWithArtifacts}.
-
-    The reason of why the  most of the issues are related to the evolvability, 
-    completeness and correctness, and less for fidelity and efficiency is due to the stage that the FELICE project is in.
-Not only the exility of the information is the limiting factor, also the visibility of the information
-    is also an interesting factor. Therefore, evolvability, completeness and correctness are easier to map and detect , rather than fidelity and efficiency.
+    In contrast, the simulation and conceptual model offer a plethora of aspects to examine and assess, which results in a higher probability of discovering the issues~\ref{fig:QualityInspectonResultsWithArtifacts}.
 

### 2023-03-17 manuscripts/paper-1/main.tex
Last_Draft

@@
 
-    These days, there is evidence that digital twins play a crucial role in the manufacturing industries, 
+    In recent years, there is evidence that digital twins play a crucial role in the manufacturing industries, 
     life sciences, healthcare, infrastructure and smart cities\cite{Review2}.
     For example, a digital wind farm from General Electric is a good illustration of how building a digital twin helped to design a better turbine, 
-    and later is used to collect and analyze the data from the real system for making the process of the real system more efficient \cite{GeneralElectricWindTurbine}. 
-    Another fascinating example of the use of digital twins is Philips' virtual heart model. Twin of the heart evolves with the  data generated by ultrasonic sensors to calculate 
+    which was used to collect and analyze the data from the real system for making the process of the real system more efficient~\cite{GeneralElectricWindTurbine}. 
+    Another fascinating example of the use of digital twins is Philips' virtual heart model. The twin of the heart evolves with the data generated by ultrasonic sensors to calculate 
     how well the real heart is pumping the blood.
-This information can be used to predict a potential heart failure, allowing for early intervention and potentially life-saving treatment \cite{PhilipsHearth}.
+This information can be used to predict a potential heart failure, allowing for early intervention and potentially life-saving treatment~\cite{PhilipsHearth}.
     Lastly, FELICE is another interesting example of a digital twin application in manufacturing. In the project, twin models of machines/equipment and 
-    agents are utilized to support real-time decision-making and to conduct what-if analysis and experiments.
-To ensure the quality of these digital twins, a specific Verification \& Validation process is implemented ~\cite{FELICE}.
+    agents are utilized to support real-time decision-making and to conduct what-if analysis and experiments~\cite{FELICE}.
 
@@
 
-    This paper aims to review the digital twin artifacts utilized in the FELICE project and evaluate the quality issues associated with FELICE's digital twin system~\cite{FELICE}. 
-    The evaluation aims to enhance the scientific understanding of the quality of digital twins. The artifacts analyzed in this study include process videos showing the current assembly procedure, 
+    This paper aims not only to review the digital twin artifacts utilized in the FELICE project and evaluate the quality issues associated with them~\cite{FELICE}. 
+    also, targets to enhance the scientific understanding of the quality of digital twins. The artifacts analyzed in this study include process videos showing the current assembly procedure, 
     a scope definition, a requirements specification, a general and operational conceptual model, and a discrete event simulation module. 
@@
     such as computer systems\cite{OxfordDictionary}. Its quality is determined by how well it fulfills the requirements that were set. However, 
-    those requirements may not always reflect the needs of the stakeholders, hence the quality depends on how accurately these requirements were set \cite{IEE730-2014}. 
+    those requirements may not always reflect the needs of the stakeholders, hence the quality depends on how accurately these requirements were set~\cite{IEE730-2014}. 
     As an example, ISO/IEC:25010 has standardized eight attributes, 
@@
 For example,  software programs such as ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} enable users
-    to build a simulation model to make predictions and get information about the past - as well as the current state - of the system.  
-    Quality characteristics of these simulation models must be evaluated by the validation and verification techniques \cite{StewartSimulation} \cite{VerificationValidationSergent} \cite{OsmanBalci}.
+    to build a simulation model to make predictions and get information about the past- as well as the current state of the system.
 
+    Quality characteristics of these simulation models must be evaluated by the validation and verification techniques~\cite{StewartSimulation,VerificationValidationSergent,OsmanBalci}.
 Validation is the process of evaluating the simulation quality in comparison to the real system from the perspective of its intended applications.
     On the other hand, verification is a procedure to evaluate the implementation of the simulation model and 
-    its associated data concerning the conceptual description and specifications of the model developer\cite{StewartSimulation}\cite{VerificationValidationSergent}. 
+    its associated data concerning the conceptual description and specifications of the model developer\cite{StewartSimulation,VerificationValidationSergent}. 
     These techniques are broadly categorized into six areas: informal, static, dynamic, 
-    symbolic, constraint, and formal techniques \cite{balcicategories}\cite{balcitechniques}. Formal techniques involve mathematical formality, whereas informal techniques rely on 
+    symbolic, constraint, and formal techniques \cite{balcicategories,balcitechniques}. Formal techniques involve mathematical formality, whereas informal techniques rely on 
     human intervention and reasoning. Although mathematical techniques are more precise, informal techniques are more commonly used \cite{balcicategories}.
@@
 
+    %%TODO
     \textbf{Discrete Event Simulation Model} consisted of seven sections, including two animation sections, two input sections, one output section, one process logic section, and a database section. 
@@
     In the context of the digital twins, the fact or truth is the real system hence, \textit{correctness} is a grade of quality, 
-    that indicates an error between the real system and a digital twin system (Figure~\ref{fig:CorrectnessAndCompleteness}). This 
-    Meanwhile, the quality of being \textit{correct} is described by the term accuracy \cite{OxfordDictionary}.
+    that indicates an error between the real system and a digital twin system (Figure~\ref{fig:CorrectnessAndCompleteness}).
+    Meanwhile, the quality of being \textit{correct} is described by the term accuracy~\cite{OxfordDictionary}.
 
+    %%TODO
     \textbf{Completeness} is a derived word from the word  \textit{complete}, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
@@
             \includegraphics[width = 1\textwidth]{Correctness and Completeness.png}
-            \caption{Correctness and Completeness}\label{fig:CorrectnessAndCompleteness}
+            \caption{Incorrect  (a) and incomplete (b) status has been demonstrated with a 
+            simplified finite state machine. Incorrectness can be observed in the behavior 
+            of the machine after 2 state transitions. Incompleteness, on the other hand, can be observed in 
+            the missing state. It should be noted that, even though the second state machine is missing a 
+            component, it shows the right behavior, hence it is correct. }\label{fig:CorrectnessAndCompleteness}
     \end{figure}
@@
     The concept of fidelity has garnered significant attention in recent
-    years and continues to be an important focus in Digital Twin research\cite{Review2}\cite{Review1}.
+    years and continues to be an important focus in Digital Twin research~\cite{Review2,Review1}.
 
-    \textbf{Efficiency} refers to the quality of being efficient\cite{OxfordDictionary}. 
-    Therefore, efficiency is achieving maximum productivity with minimum wasted effort or expense (Figure~\ref{fig:EfficiencyandFidelity}). 
-    It is worth mentioning that the concept of efficiency is tightly intertwined with the concept of productivity, 
-    although it differs from the latter's definition, which is defined as the ability to produce large amounts of goods\cite{OxfordDictionary}.  
-    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired.
+    \textbf{Efficiency} refers to the quality of being efficient~\cite{OxfordDictionary}. 
+    Therefore, \textit{efficiency} is achieving maximum productivity with minimum wasted resources (Figure~\ref{fig:EfficiencyandFidelity}). 
+    It is worth mentioning that the concept of \textit{efficiency} is tightly coupled with the notion of productivity, 
+    although \textit{efficiency} differs from the latter's definition, which is defined as the capability to produce large amounts of goods~\cite{OxfordDictionary}.  
+    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired (Figure~\ref{fig:EfficiencyandFidelity}).
 
@@
         \includegraphics[width = 1\textwidth]{Efficiency and Fidelity.png}
-        \caption{Efficiency and Fidelity}~\label{fig:EfficiencyandFidelity}
+        \caption{Fidelity (a) and efficiency (b) levels have been demonstrated with simplified CAD drawings and 
+        finite state machines.}~\label{fig:EfficiencyandFidelity}
     \end{figure}
@@
     structure\cite{MobusSystemTheory}. Another term to describe the response to changes in the environment is adaptability.
-    However, this concept differs from evolvability in that it only affects a system's internal or functional structure temporarily. 
+    However, this concept differs from \textit{evolvability} in that it only affects a system's internal or functional structure temporarily. 
     For instance, a digital twin, which is an evolvable virtual system, can be designed to be more flexible and scalable, 
     allowing for easy updates and the addition of new features\cite{ZHANGUPDATEMETHOD}. 
-    Furthermore, the evolvability of the digital twin was assessed based on the quantity of effort, which is a neccessaryy resource to initiate transformation
+    Furthermore, the evolvability of the digital twin was assessed based on the quantity of effort, which is a necessary resource to initiate transformation
     within the system (Figure~\ref{fig:Evolvability}).
@@
         \includegraphics[width = 1\textwidth]{Evolvability.png}
-        \caption{Evolvability}
-        ~\label{fig:Evolvability}
+        \caption{Evolvability has been demonstrated with simplified finite state machines. 
+        Evolving the machines on the left side, needed effort 
+        and the evolved finite state machines on the right side can be observed.}~\label{fig:Evolvability}
     \end{figure}
@@
     To begin this process, the findings were collected from the manual review, followed by an inspection of the findings to determine which digital twin qualities were absent. 
-    Finally, the findings were mapped to the relevant missing quality attribute(s) and submitted for artifact quality evaluation.
+    Finally, the findings were mapped to the relevant missing quality attribute(s) and submitted for artifact quality evaluation (Figure~\ref{fig:RequirementSpecifications}).
 
@@
     The process started by identifying which quality attribute(s) were mapped. 
-    Once identified, the missing attribute(s) was incremented by 1 to determine the total quality missing attributes of the artifact.
+    Once identified, the missing attribute(s) was incremented by 1 to determine the total quality of missing attributes of the artifact(Figure~\ref{fig:RequirementSpecifications}).
 
@@
     \subsection{Digital Twin Quality Evaluation}
-    To assess the quality of the digital twin, the values obtained from evaluating each artifact's quality are collected and summed. 
-    The resulting sum was assigned to the corresponding digital twin quality attribute. 
-    As a result, the digital twin quality was expressed with quality attribute values.
+    To determine the quality of the digital twin, 
+    the values obtained from evaluating each artifact's quality were collected and summed. 
+    Furthermore, the value of the sum was assigned to the related digital twin quality attribute. 
+    As a result, the digital twin quality was demonstrated with quality attribute values (Figure~\ref{fig:DigitalTwinQuality}).
 
@@
 
-    %TODO REWRITE HERE FOR NOVELTY
     First, to assess digital twin quality,
@@
     As a result, a total of twenty-one quality issues were identified,
-    listed and finally mapped to the digital twin quality attributes(Table~\ref{tab:Table1})(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
+    listed, and finally mapped to the digital twin quality attributes(Table~\ref{tab:Table1})(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
     The mapping process 
@@
     Specifically, 23\% of the quality issues of the digital twin were related to correctness, 
-    which indicates an error between the real- and digital twin system. 36\%  were related to completeness, 
-    proving that some necessary or appropriate parts were missing.
-    8\%  were related to fidelity, indicating a lack of detail. 
-    5\%  were related to efficiency, indicating poor performance or excessive resource usage.
-    and finally, 28\% were related to evolvability, indicating that the system was unresponsive to the environment and was not flexible or scalable.
+    which indicates an error between the real- and digital twin system. Furthermore, 36\%  were related 
+    to completeness, proving that some necessary or appropriate parts were missing.
+    Moreover, 8\%  were related to fidelity, indicating a lack of detail. 
+    In addition, 5\%  were related to efficiency, indicating poor performance or excessive resource usage.
+    And finally, 28\% were related to evolvability, indicating that the system was unresponsive 
+    to the environment and was not flexible or scalable.
 
     \subsection{Example Findings}  
-    Two examples(Finding 12, Finding 18) are given to the reader o illustrate 
+    Two examples(Finding 12, Finding 18) are given to the reader to illustrate 
     the results of the manual review as well as the mapping to the digital twin quality attributes.
 
-    \subsubsection{Conceptual Model-Finding 12}
+    \subsubsection{Conceptual Model-Finding 12:}
 
@@
 
-    \subsubsection{Simulation Model-Finding 18 }
+    \subsubsection{Simulation Model-Finding 18:}
         The discrete event simulation model enforced a strictly sequential execution of micro-operations,
@@
         Thus, the exclusion of parallel executions indicates that the simulation model was incomplete,
-        at the same time using the wrong type of execution highlights its inaccuracies(Table~\ref{tab:Table1}) .
+        at the same time, using the wrong type of execution highlights its inaccuracies(Table~\ref{tab:Table1}) .
 
@@
     \begin{center}
-    \caption{Mapping of digital twin attributes to the results of the manual reviews: In cases where an attribute is mapped shown by `X'.}
-    \label{tab:Table1}
+    \caption{Mapping of digital twin attributes to the results of the 
+    manual reviews: Cases where an attribute is mapped, were marked by `X'.}\label{tab:Table1}
     \scalebox{0.80}{
@@
 
-    The results of this study demonstrate that a manual review and mapping of quality attributes to issues is an effective approach for evaluating the quality of digital twins in the design phase.  
-    Therefore, systematic analysis of the identified issues in terms of their relevance to various quality attributes is an effective way to gain insight into the strengths and weaknesses of the digital twin system under development.
-    These insights can be used to guide further design decisions and improvements, ultimately leading to a higher-quality end product.
+    This paper aimed to evaluate the quality issues with the given digital twin system in the FELICE project while enhancing the 
+    scientific understanding of the quality of digital twins. As a result, this study demonstrates the idea of doing a manual review and mapping 
+    quality attributes to issues as a suitable approach for evaluating the quality of digital twins in the design phase. Furthermore, 
+    the study suggests that this evaluation is an effective way to collect information about the strengths and weaknesses of the digital twin system.
+    Although the findings should be interpreted with caution, collected information can be used to improve the upcoming design decisions, consequently to higher-quality digital twin systems.
 
-    The quality assessment of the digital twin encountered limitations due to the exility of information about the real system. Some artifacts provided less information, 
-    such as process videos, which only provide a limited perspective of the shop floor based on the camera's field of view and the skills of the video maker. 
-    In contrast, the simulation and conceptual model offer a plethora of aspects to examine and assess, which results in a higher probability of discovering the issues~\ref{fig:QualityInspectonResultsWithArtifacts}.
+    However, manual reviews are a time-consuming endeavor, and even with a reasonable investment of resources, it is not feasible that all relevant data will be covered. 
+    Additionally, the completeness of manual reviews is questionable due to the inherent limitations of the process. 
+    Moreover, the reliance on human judgment in manual reviews presents an additional challenge, as it is subject to individual interpretation and bias.  
+    For example, during the walkthrough, the author's assessment of the system could be flawed due to limited information about the designed digital twin system, resulting in false 
+    issue identification and mapping. Additionally, those explaining the system to the authors may be biased, 
+    whether due to political or economic reasons or lacking explanation ability.
+As a result, the data gathered from the walkthroughs is highly subjective and lacks objectivity.
+Lastly, this issue not only shows the severity of the data but also raises concerns about
+    the overall quality of the review process.
 
-    Person dependent, also not everything is written, memory problem, completeness, 
-    issuee finding sometimes even though the issue is not there, still assesed as a issue, assuming that person is correct
+    Taken together, the quality assessment of the digital twin encountered limitations due to the exility of information about the real system. 
+    Some artifacts provided less information, such as process videos, which gave a limited perspective of the shop floor based on the camera's 
+    field of view and the skills of the video maker. In contrast, the simulation and conceptual model offer a plethora of aspects to examine and assess, 
+    which results in a higher probability of discovering the issues (Figure~\ref{fig:QualityInspectonResultsWithArtifacts}). 
+    A possible explanation for this is the stage that the FELICE project is in. Not only the exility but also the visibility of the information is the limiting factor. 
+    Therefore, evolvability, completeness, and correctness were easier to map and detect, rather than fidelity and efficiency.
 
-    The write a protocol, timing ,hard to cover everything,
+    It would be interesting to map the risks of the issues instead of the issues to the quality attributes. 
+    The risk mapping approach includes severity and priority variables, which would include the perspective of the stakeholders~\cite{CemKanerSoftwareTesting, ISO/IEC/IEEE29119}.
+    As a result, quality attributes can be weighted regarding the stakeholder needs.  This aspect might be important because of relativity, 
+    more specifically the political and economical nature of the quality~\cite{SystemQuality}.
 

### 2023-03-20 manuscripts/paper-1/main.tex
Achknowledgement + Email remaning

@@
     4600 Wels, Upper Austria, Austria\\
+    %%TODO EMAIL
     \email{lncs@springer.com}}
@@
     The notion of the digital twin, which has gained popularity in 
-    recent years, is often subject to vague and ambiguous envisions\cite{Review1}.
+    recent years, is often subject to vague and ambiguous envisions~\cite{Review1}.
     The mispresenting of this notion began with the physical twin of the Apollo 13 spacecraft. 
     The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilized in physical simulations. 
-    Even though the digital aspect was expected to be present, there wasn't\cite{GrievesApollo13}.
+    Even though the digital aspect was expected to be present, there wasn't~\cite{GrievesApollo13}.
     Another physical twin is the historic D-day map (also known as the Big Board) in Southwick House England, 
@@
     implemented to give directives from the real system to control the operation 
-    flow and to update the physical twin state\cite{AMRC}.
+    flow and to update the physical twin state~\cite{AMRC}.
     In contrast, a digital twin is a virtual counterpart of a real system, which should 
-    be synchronized with a selected frequency and fidelity\cite{Review1,Review2,digitaltwinconsortium2022}.
+    be synchronized with a selected frequency and fidelity~\cite{Review1,Review2,digitaltwinconsortium2022}.
 
@@
     time and material. Initially, this model had four main parts. The real system, 
-    virtual system, connection between the real and virtual system and virtual simulations\cite{GrievesPLMBook}. 
-    Later, Grieves removed the latter, to simplify the model\cite{Originsofdigitaltwinconcept}. Lastly, after co-authoring with Vicker in 2010, 
-    Grieves decided to use the NASA-invented "Digital Twin" word, instead of the information mirroring model\cite{Originsofdigitaltwinconcept}.
+    virtual system, connection between the real and virtual system and virtual simulations~\cite{GrievesPLMBook}. 
+    Later, Grieves removed the latter, to simplify the model~\cite{Originsofdigitaltwinconcept}. Lastly, after co-authoring with Vicker in 2010, 
+    Grieves decided to use the NASA-invented `Digital Twin' word, instead of the information mirroring model~\cite{Originsofdigitaltwinconcept}.
 
     In recent years, there is evidence that digital twins play a crucial role in the manufacturing industries, 
-    life sciences, healthcare, infrastructure and smart cities\cite{Review2}.
+    life sciences, healthcare, infrastructure and smart cities~\cite{Review2}.
     For example, a digital wind farm from General Electric is a good illustration of how building a digital twin helped to design a better turbine, 
@@
 
-    The previous studies predominantly focused on the design and implementation of digital twins\cite{Review1, Review2}. 
+    The previous studies predominantly focused on the design and implementation of digital twins~\cite{Review1, Review2}. 
     However, a crucial aspect that remains unclear is how to achieve quality in these highly intricate and evolvable systems. 
@@
 
-    This paper aims not only to review the digital twin artifacts utilized in the FELICE project and evaluate the quality issues associated with them~\cite{FELICE}. 
-    also, targets to enhance the scientific understanding of the quality of digital twins. The artifacts analyzed in this study include process videos showing the current assembly procedure, 
+    This paper aims not only to review the digital twin artifacts utilized in the FELICE project and evaluate the quality issues associated with them~\cite{FELICE},  
+    but also, targets to enhance the scientific understanding of the quality of digital twins. The artifacts analyzed in this study include process videos showing the current assembly procedure, 
     a scope definition, a requirements specification, a general and operational conceptual model, and a discrete event simulation module. 
@@
     \section{State of the art on quality}
-    The Oxford English Dictionary defines the word "quality" as a noun or an adjective form. The adjective form indicates, 
-    a high standard of excellence as in  "quality products" \cite{OxfordDictionary}. Even though the noun form is defined in multiple ways, the most impactful 
-    definition refers to a  standard of an entity that is measured relative to other entities, whether different or similar \cite{OxfordDictionary}.  
+    The Oxford English Dictionary defines the word `quality' as a noun or an adjective form. The adjective form indicates, 
+    a high standard of excellence as in  `quality products`~\cite{OxfordDictionary}. Even though the noun form is defined in multiple ways, the most impactful 
+    definition refers to a  standard of an entity that is measured relative to other entities, whether different or similar~\cite{OxfordDictionary}.  
     Additionally, quality is the degree to which a set of inherent properties of an entity fulfills the given requirements~\cite{ISO9000}.
@@
     A product is a tangible or intangible system that satisfies the needs or wants of a customer.
-    A product can be a physical system like a car, or an abstract system, like a digital twin. Furthermore, product quality is comprised of two aspects~\cite{GrievesPLMBook}.  
+A product can be a physical system like a car, or an abstract system, like a digital twin.
+Furthermore,
+    product quality is comprised of two aspects~\cite{GrievesPLMBook}.  
     Firstly, quality is an attribute of a product, which refers to the degree to which a product meets its specifications.
@@
     As an example, ISO/IEC:25010 has standardized eight attributes, 
-    including functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability, and portability, to measure software quality.
+    including functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability, and portability, to measure software quality~\cite{ISO/IEC:25010}.
 
     \subsection{Simulation Quality}
-    The human brain simulates real systems abstractly either to predict the future state of the system or to gather information about the past state of the system 
-    \cite{MobusSystemTheory}.
-However, these days, many simulation processes are done by virtual systems.
-For example,  software programs such as ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} enable users
+    The human brain simulates real systems abstractly either to predict the future state of the system or to gather information about the past state of the system~\cite{MobusSystemTheory}.
+    However, these days, many simulation processes are done by virtual systems. For example, software programs such as ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} enable users 
     to build a simulation model to make predictions and get information about the past- as well as the current state of the system.
@@
     These techniques are broadly categorized into six areas: informal, static, dynamic, 
-    symbolic, constraint, and formal techniques \cite{balcicategories,balcitechniques}. Formal techniques involve mathematical formality, whereas informal techniques rely on 
-    human intervention and reasoning. Although mathematical techniques are more precise, informal techniques are more commonly used \cite{balcicategories}.
+    symbolic, constraint, and formal techniques~\cite{balcicategories,balcitechniques}. Formal techniques involve mathematical formality, whereas informal techniques rely on 
+    human intervention and reasoning. Although mathematical techniques are more precise, informal techniques are more commonly used~\cite{balcicategories}.
 
@@
 
-    He Zhang et al. introduced the updating method for digital twin models in yet another insightful article.
+    In yet another insightful article, He Zhang et al. introduced the updating method for digital twin models.
     Once more, the accuracy and coherence of the model concepts were addressed~\cite{ZHANGUPDATEMETHOD}.
 
-    Selch et al. presented a machine-learning approach based on Bayesian networks to track the quality of the digital twin. 
+    Furthermore, Selch et al. presented a machine-learning approach based on Bayesian networks to track the quality of the digital twin. 
     The unique aspect of this study is that the authors determined the contributions of subsystems to forecast the overall quality of the digital twin, 
@@
 
-    %%TODO
     \textbf{Discrete Event Simulation Model} consisted of seven sections, including two animation sections, two input sections, one output section, one process logic section, and a database section. 
@@
 
-    %%TODO
     \textbf{Completeness} is a derived word from the word  \textit{complete}, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
@@
     \begin{figure}[htbp]
+        \centering
         \includegraphics[width = 1\textwidth]{Evolvability.png}
@@
     To begin this process, the findings were collected from the manual review, followed by an inspection of the findings to determine which digital twin qualities were absent. 
-    Finally, the findings were mapped to the relevant missing quality attribute(s) and submitted for artifact quality evaluation (Figure~\ref{fig:RequirementSpecifications}).
+    Finally, the findings were mapped to the relevant missing quality attribute(s) and submitted for artifact quality evaluation (Figure~\ref{fig:Method}).
 
@@
     The process started by identifying which quality attribute(s) were mapped. 
-    Once identified, the missing attribute(s) was incremented by 1 to determine the total quality of missing attributes of the artifact(Figure~\ref{fig:RequirementSpecifications}).
+    Once identified, the missing attribute(s) was incremented by 1 to determine the total quality of missing attributes of the artifact(Figure~\ref{fig:Method}).
 
     \begin{figure}[htbp]
-        \includegraphics[scale = 0.30]{RequirementSpecifications.png}
-        \caption{Method for the evaluation of the digital twin artifact quality: Artifact. finding indicates that the finding belongs to the artifact, while -> indicates mapping}
-        \label{fig:Method}
+        \centering
+        \includegraphics[width = 0.8\textwidth]{RequirementSpecifications.png}
+        \caption{Method for the evaluation of the digital twin artifact quality: Artifact. finding indicates that the finding belongs to the artifact, while -> indicates mapping}\label{fig:Method}
     \end{figure}
@@
     Furthermore, the value of the sum was assigned to the related digital twin quality attribute. 
-    As a result, the digital twin quality was demonstrated with quality attribute values (Figure~\ref{fig:DigitalTwinQuality}).
+    As a result, the digital twin quality was demonstrated with quality attribute values (Figure~\ref{fig:MethodforDigitalTwinQuality}).
 
     \begin{figure}[htbp]
-        \includegraphics[scale = 0.25]{DigitalTwinQuality.png}
-            \caption{Method for the evaluation of the digital twin quality}
-        \label{fig:MethodforDigitalTwinQuality}
+        \centering
+        \includegraphics[width = 0.8\textwidth]{DigitalTwinQuality.png}
+            \caption{Method for the evaluation of the digital twin quality}\label{fig:MethodforDigitalTwinQuality}
     \end{figure}
@@
             Y-Axis represents the number of missing quality attributes found for each artifact, 
-            and lastly, each digital twin quality attribute is shown by the colors.}
-            \label{fig:QualityInspectonResultsWithArtifacts}
+            and lastly, each digital twin quality attribute is shown by the colors.}\label{fig:QualityInspectonResultsWithArtifacts}
     \end{figure}
@@
     \section*{Acknowledgements}
-    TODO
+    %TODO
 

### 2023-03-23 manuscripts/paper-1/main.tex
Bug is fixed, pictures are revised, bib is updated

@@
 \usepackage[T1]{fontenc}
-\usepackage{listings}
-\usepackage{float}
+\usepackage{bookmark}
 \usepackage{graphicx}
-\usepackage{amsfonts}
-\usepackage{verbatim}
-\usepackage{cite}
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{cleveref}
+\usepackage{dirtree,array}
 \usepackage{tabularray}
-\usepackage{dirtree,array}
-\usepackage{subcaption}
 
@@
 
-    \title{Quality assurance of digital twins -- An experience report in the automotive industry}
+    \title{Quality assurance of digital twins: An experience report in the automotive industry}
 
@@
     \section{Introduction}\label{section:introduction}
-
-    The notion of the digital twin, which has gained popularity in 
-    recent years, is often subject to vague and ambiguous envisions~\cite{Review1}.
+    The notion of the digital twin, which has gained popularity in recent years, is often subject to vague and ambiguous envisions~\cite{Review1}.
     The mispresenting of this notion began with the physical twin of the Apollo 13 spacecraft. 
     The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilized in physical simulations. 
-    Even though the digital aspect was expected to be present, there wasn't~\cite{GrievesApollo13}.
+    Even though the digital aspect was expected to be present, there wasn't~\cite{GrievesMichaelApolloMyth}.
     Another physical twin is the historic D-day map (also known as the Big Board) in Southwick House England, 
@@
     The envision of a digital twin emerged from Grieves'es conceptual model, which was called mirrored spaces model in 2002~\cite{Originsofdigitaltwinconcept},
-    and later referenced in a 2005 journal article~\cite{2005JournayArticle}. 
+    and later referenced in a 2005 journal article~\cite{2005ArticleGrievesMichael}. 
     Furthermore, he introduced the information mirroring model, which was his ideal product lifecycle management tool with only one goal. 
@@
 
-    In recent years, there is evidence that digital twins play a crucial role in the manufacturing industries, 
-    life sciences, healthcare, infrastructure and smart cities~\cite{Review2}.
+    In recent years, there is evidence that digital twins play a crucial role in the manufacturing industries, life sciences, healthcare, infrastructure and smart cities~\cite{Review2}.
     For example, a digital wind farm from General Electric is a good illustration of how building a digital twin helped to design a better turbine, 
@@
 
-    The previous studies predominantly focused on the design and implementation of digital twins~\cite{Review1, Review2}. 
+    The previous studies predominantly focused on the design and implementation of digital twins~\cite{Review1,Review2}. 
     However, a crucial aspect that remains unclear is how to achieve quality in these highly intricate and evolvable systems. 
@@
 
-    \section{State of the art on quality}
-    The Oxford English Dictionary defines the word `quality' as a noun or an adjective form. The adjective form indicates, 
-    a high standard of excellence as in  `quality products`~\cite{OxfordDictionary}. Even though the noun form is defined in multiple ways, the most impactful 
-    definition refers to a  standard of an entity that is measured relative to other entities, whether different or similar~\cite{OxfordDictionary}.  
-    Additionally, quality is the degree to which a set of inherent properties of an entity fulfills the given requirements~\cite{ISO9000}.
-    Both of these definitions clearly show the relative aspect of quality, and the following subcategories are the specialization of these definitions.
-    \subsection{Product quality}
-    A product is a tangible or intangible system that satisfies the needs or wants of a customer.
-A product can be a physical system like a car, or an abstract system, like a digital twin.
-Furthermore,
-    product quality is comprised of two aspects~\cite{GrievesPLMBook}.  
-    Firstly, quality is an attribute of a product, which refers to the degree to which a product meets its specifications.
-These product specifications are mostly defined by the supra-systems' subsystems, such as the stakeholders.
-    For this aspect, if the stakeholders' expectations or needs are met,  high quality is considered. The second aspect of product quality is the ability to execute to a specific usage standard.
-    Unlike the first aspect, standardization is not controllable. Therefore, the product's quality is determined by how well the implied or obligatory standards are met~\cite{GrievesPLMBook}.
+    \section{Related Work on Quality}
+    The notion of quality is defined in many forms in the literature. Some scholars defined quality as conformance to specifications and
+    requirements~\cite{ProductConformanceCostGilmore,LevittTheodoreProduction-LineApproach,QualityisFree}, while others saw it as a value~\cite{QualityandCompetitionanEssayinEconomicTheory} or the 
+    fitness for use~\cite{Juran1974}which evolved to fitness for purpose later~\cite{Juran2010},  
+    or an abstain of loss~\cite{GenichiTaguchi}, and meeting or exceeding customer expectations~\cite{Groenrossstrategicmanagementandmarketing}. 
+    Even the ISO9000 standard defines the quality differently, which is an inherent characteristic of the entity~\cite{ISO9000}. 
+    These definitions endeavors to provide an universal understanding of quality and assess it subsequently. However, 
+    they come with some strengths and weaknesses.
+For example, conforming to the requirements and specifications can be useful for assessing the quality of the system but may not always reflect the needs of the stakeholders,
+    hence the quality of the system depends on how accurately these requirements were set~\cite{IEE7302014}.
 
-    \subsection{Software quality}
-    Software is a combination of programs and data that can be utilized by both virtual and physical systems, 
-    such as computer systems\cite{OxfordDictionary}. Its quality is determined by how well it fulfills the requirements that were set. However, 
-    those requirements may not always reflect the needs of the stakeholders, hence the quality depends on how accurately these requirements were set~\cite{IEE730-2014}. 
-    As an example, ISO/IEC:25010 has standardized eight attributes, 
-    including functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability, and portability, to measure software quality~\cite{ISO/IEC:25010}.
+    The first serious discussions of subcategorization of quality trace back to the beginning of the 20th century with the emergence of product-focused quality management practices in manufacturing~\cite{HistoryofControlEngineering}.
+    Later on, with the development of new technologies, subcategorization of quality was evolved and extended to other areas, such as software, which appeared in the 1970s~\cite{ThePsychologyofComputerProgramming}.
+    With this emergence, assessing the software quality became inevitable and as a result, a considerable amount of software quality models and characteristics have been established~\cite{SoftwareQualityModels,Charecteristicsofsoftwarequality,AnActivityBasedQualityModelforMaintainability}.
+    As an example, ISO/IEC:25010 has standardized eight software quality characteristics, including functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability,
+    and portability, to determine software quality~\cite{ISO/IEC:25010}.
 
-    \subsection{Simulation Quality}
-    The human brain simulates real systems abstractly either to predict the future state of the system or to gather information about the past state of the system~\cite{MobusSystemTheory}.
-    However, these days, many simulation processes are done by virtual systems. For example, software programs such as ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} enable users 
-    to build a simulation model to make predictions and get information about the past- as well as the current state of the system.
-
-    Quality characteristics of these simulation models must be evaluated by the validation and verification techniques~\cite{StewartSimulation,VerificationValidationSergent,OsmanBalci}. 
+    It was not until the late 1950s that another important subcategory for the context of this paper `computer simulation quality' 
+    was considered~\cite{SomeProblemsofDigitalSystemsSimulation}.
+Surprisingly, R.
+W.
+Conway et al.identified several potential problems with computer simulation systems in this era, which are still relevant today.
+    To find and evaluate these problems, validation and verification techniques have emerged~\cite{StewartSimulation,VerificationValidationSergent,OsmanBalci}. 
     Validation is the process of evaluating the simulation quality in comparison to the real system from the perspective of its intended applications. 
-     On the other hand, verification is a procedure to evaluate the implementation of the simulation model and 
-    its associated data concerning the conceptual description and specifications of the model developer\cite{StewartSimulation,VerificationValidationSergent}. 
-    These techniques are broadly categorized into six areas: informal, static, dynamic, 
-    symbolic, constraint, and formal techniques~\cite{balcicategories,balcitechniques}. Formal techniques involve mathematical formality, whereas informal techniques rely on 
-    human intervention and reasoning. Although mathematical techniques are more precise, informal techniques are more commonly used~\cite{balcicategories}.
+    On the other hand, verification is a procedure to evaluate the implementation of the simulation model and its associated data concerning the conceptual description and specifications of 
+    the model developer~\cite{StewartSimulation,VerificationValidationSergent}. These techniques are broadly categorized into six areas: informal, static, dynamic, symbolic, constraint, 
+    and formal techniques~\cite{balcicategories,balcitechniques}. Formal techniques involve mathematical formality, 
+    whereas informal techniques rely on human intervention and reasoning. Although mathematical techniques are more precise, informal techniques are more commonly used~\cite{balcicategories}.
 
@@
 
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%METHODS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     \section{Method}
@@
     Therefore, manual reviews were deemed the most suitable tool to account for the characteristics of this situation.
-    The manual review included, audits, inspections, reviews, structural analysis and walkthroughs 
+    The manual review included audits, inspections, reviews, structural analysis and walkthroughs 
     with the project partners which was inspired by Balci's manual review works~\cite{balcitechniques}.
@@
     as well as the Oxford dictionary was consulted to 
-    synthesize our findings\cite{ISO9000,ISO90012015,ISO/IEC:25010,IEE730-2014, OxfordDictionary}.
+    synthesize our findings\cite{ISO9000,ISO90012015,ISO/IEC:25010,IEE7302014,OxfordDictionary}.
 
@@
 
-    \textbf{Completeness} is a derived word from the word  \textit{complete}, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 1\textwidth]{CorrectnessandCompleteness.png}
+        \caption{Incorrect (a) and incomplete (b) status has been demonstrated with a simplified finite state machine. Incorrectness can be observed in the behavior 
+        of the machine after 2 state transitions. Incompleteness, on the other hand, can be observed in the missing state. It should be noted that, even though the second state machine is missing a 
+        component, it shows the right behavior, hence it is correct.}\label{fig:CorrectnessAndCompleteness}
+    \end{figure}
+
+    \textbf{Completeness} is a derived word from the word  \textit{complete}, which can be described as an adjective, attribute, or verb~\cite{OxfordDictionary}. 
     The adjectival form used in the study denotes \textit{complete} as a state of having all the necessary or appropriate parts according to the real system 
@@
     were inspected but identified as a completeness issue.
-
-    \begin{figure}
-
-        \centering
-            \includegraphics[width = 1\textwidth]{Correctness and Completeness.png}
-            \caption{Incorrect  (a) and incomplete (b) status has been demonstrated with a 
-            simplified finite state machine. Incorrectness can be observed in the behavior 
-            of the machine after 2 state transitions. Incompleteness, on the other hand, can be observed in 
-            the missing state. It should be noted that, even though the second state machine is missing a 
-            component, it shows the right behavior, hence it is correct. }\label{fig:CorrectnessAndCompleteness}
-    \end{figure}
 
@@
     For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired (Figure~\ref{fig:EfficiencyandFidelity}).
-
     \begin{figure}[htbp]
@@
     \end{figure}
-
     \textbf{Evolvability} is a system's capability to enhance its suitability to its environment through alterations to both its internal and functional 
@@
     within the system (Figure~\ref{fig:Evolvability}). 
-
     \begin{figure}[htbp]
@@
     \end{figure}
-
     \subsection{Mapping Digital Twin Attributes to Manual Review Results}
@@
     Finally, the findings were mapped to the relevant missing quality attribute(s) and submitted for artifact quality evaluation (Figure~\ref{fig:Method}).
-
     \subsection{Artifact Quality Evaluation}
@@
     Once identified, the missing attribute(s) was incremented by 1 to determine the total quality of missing attributes of the artifact(Figure~\ref{fig:Method}).
-
     \begin{figure}[htbp]
@@
         \includegraphics[width = 0.8\textwidth]{RequirementSpecifications.png}
-        \caption{Method for the evaluation of the digital twin artifact quality: Artifact. finding indicates that the finding belongs to the artifact, while -> indicates mapping}\label{fig:Method}
+        \caption{Method for the evaluation of the digital twin artifact quality: `Artifact.finding' indicates that the finding belongs to the artifact, while `->' indicates mapping}\label{fig:Method}
     \end{figure}
-
     \subsection{Digital Twin Quality Evaluation}
@@
     As a result, the digital twin quality was demonstrated with quality attribute values (Figure~\ref{fig:MethodforDigitalTwinQuality}).
-
     \begin{figure}[htbp]
@@
     \end{figure}
-
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%RESULTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     \section{Results}
-
-    First, to assess digital twin quality,
-    manual reviews for each artifact were conducted (Figure~\ref{fig:QualityInspectonResultsWithArtifacts} ). 
-    As a result, a total of twenty-one quality issues were identified,
-    listed, and finally mapped to the digital twin quality attributes(Table~\ref{tab:Table1})(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
-    The mapping process 
-    revealed that a total of thirty-eight digital twin quality attributes were 
-    lacking in the artifacts(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).  
-    Specifically, 23\% of the quality issues of the digital twin were related to correctness, 
-    which indicates an error between the real- and digital twin system. Furthermore, 36\%  were related 
+    First, to assess digital twin quality, manual reviews for each artifact were conducted (Figure~\ref{fig:QualityInspectonResultsWithArtifacts}). 
+    As a result, a total of twenty-one quality issues were identified, listed, and finally mapped to the digital twin quality attributes (Table~\ref{tab:Table1}) (Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
+    The mapping process revealed that a total of thirty-eight digital twin quality attributes were lacking in the artifacts (Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).  
+    Specifically, 23\% of the quality issues of the digital twin were related to correctness, which indicates an error between the real- and digital twin system. Furthermore, 36\%  were related 
     to completeness, proving that some necessary or appropriate parts were missing.
@@
     to the environment and was not flexible or scalable.
-
     \subsection{Example Findings}  
@@
     the results of the manual review as well as the mapping to the digital twin quality attributes. 
-
     \subsubsection{Conceptual Model-Finding 12:}
-
     The duration of the micro-operations in the conceptual model was calculated using a simple calculation 
@@
     simplified calculations for the micro-operation durations,
-    suggests that the digital twin conceptual model suffers from issues of correctness and completeness(Table~\ref{tab:Table1}) .
-
+    suggests that the digital twin conceptual model suffers from issues of correctness and completeness (Table~\ref{tab:Table1}). 
     \subsubsection{Simulation Model-Finding 18:}
@@
         Thus, the exclusion of parallel executions indicates that the simulation model was incomplete,
-        at the same time, using the wrong type of execution highlights its inaccuracies(Table~\ref{tab:Table1}) .
-
+        at the same time, using the wrong type of execution highlights its inaccuracies (Table~\ref{tab:Table1}).
     \begin{figure}[htbp]
@@
             \includegraphics[scale = 0.35]{quality_inspection_results_with_artifacts.png}
-            \caption{Quality Inspection Results Categorized with Artifacts: X-Axis represents artifacts in section~\ref{section:Artifacts}, 
+            \caption{Quality Inspection Results Categorized with Artifacts: X-Axis represents artifacts in section \ref{section:Artifacts}, 
             Y-Axis represents the number of missing quality attributes found for each artifact, 
@@
     \end{figure}
-
     \begin{table}[h!]
@@
         manual reviews: Cases where an attribute is mapped, were marked by `X'.}\label{tab:Table1}
-    \scalebox{0.80}{
+        \scalebox{0.75}{
             \begin{tabular}{llllll}
@@
     \end{table}
-
     \section{Discussion}
-
     This paper aimed to evaluate the quality issues with the given digital twin system in the FELICE project while enhancing the 
@@
     It would be interesting to map the risks of the issues instead of the issues to the quality attributes. 
-    The risk mapping approach includes severity and priority variables, which would include the perspective of the stakeholders~\cite{CemKanerSoftwareTesting, ISO/IEC/IEEE29119}.
-    As a result, quality attributes can be weighted regarding the stakeholder needs.  This aspect might be important because of relativity, 
-    more specifically the political and economical nature of the quality~\cite{SystemQuality}.
-
+    The risk mapping approach includes severity and priority variables, which would include the perspective of the stakeholders~\cite{CemKanerSoftwareTesting,ISO/IEC/IEEE29119}.
+    As a result, quality attributes can be weighted regarding the stakeholder needs. This aspect might be important, because of relativity, 
+    more specifically due to the political and economical nature of the quality~\cite{SystemQuality}. 
     \section*{Acknowledgements}
-    %TODO
 

### 2023-03-24 manuscripts/paper-1/main.tex
Redesigned the pictures to fit 15

@@
     \subsection{Artifacts}\label{section:Artifacts}
-    The current stage of review encompasses five key artifacts, including process videos displaying the current assembly procedure without an adaptive workstation and cobot, a scope definition outlining the objects on the shop floor requiring tracking or twinning, a requirements specification summarizing functional and non-functional requirements for the digital twin, a general and an operational conceptual model elucidating the high-level structure of the assembly procedure,
+    The current stage of review encompasses five key artifacts, including process videos displaying the current assembly procedure without an adaptive workstation and cobot,
+     a scope definition outlining the objects on the shop floor requiring tracking or twinning, a requirements 
+     specification summarizing functional and non-functional requirements for the digital twin, a general and an operational 
+     conceptual model elucidating the high-level structure of the assembly procedure, 
     and a discrete event simulation module that implements the structures prescribed by the conceptual models.
@@
         \includegraphics[width = 1\textwidth]{Efficiency and Fidelity.png}
-        \caption{Fidelity (a) and efficiency (b) levels have been demonstrated with simplified CAD drawings and 
-        finite state machines.}~\label{fig:EfficiencyandFidelity}
+        \caption{Fidelity and efficiency levels have been demonstrated with simplified CAD drawings.}~\label{fig:EfficiencyandFidelity}
     \end{figure}
+
     \textbf{Evolvability} is a system's capability to enhance its suitability to its environment through alterations to both its internal and functional 
@@
         \centering
-        \includegraphics[width = 1\textwidth]{Evolvability.png}
-        \caption{Evolvability has been demonstrated with simplified finite state machines. 
-        Evolving the machines on the left side, needed effort 
-        and the evolved finite state machines on the right side can be observed.}~\label{fig:Evolvability}
+        \includegraphics[width = 0.9\textwidth]{Evolvability.png}
+        \caption{Figure represents the demonstration of evolvability with the comparison between the first state machine(represented in black), and the evolved state machine(represented in green).
+The required effort
+        to evolve from the black state machine to the green state machine could be evaluated as \textit{Evolvability}.}~\label{fig:Evolvability}
     \end{figure}

### 2023-04-06 manuscripts/paper-2/main.tex
Init Commit

\documentclass[conference]{IEEEtran}
\usepackage[colorlinks,allcolors=blue]{hyperref}
\usepackage{amsfonts}
\usepackage{graphicx}

\begin{document}

    \title{Construction of Proto Digital Twin with ROS2 and Omniverse}
    \author{\IEEEauthorblockN{Georg Hackenberg} 
    \IEEEauthorblockA{School of Electrical and\\ Computer Engineering\\ Georgia Institute of Technology\\ Atlanta, Georgia 30332--0250\\ Email: mshell@ece.gatech.edu} 
    \and 
    \IEEEauthorblockN{Alican Tüzün\\ and Montgomery Scott} 
    \IEEEauthorblockA{Starfleet Academy\\ San Francisco, California 96678-2391\\ Telephone: (800) 555--1212\\ Fax: (888) 555--1212}}

    \maketitle

    \begin{abstract}
        Digital twins are becoming more and more important for the efficient and effective development and operation of cyber-physical systems.
        However, digital twins are only useful if they reflect the real-world system accurately enough, i.e. their quality is high enough. 
        This claim entails the question, of what the term quality in the context of digital twins means and how it can be measured. 
        In this article, we present our experience with the quality assurance of a digital twin for an assembly line in the automotive industry.
        We explain our preliminary definition of digital twin quality, which we derive from classical quality models for general software systems. 
        Furthermore, we describe quality issues, which we were able to detect in a digital twin of an assembly line in the automotive industry. \
        Finally, we conclude how to leverage our experience in different contexts and how to generalize the underlying approaches.
    \end{abstract}

    \section{Introduction}\label{section:introduction}
    In recent years, as new and complex technologies have advanced to emerge, it becomes progressively 
    difficult to understand and define their core concepts. One of the most significant current examples in the 
    area of digitalization is the concept of digital twins, which has resulted in numerous definitions, that vary 
    from one derivation to another. Because, even though the terms `digital' and `twin' are easy to grasp,  their 
    consolidation develops a new challenging concept, which can be resulted in misunderstanding and misapplication. For example, 
    some authors claim that the first utilization of the digital twins 
    happened in Apollo 13 space mission in 1970.  
    Even though there was a `twin'  to simulate the spacecraft in space, which fulfills the first part of the concept of 
    `digital twin', the digital component was missing. Therefore this claim is not accurate.

    \section{Components}\label{section:components}
    There are several components to inspect..

    \subsection{ROS2}\label{section:ros2}
    \subsection{Omniverse}\label{section:Omniverse}
    \subsection{Raspberry Pi \& Ubuntu 20.04}\label{section:RaspberryPi}
    \subsection{Fusion 360 and Blender}\label{section:Fusion360}
    \section{Method}\label{section:method}
    What we are studying, and what we are going to do with the object.
    \section{Implementation}\label{section:implementation}
    How we are going to analyze the object.
    \section{Results}\label{section:results}
    Problems with data collection
    Show digital twin
    \section{Discussion}\label{section:discussion}
    Last sentence of the introduction, should be the first sentence of the discussion.
    How did your actual results compare with what you expected?
    Unexpected results
    Bring everything together, possible applications, extensions for further improvements
    \bibliography{main}
    \bibliographystyle{plain}

\end{document}

### 2023-04-06 manuscripts/paper-2/main.tex
Second Introduction paragraph

@@
     \author{\IEEEauthorblockN{Georg Hackenberg} 
-    \IEEEauthorblockA{School of Electrical and\\ Computer Engineering\\ Georgia Institute of Technology\\ Atlanta, Georgia 30332--0250\\ Email: mshell@ece.gatech.edu} 
+    \IEEEauthorblockA{School of Electrical and\\ Computer Engineering\\ Georgia Institute of Technology\\ Atlanta,
+    Georgia 30332--0250\\ Email: mshell@ece.gatech.edu} 
     \and 
     \IEEEauthorblockN{Alican Tüzün\\ and Montgomery Scott} 
-    \IEEEauthorblockA{Starfleet Academy\\ San Francisco, California 96678-2391\\ Telephone: (800) 555--1212\\ Fax: (888) 555--1212}}
+    \IEEEauthorblockA{Starfleet Academy\\ San Francisco, California 966782391\\ Telephone: (800) 555--1212\\ Fax: (888) 555--1212}}
 
@@
         Digital twins are becoming more and more important for the efficient and effective development and operation of cyber-physical systems.
-        However, digital twins are only useful if they reflect the real-world system accurately enough, i.e. their quality is high enough. 
+        However, digital twins are only useful if they reflect the real-world system accurately enough, i.e.their quality is high enough. 
         This claim entails the question, of what the term quality in the context of digital twins means and how it can be measured. 
@@
     In recent years, as new and complex technologies have advanced to emerge, it becomes progressively 
-    difficult to understand and define their core concepts. One of the most significant current examples in the 
+    difficult to understand and define their core concepts. One of the significant current examples in the 
     area of digitalization is the concept of digital twins, which has resulted in numerous definitions, that vary 
@@
     some authors claim that the first utilization of the digital twins 
-    happened in Apollo 13 space mission in 1970.  
-    Even though there was a `twin'  to simulate the spacecraft in space, which fulfills the first part of the concept of 
+    happened in Apollo 13 space mission in 1970. Even though there was a `twin'  to simulate the spacecraft in space, which fulfills the first part of the concept of 
     `digital twin', the digital component was missing. Therefore this claim is not accurate.
 
+    The idea of the digital twin originated in 2002 by the Grieves, as an ideal form of product life cycle management. 
+    The proposal was to create a co-existed information twin of a real system to gather new information to minimize 
+    the system needs and waste, such as material, time, and energy. It should be noted that initially this concept was 
+    called the information mirroring model. The concept had all the components of today's digital twins: a real system, 
+    a virtual system,  a connection between them and ancillary the virtual simulation. However, after co-authoring with Vickers in 2010, 
+    the term `digital twin' was adopted and Grieves simplified the model by excluding the virtual simulation aspect.
+
     \section{Components}\label{section:components}
-    There are several components to inspect..
+    There are several components to inspect
 
@@
     \section{Discussion}\label{section:discussion}
-    Last sentence of the introduction, should be the first sentence of the discussion.
+    The last sentence of the introduction should be the first sentence of the discussion.
     How did your actual results compare with what you expected?

### 2023-04-08 manuscripts/paper-2/main.tex
Introduction is done

@@
     \section{Introduction}\label{section:introduction}
-    In recent years, as new and complex technologies have advanced to emerge, it becomes progressively 
-    difficult to understand and define their core concepts. One of the significant current examples in the 
+    As new and complex technologies have advanced to emerge, it becomes progressively 
+    difficult to understand and define their core concepts. One significant example in the 
     area of digitalization is the concept of digital twins, which has resulted in numerous definitions, that vary 
@@
     some authors claim that the first utilization of the digital twins 
-    happened in Apollo 13 space mission in 1970. Even though there was a `twin'  to simulate the spacecraft in space, which fulfills the first part of the concept of 
-    `digital twin', the digital component was missing. Therefore this claim is not accurate.
+    happened in Apollo 13 space mission in 1970. Even though there was a `twin' used to simulate the spacecraft in space, fulfilling the first part of the concept of 
+    `digital twin', the digital component was missing, making this claim inaccurate.
 
@@
     the system needs and waste, such as material, time, and energy. It should be noted that initially this concept was 
-    called the information mirroring model. The concept had all the components of today's digital twins: a real system, 
-    a virtual system,  a connection between them and ancillary the virtual simulation. However, after co-authoring with Vickers in 2010, 
+    called the information mirroring model and included all the components of today's digital twins: a real system, 
+    a virtual system, a connection between them and an ancillary, the virtual simulation. However, after co-authoring with Vickers in 2010, 
     the term `digital twin' was adopted and Grieves simplified the model by excluding the virtual simulation aspect.
+
+    A considerable amount of literature has been published on Digital Twins, however, to date there has been little agreement on the precise definition and application.
+Numerous authors have considered different
+    definitions, including digital twins as a multi-physics environment, an equivalent to a product, a digital copy, a cyber component of a Cyber-Physical System, a controlling and monitoring unit,
+    and many more. However, if inspected carefully, most of these definitions focus more on the quality factors or applications of digital twins rather than their notion.
+    Therefore, despite the subjective phenomena of the definition of digital twins, the definition by the Digital Twin Consortium was considered to be more suitable for the authors. 
+    Consortium's definition describes digital twins as virtual representations of real systems with a synchronization attribute,
+    presenting a more abstract and objective perspective.
+
+    Not only in the literature but digital twins also gained popularity 
+    nearly in all branches of industry, especially in the manufacturing scene.  
+    This resulted in the development of general platforms to construct digital twins. Furthermore, for the visualization of the digital twins, 
+    game engines such as Unity and  Unreal Engine have become popular tools, and some of them already offer dedicated digital 
+    twin platforms. 
+    For databases, there are ontology-based cloud solutions even with newly defined languages for 
+    managing the data associated with digital twins. While there are some accessible open-source projects, 
+    most of the digital twin platforms today are not free to use and may not be easy to access or grasp.
+
+    Therefore, the main purpose of this paper is not only to demonstrate a proto-digital twin but also to give an introductory 
+    understanding of digital twins, including the difference between a digital twin, digital shadow and digital model. The real system consists of three LED lamps (red, green, blue),
+    one ultrasonic sensor, one Raspberry Pi, five 330 ohm resistors, and several jumper cables.
+    The goal is to digitalize nearly all the components of the real system and properly twin one of them. To achieve twinning, 
+    authors used Omniverse as a simulation and visualization tool, and ROS2(Robot Operating System) as a sensor and communication middleware.
 

### 2023-04-08 manuscripts/paper-2/main.tex
Updated method intro

@@
 
-    Not only in the literature but digital twins also gained popularity 
-    nearly in all branches of industry, especially in the manufacturing scene.  
+    Not only in the literature but digital twins also gained popularity nearly in all branches of industry, especially in the manufacturing scene.  
     This resulted in the development of general platforms to construct digital twins. Furthermore, for the visualization of the digital twins, 
@@
     authors used Omniverse as a simulation and visualization tool, and ROS2(Robot Operating System) as a sensor and communication middleware. 
+    \section{Method}\label{section:components}
+    There are several components to inspect
+    To demonstrate the concept of a proto-digital twin, several steps were taken. 
+    First, the real system was created and digitalized. Next, a digital model representing the digitalized form of 
+    a real system was developed. Then a digital shadow was created to accomplish an automatic unidirectional data transfer from the real system to the virtual system. 
+    And finally, a digital twin, which has a bidirectional data flow between the real and the virtual system was created.
 
-    \section{Components}\label{section:components}
-    There are several components to inspect
-
-    \subsection{ROS2}\label{section:ros2}
-    \subsection{Omniverse}\label{section:Omniverse}
-    \subsection{Raspberry Pi \& Ubuntu 20.04}\label{section:RaspberryPi}
-    \subsection{Fusion 360 and Blender}\label{section:Fusion360}
-    \section{Method}\label{section:method}
-    What we are studying, and what we are going to do with the object.
-    \section{Implementation}\label{section:implementation}
-    How we are going to analyze the object.
+    \subsection{Creating a real system}\label{section:real_system}
+    \subsection{Digitalizing the real system}\label{section:digitalizing}
+    \subsection{Creating the digital shadow}\label{section:digital_shadow}
+    \subsection{Creating the digital twin}\label{section:digital_twin}
     \section{Results}\label{section:results}

### 2023-04-12 manuscripts/paper-2/main.tex
Method check

--- 2023-04-08 manuscripts/paper-2/main.tex
@@
     Consortium's definition describes digital twins as virtual representations of real systems with a synchronization attribute,
-    presenting a more abstract and objective perspective.
+    presenting a more abstract and objective perspective.\cite{asf}
 
-    Not only in the literature but digital twins also gained popularity 
-    nearly in all branches of industry, especially in the manufacturing scene.  
+    Not only in the literature but digital twins also gained popularity nearly in all branches of industry, especially in the manufacturing scene.  
     This resulted in the development of general platforms to construct digital twins. Furthermore, for the visualization of the digital twins, 
@@
     twin platforms.
+
     For databases, there are ontology-based cloud solutions even with newly defined languages for 
@@
     authors used Omniverse as a simulation and visualization tool, and ROS2(Robot Operating System) as a sensor and communication middleware. 
+    \section{Method}\label{section:components}
+    To demonstrate the notion of a proto digital twin, several procedures were executed.
+    Initially, a digital model representing the digitalized form of the real system was developed.
+    Subsequently, relative to the  digitalized model, real system was established.
+    Then a digital shadow was generated to accomplish an automatic unidirectional data transfer 
+    from the real to the virtual system. And finally a digital twin, with  
+    bidirectional data flow between the real and the virtual system were created.
 
-    \section{Components}\label{section:components}
-    There are several components to inspect
+    \subsection*{Digital Model}\label{section:digital_model}
+    To create a digital model of the planned real system, Fusion 360, a  
+    Computer-Aided-Design(CAD) software was used. First, 
+    pre-existing digitalized real system components were sourced from the internet,
+    and modified. The ones that were not found, such as jumper cables, were modeled in the CAD software. 
+    Once all the required components were avaliable and reached a needed  model fidelity level,
+    detailing were stoped and parts were digitaly assembled. 
+    Lastly, the assembled digital model was saved as .fbx file.
 
-    \subsection{ROS2}\label{section:ros2}
-    \subsection{Omniverse}\label{section:Omniverse}
-    \subsection{Raspberry Pi \& Ubuntu 20.04}\label{section:RaspberryPi}
-    \subsection{Fusion 360 and Blender}\label{section:Fusion360}
-    \section{Method}\label{section:method}
-    What we are studying, and what we are going to do with the object.
-    \section{Implementation}\label{section:implementation}
-    How we are going to analyze the object.
+    After the conversion occured, 3D-Graphics software called Blender was used, to convert 
+    a .fbx file to .usd file for import  into the simulation environment. 
+    However, before the conversion, adjustments were made to the .fbx file to fix issues, 
+    such as corrupted visuals and hiearchy problems. Later, the fixed file were saved as a .usd file.
+
+    Lastly, Blender was reopened, and the converted .usd file was imported. 
+    Further  adjustments were made, and the file was saved  again as a .usd file. 
+    Upon completion of this process, the file was ready to import into the simulation environment.
+    \subsection*{Real System}\label{section:real_system}
+    First, components were inserted on the prototype breadboard according to the digital model.
+    Next, circuit components were connected with the jumper cables to the appropriate general 
+    purpose input/output (GPIO), ground and power pins of Raspberry Pi 4 (RPI4).
+
+    Next, Ubuntu 20.04 was installed on a micro-SD card,  and inserted into the RPI4.
+    Second  the cryptographic network protocol SSH, was used to connect the RPI to a local computer 
+    which already had the same version of the ubuntu. Next the Robot Operating System 2 (ROS2) 
+    version Foxy was installed on both the RPI and the local computer. 
+    Lastly, to access and control the GPIO pins of the RPI4, the Wiring Pi library was installed on RPI4.
+
+    ROS2 was used as a sensor and communication middleware to give 
+    behavior to the real system components. A package was written
+    to read a data from the ultrasonic sensor and control the state of three LEDs 
+    and then combined into a single node with a single-thread executor. 
+    Lastly, combined ros node was run, and the state space of the real system was observed and 
+    checked if the three led's were giving the expected state.
+
+    \subsection*{Digital Shadow}\label{section:digital_shadow}
+
+    The simulation platform chosen for this demonstration was Isaac Sim, 
+    which is already integrated within NVIDIA Omniverse platform. 
+    Isaac Sim was designed for training and testing complex robotic systems within realistic virtual environments. 
+    Even though this demonstration was not a complex robotic system, there were two important 
+    reasons for the platform selection. First Isaac Sim has a ROS2 bridge, which enabled seemless 
+    connection between the ROS2 and Omniverse, second, it uses RTX Graphics, which delivered 
+    high-performance graphics rendering, resulted in improvement of visual fidelity. 
+    However, to use Omniverse platform, an RTX graphics card is required. 
+    Therefore,  in this demonstration, the authors used an NVIDIA RTX 2060 graphics card, to 
+    facilitate the simulation.
+
+    First to initialize the simulation, 
+    Isaac Sim was installed on a local computer using Omniverse launcher. 
+    After the installation was complete, the correct ROS2 bridge, was selected.
+    At this step, it was important to not source the ROS2 Workspace within the same terminal, 
+    which Isaac Sim was operating. If automatic sourcing via bashrc was enabled, 
+    it needed to be disabled to prevent potential compilation errors.
+
+    After the initialization, the modified .usd file was imported into the Isaac Sim scene. 
+    After the import, a visual inspection for the individual parts was then conducted, and 
+    needed adjustments were made. Lastly,  the required level of fidelity of the digital model, 
+    within the simulation environment was reached, and the consutrction was ready to proceed to the next step.
+
+    To use the ROS2 bridge within the Isaac Sim, action graphs were utilized. 
+    Isaac Sim already had several built-in ROS2 nodes, and authors instead of writing their own ROS2 nodes, 
+    used the built-in ones just for the simplification of the demonstration. 
+    With the help of these built-in nodes, a visual script has been written, and Isaac Sim subscriebed
+    and published the topics that corresponds 1:1 with  the written ROS2 package for the real system.
+
+    Finally, the ROS2 package and simulation environment were initialized 
+    and the behavior of the three LEDs was observed to ensure that their state was 
+    synchronous and unidirectional between the real and virtual systems.
+
+    \subsection*{Digital Twin}\label{section:digital_twin}
+    The key difference between the digital shadow and digital twin lies within their mode of communication, 
+    which the latter is bidirectional instead of the unidirectional behavior like the first one.
+    To achieve this bidirectional behavior, action graph was expended and gave a new 
+    behavior to the real system: a blue LED  controlled by a counter embedded in the simulation environment.
+
+    In order to see the effect of the bidirectional behavior, ROS2 node and simulation environment 
+    were initialized again, and the behaviour of the three LEDs were monitored to ensure that their state was 
+    synchronous and bidirectional.
+
     \section{Results}\label{section:results}

### 2023-05-15 manuscripts/paper-2/main.tex
Update Introduction

--- 2023-04-08 manuscripts/paper-2/main.tex
@@
 
-    \title{Construction of Proto Digital Twin with ROS2 and Omniverse}
+    \title{Modeling and Observing ProtoDigital Twin with ROS2 and Omniverse}
     \author{\IEEEauthorblockN{Georg Hackenberg} 
@@
     from one derivation to another. Because, even though the terms `digital' and `twin' are easy to grasp,  their 
-    consolidation develops a new challenging concept, which can be resulted in misunderstanding and misapplication. For example, 
-    some authors claim that the first utilization of the digital twins 
-    happened in Apollo 13 space mission in 1970. Even though there was a `twin' used to simulate the spacecraft in space, fulfilling the first part of the concept of 
-    `digital twin', the digital component was missing, making this claim inaccurate.
+    consolidation develops a new challenging concept, which can be resulted in misunderstanding and misapplication. 
+    Therefore, a proto example of digital twin, can significantly improve the understanding 
+    of the notion of digital twin, and can help to clear the fuzzy boundaries between similar concepts such as digital shadow and digital model.
 
@@
 Numerous authors have considered different
-    definitions, including digital twins as a multi-physics environment, an equivalent to a product, a digital copy, a cyber component of a Cyber-Physical System, a controlling and monitoring unit,
-    and many more. However, if inspected carefully, most of these definitions focus more on the quality factors or applications of digital twins rather than their notion.
-    Therefore, despite the subjective phenomena of the definition of digital twins, the definition by the Digital Twin Consortium was considered to be more suitable for the authors. 
-    Consortium's definition describes digital twins as virtual representations of real systems with a synchronization attribute,
-    presenting a more abstract and objective perspective.
+    definitions, including digital twins as a multi-physics environment, an equivalent to a product,
+    a digital copy, a cyber component of a Cyber-Physical System, a controlling and monitoring unit,
+    and many more. However, if inspected carefully, most of these definitions focus more on the quality 
+    factors or applications of digital twins rather than their notion.
+    Therefore, despite the subjective phenomena of the definition of digital twins,
+    the definition by the Digital Twin Consortium was considered to be more suitable for the authors. 
+    Consortium's definition describes digital twins as virtual representations of real systems with 
+    a synchronization attribute, presenting a more abstract and objective perspective.\cite{asf}
 
-    Not only in the literature but digital twins also gained popularity 
-    nearly in all branches of industry, especially in the manufacturing scene.  
-    This resulted in the development of general platforms to construct digital twins. Furthermore, for the visualization of the digital twins, 
-    game engines such as Unity and  Unreal Engine have become popular tools, and some of them already offer dedicated digital 
-    twin platforms. 
-    For databases, there are ontology-based cloud solutions even with newly defined languages for 
-    managing the data associated with digital twins. While there are some accessible open-source projects, 
+    Not only in the literature but digital twins also gained popularity nearly in all branches
+    of industry, especially in the manufacturing scene.  
+    This resulted in the development of general platforms to construct digital twins. 
+    Furthermore, for the visualization of the digital twins, 
+    game engines such as Unity and  Unreal Engine have become popular tools, 
+    and some of them already offer dedicated digital twin platforms. Also for databases,
+    there are ontology-based cloud solutions even with newly defined languages for 
+    managing the data associated with digital twins.However,While there are some accessible open-source projects, 
     most of the digital twin platforms today are not free to use and may not be easy to access or grasp.
 
-    Therefore, the main purpose of this paper is not only to demonstrate a proto-digital twin but also to give an introductory 
-    understanding of digital twins, including the difference between a digital twin, digital shadow and digital model. The real system consists of three LED lamps (red, green, blue),
-    one ultrasonic sensor, one Raspberry Pi, five 330 ohm resistors, and several jumper cables.
-    The goal is to digitalize nearly all the components of the real system and properly twin one of them. To achieve twinning, 
-    authors used Omniverse as a simulation and visualization tool, and ROS2(Robot Operating System) as a sensor and communication middleware.
+    To adresss the challanges associated with the accessability and comprehensibility of the notion of digital twins, main purpose of this paper is not only to provide a fully functional free-to-model proto digital twin, but also give observation results, including the challanges and solutions encountered during the creation of a digital model, digital shadow and digital twin.
+Goal of the process of modelling a digital twin is to digitalize nearly all the components of the real system and properly twin one of them.
+    To make the twinning happen, authors used Omniverse as a simulation and visualization tool, 
+    and ROS2(Robot Operating System)  as a sensor and communication middleware. 
+    To control the behavior of digitalized artifacts, an HC-SR04 ultrasonic sensor, Raspberry Pi,
+    and several software has been used. Also, despite the subjective phenomena of the definition 
+    of digital twins, the definition by the Digital Twin Consortium were considered
+    to be more suitable for the authors. Consortiums definition describes digital
+    twins  as virtual representations of real systems with a synchronization attribute,
+    presenting a more abstract and objective perspective which will be a guide for the 
+    creation of the proto digital twin.
 
-    \section{Components}\label{section:components}
-    There are several components to inspect
+    \section{Modeling the Proto Digital Twin}\label{section:components}
+    Several procedures were executed to demonstrate the notion of a proto-digital twin. 
+    Initially, a digital model representing the digitalized form of the real system was developed. 
+    Subsequently, relative to the digitalized model, a real system was established. 
+    Then a digital shadow was generated to accomplish an automatic unidirectional data 
+    transfer from the real to the virtual system. And finally, a digital twin, with 
+    bidirectional data flow between the real and the virtual system was created.
 
-    \subsection{ROS2}\label{section:ros2}
-    \subsection{Omniverse}\label{section:Omniverse}
-    \subsection{Raspberry Pi \& Ubuntu 20.04}\label{section:RaspberryPi}
-    \subsection{Fusion 360 and Blender}\label{section:Fusion360}
-    \section{Method}\label{section:method}
-    What we are studying, and what we are going to do with the object.
-    \section{Implementation}\label{section:implementation}
-    How we are going to analyze the object.
-    \section{Results}\label{section:results}
-    Problems with data collection
-    Show digital twin
+    \subsection*{The Digital Model}\label{section:digital_model}
+    To create a digital model of the planned real system, two different software programs were used for two different 
+    purposes including Fusion 360, a Computer-Aided Design software, and Blender, a 3D-Graphics software.
+
+    First, pre-existing digitalized real system components were sourced from the internet, and modified.
+     The ones that were not found, such as jumper cables, were modeled in the Fusion 360. 
+     Once all the required components were available and reached a needed model fidelity level, 
+     detailing was stopped and parts were digitally assembled. Lastly, the assembled digital model 
+     was converted to a .fbx file.
+
+    After the conversion occurred, the Blender was used, to convert a .fbx file to a .usd 
+    file for import into the simulation environment. However, before the conversion, adjustments 
+    were made to the .fbx file to fix issues, such as corrupted visuals and hierarchy problems. 
+    Later, the fixed file was saved as a .usd file.
+
+    Finally, Blender was reopened, and the previously converted .usd file was imported. 
+    Further adjustments were made to the file and were saved again as a .usd file.
+    Upon completion of this process, the file was prepared for importation into the simulation environment.
+
+    \subsection*{Integrating digital model to Omniverse}\label{section:omniverse}
+    The chosen simulation platform for this demonstration was Isaac Sim, which is fully integrated into the NVIDIA Omniverse platform.
+Isaac Sim was designed specifically for the training and testing of complex robotic systems in realistic virtual environments.
+Despite the simplicity of the demonstration, which was not a complex robotic system, there were two crucial reasons for the platform selection.
+First, Isaac Sim offers a ROS2 bridge, which enabled a seamless connection between ROS2 and Omniverse, facilitating relatively easy and smooth data exchange.
+Second, it leverages RTX Graphics, which delivered high-performance graphics rendering, resulting in an improvement in visual fidelity.
+However, to use the Omniverse platform, an RTX graphics card is required.
+Therefore, for this demonstration, the authors used an NVIDIA RTX 2060 graphics card, to run the simulation.
+
+    First, to initialize the simulation, Isaac Sim was installed on a local computer using the Omniverse launcher.
+Once the installation was completed, the correct ROS2 bridge was selected.
+At this step, it was important not to source the ROS2 Workspace within the same terminal that Isaac Sim was operating, for example with bashrc, to prevent potential compilation errors.
+
+    After the initialization, the modified .usd file was imported into the Isaac Sim scene.
+After the import, a visual inspection of the individual parts was then conducted, and needed adjustments were made.
+Lastly,  the required level of fidelity of the digital model, within the simulation environment was reached, and the step of the construction of the real system was ready.
+    \subsection*{Real System}\label{section:real_system}
+    First, the components were inserted on the prototype breadboard in accordance with the digital model.
+    Next, circuit components were connected with the jumper cables to the appropriate general-purpose input/output (GPIO),
+    ground, and power pins of Raspberry Pi 4 (RPI4).
+
+    Afterward, Ubuntu 20.04 was installed on a micro-SD card, 
+    and inserted into the RPI4. Second, the cryptographic network protocol SSH was used to connect the 
+    RPI4 to a local computer that already had the same version of Ubuntu. Subsequently, 
+    the Robot Operating System 2 (ROS2) version of Foxy was installed on both the RPI 4 and 
+    the local computer. Lastly, to access and control the GPIO pins of the RPI4, 
+    the Wiring Pi library was installed on RPI4.
+
+    ROS2 was used as a sensor and communication middleware to give behavior to the real system components.
+    A custom package was developed to read data from the ultrasonic sensor and control the state of three LEDs. 
+    This behavior were integrated into a single node, which was executed with a single-thread executor.
+    Lastly, a combined ROS2 node was run, and the state space of the real system was observed to ensure
+    that the three LEDs were giving the expected state.
+
+    \subsection*{Digital Shadow}\label{section:digital_shadow}
+
+    %WRITE LEAD HERE
+
+    To use the ROS2 bridge within the Isaac Sim, action graphs were utilized. 
+    Isaac Sim already had several built-in ROS2 nodes, and authors instead of writing their own ROS2 nodes, 
+    used the built-in ones just for the simplification of the demonstration. 
+    With the help of these built-in nodes, a visual script has been written, and Isaac Sim subscriebed
+    and published the topics that corresponds 1:1 with  the written ROS2 package for the real system.
+
+    Finally, the ROS2 package and simulation environment were initialized 
+    and the behavior of the three LEDs was observed to ensure that their state was 
+    synchronous and unidirectional between the real and virtual systems.
+
+    \subsection*{Digital Twin}\label{section:digital_twin}
+    The key difference between the digital shadow and digital twin lies within their mode of communication, 
+    which the latter is bidirectional instead of the unidirectional behavior like the first one.
+    To achieve this bidirectional behavior, action graph was expended and gave a new 
+    behavior to the real system: a blue LED  controlled by a counter embedded in the simulation environment.
+
+    In order to see the effect of the bidirectional behavior, ROS2 node and simulation environment 
+    were initialized again, and the behaviour of the three LEDs were monitored to ensure that their state was 
+    synchronous and bidirectional.
+
+    \section{Observations}\label{section:results}
+    The modeling process of the digital twin with ROS2 and Omniverse showed that modeling the digital twin was relatively easy to construct, 
+    debug, and free to model while catching a high degree of visual fidelity. 
+    \subsection*{Observations while Creating Digital Model}
+    The digital model was created, with several steps,
+    which resulted in great quality, which was later used for the digital shadow and digital twin.
+    However, during this process, several difficulties occurred and were solved.
+
+    First, the authors did not consider the CAD environment as a digital environment, 
+    instead considered Omniverse as a digital environment. 
+    Therefore, in this application, conversion of CAD files to 
+    .obj or .fbx and later to .usd was inevitable. The results of the conversions 
+    show that a significant amount of model data gets lost, corrupted, or duplicated 
+    during the file conversions because of the complexity of the models. 
+    Therefore to minimize the data loss, reducing the number of parts
+    by grouping parts together as one solid part and removing the unnecessary 
+    details, modifying the names of the parts to simple ones, and deleting material
+    properties were helpful. However, some of these processes are irreversible, 
+    hence they might reduce the fidelity of the model drastically.
+
+    Further observations show that, during the process of the modeling, non-conventional ways,
+    such as modeling electric cables as 3D in CAD increased the overall fidelity of the digital model,
+    as well as the digital twin significantly.
+
+    Lastly, there was a significant difference in data loss, between the quality of file converters, 
+    Blender and Embedded Omniverse Converter, when the conversion of the .fbx file to a .usd file was wanted. 
+    Hence, before putting the .fbx file directly into the omniverse, putting it into the blender and modifying
+    there,  gives a better conversion of .fbx to .usd as well as gives more flexibility to manipulate the
+    corrupted data which occurs during the conversion to .fbx file from .step file.
+
+    \subsection*{Observations while creating a Real System}
+    With the help of the digital model, real system assembly time was reduced 
+    significantly as well as overall process safety increased.
+
+    First, the assembly time of the real system according to the digital model, 
+    dramatically decreased, due to the provided spatial and visual data from the digital model,
+    especially the cabling between the RPI and the breadboard.
+
+    Also the safety of components, during the assembly, also increased, which prevented
+    common mistakes such as giving higher voltage to 
+    GPIO pins, which could result in damaging the RPI, was prevented.
+
+    \subsection*{Observations of manual connection between the real and virtual system}
+    \subsection*{Observations while Creating a Digital Shadow}
+    \subsection*{Observations of automatic unidirectional connection between the real and virtual system}
+    \subsection*{Observations while Creating a Digital Twin}
+    \subsection*{Observations of automatic bidirectional connection between the real and virtual system}
     \section{Discussion}\label{section:discussion}

### 2023-05-15 manuscripts/paper-1/main.tex
Added email address to author list

@@
 
-    \author{Georg Hackenberg\inst{1}
+    \author{Alican Tüzün
     \and
-    Alican Tüzün\inst{1}
+    Georg Hackenberg
     }
@@
     4600 Wels, Upper Austria, Austria\\
-    %%TODO EMAIL
-    \email{lncs@springer.com}}
+    \email{alican.tuzuen@fh-wels.at}
+    \email{georg.hackenberg@fh-wels.at}
+    }
 
@@
         Digital twins are becoming more and more important for the efficient and effective development and operation of cyber-physical systems.
-        However, digital twins are only useful if they reflect the real-world system accurately enough, i.e.\ their quality is high enough.
-        This claim entails the question, of what the term quality in the context of digital twins means and how it can be measured.
-        In this article, we present our experience with the quality assurance of a digital twin for an assembly line in the automotive industry.
-        We explain our preliminary definition of digital twin quality, which we derive from classical quality models for general software systems.
-        Furthermore, we describe quality issues, which we were able to detect in a digital twin of an assembly line in the automotive industry.
-        Finally, we conclude how to leverage our experience in different contexts and how to generalize the underlying approaches.
+        However, digital twins are only useful if they reflect the real-world system accurately enough,
+        i.e.\ their quality is high enough.
+        This claim entails the question, of what the term quality in the context of digital twins means and
+        how it can be measured. In this article, authors presented their experience with the quality assurance of a digital
+        twin for an assembly line in the automotive industry.
+        Authors explained the preliminary definition of digital twin quality, 
+        which authors derived from classical quality models for general software systems.
+        Furthermore, authors described quality issues, 
+        which they were able to detect in a digital twin of an assembly line in the automotive industry.
+        Finally, authors concluded how to leverage their experience in different contexts 
+        and how to generalize the underlying approaches.
     \end{abstract}
@@
     flow and to update the physical twin state~\cite{AMRC}.
-    In contrast, a digital twin is a virtual counterpart of a real system, which should 
+    In contrast, a digital twin is virtual information of a possible or constructed real system, which can 
     be synchronized with a selected frequency and fidelity~\cite{Review1,Review2,digitaltwinconsortium2022}.
@@
     and later referenced in a 2005 journal article~\cite{2005ArticleGrievesMichael}. 
-    Furthermore, he introduced the information mirroring model, which was his ideal product lifecycle management tool with only one goal. 
-    The goal was to gather enhanced information about the real system to minimize the waste of the system's sources such as energy, 
-    time and material. Initially, this model had four main parts. The real system, 
-    virtual system, connection between the real and virtual system and virtual simulations~\cite{GrievesPLMBook}. 
+    Furthermore, he introduced the information mirroring model, which was his ideal form of product lifecycle management
+    at that time with only one goal. The goal was to gather as much relevant and useful information about the real system and leverage that information to trade the required energy, time, 
+    and material sources for the system operations.
+    Initially, this model had four main parts. The real system, virtual system, connection between the real and virtual system and virtual simulations~\cite{GrievesPLMBook}. 
     Later, Grieves removed the latter, to simplify the model~\cite{Originsofdigitaltwinconcept}. Lastly, after co-authoring with Vicker in 2010, 
@@
     \section{Method}
-    The methodology consists of a set of artifacts, manual artifact reviews, mapping quality attributes to the findings, an evaluation of the artifact quality, and lastly, an evaluation of the digital twin quality.
+    The form of FELICE's digital twin was the digital twin instance, which implies that the real system was already constructed.
+It is important to note that, for the sake of convenience, the authors used the term "Digital Twin" in the subsequent chapters instead of  "digital twin instance" in the subsequent chapters.
+
+    Moreover, since the digital twin was still in the design phase, 
+    the methodology of assessing its quality consists of several key steps,
+    including a set of artifacts, manual reviews of these artifacts, 
+    mapping quality attributes to the identified findings, an evaluation of the artifact quality, and ultimately, 
+    an evaluation of the digital twin's overall quality.
     \subsection{Artifacts}\label{section:Artifacts}
-    The current stage of review encompasses five key artifacts, including process videos displaying the current assembly procedure without an adaptive workstation and cobot,
+    The current stage of review encompassed five key artifacts,
+    including process videos displaying the current assembly procedure without an adaptive workstation and cobot,
     a scope definition outlining the objects on the shop floor requiring tracking or twinning, a requirements 
@@
     which results in a higher probability of discovering the issues (Figure~\ref{fig:QualityInspectonResultsWithArtifacts}). 
-    A possible explanation for this is the stage that the FELICE project is in. Not only the exility but also the visibility of the information is the limiting factor. 
+    A possible explanation for this is the stage that the FELICE project is in. Also, not only the exility but also the visibility of the information is the limiting factor. 
     Therefore, evolvability, completeness, and correctness were easier to map and detect, rather than fidelity and efficiency.
@@
     more specifically due to the political and economical nature of the quality~\cite{SystemQuality}.
-    \section*{Acknowledgements}
 

### 2023-05-16 manuscripts/paper-1/Without_Names.tex
Revision

--- 2023-05-15 manuscripts/paper-1/main.tex
@@
 
-    \author{Alican Tüzün
-    \and
-    Georg Hackenberg
-    }
-    \institute{School of Engineering\\
-    University of Applied Sciences Upper Austria\\
-    4600 Wels, Upper Austria, Austria\\
-    \email{alican.tuzuen@fh-wels.at}
-    \email{georg.hackenberg@fh-wels.at}
-    }
-
     \maketitle
@@
     \begin{abstract}
-        Digital twins are becoming more and more important for the efficient and effective development and operation of cyber-physical systems.
+        Digital twins are becoming increasingly important for the efficient and effective development 
+        and operation of cyber-physical systems.
         However, digital twins are only useful if they reflect the real-world system accurately enough,
@@
         This claim entails the question, of what the term quality in the context of digital twins means and
-        how it can be measured. In this article, authors presented their experience with the quality assurance of a digital
+        how it can be measured. In this article, the authors presented their experience with the quality assurance of a digital
         twin for an assembly line in the automotive industry.
@@
     \section{Method}
-    The form of FELICE's digital twin was the digital twin instance, which implies that the real system was already constructed.
+    The form of FELICE's digital twin was the digital twin instance\cite{GrievesVickers2017}, 
+    which implies that the real system was already constructed.
 It is important to note that, for the sake of convenience, the authors used the term "Digital Twin" in the subsequent chapters instead of  "digital twin instance" in the subsequent chapters.
@@
                     .3 ~~~~~X.
-                    .3 ~~~~~X.
+                    .3 ~~~~~0.
                     .3 ~~~~~0.
@@
                     .3 ~~~~~X.
-                    .3 ~~~~~0.
+                    .3 ~~~~~X.
                     .3 ~~~~~X.
@@
 
+    \newpage
     \bibliography{main}

### 2023-05-16 manuscripts/paper-2/main.tex
Revision

--- 2023-04-12 manuscripts/paper-2/main.tex
@@
     from one derivation to another. Because, even though the terms `digital' and `twin' are easy to grasp,  their 
-    consolidation develops a new challenging concept, which can be resulted in misunderstanding and misapplication. For example, 
+    consolidation emerge a new challenging concept, which can be resulted in misunderstanding and misapplication. For example, 
     some authors claim that the first utilization of the digital twins 

### 2023-07-04 manuscripts/paper-1/Without_Names.tex
Reworked

@@
     \title{Quality assurance of digital twins: An experience report in the automotive industry}
+
+    \author{Alican Tüzün
+    \and
+    Georg Hackenberg
+    }
+    \institute{School of Engineering\\
+    University of Applied Sciences Upper Austria\\
+    4600 Wels, Upper Austria, Austria\\
+    \email{alican.tuzuen@fh-wels.at}
+    \email{georg.hackenberg@fh-wels.at}
+    }
 
@@
     Even though the digital aspect was expected to be present, there wasn't~\cite{GrievesMichaelApolloMyth}.
-    Another physical twin is the historic D-day map (also known as the Big Board) in Southwick House England, 
+    Another physical twin is the historic D-Day map (also known as the Big Board) in Southwick House England, 
     which was used simultaneously before and during the operation, and can be argued to be similar. 
@@
     which implies that the real system was already constructed. 
-It is important to note that, for the sake of convenience, the authors used the term "Digital Twin" in the subsequent chapters instead of  "digital twin instance" in the subsequent chapters.
+    It is important to note that, for the sake of convenience, 
+    the authors utilized the term `Digital Twin' in the subsequent chapters instead of `digital twin instance'.
 
@@
     the methodology of assessing its quality consists of several key steps,
-    including a set of artifacts, manual reviews of these artifacts, 
+    including identification of the artifacts, manual reviews of these artifacts, 
     mapping quality attributes to the identified findings, an evaluation of the artifact quality, and ultimately, 
@@
     that indicates an error between the real system and a digital twin system (Figure~\ref{fig:CorrectnessAndCompleteness}).
-    Meanwhile, the quality of being \textit{correct} is described by the term accuracy~\cite{OxfordDictionary}.
+    Meanwhile, the quality of being \textit{correct} is measured by the metric accuracy~\cite{OxfordDictionary}.
 
@@
     \subsection{Example Findings}  
-    Two examples(Finding 12, Finding 18) are given to the reader to illustrate 
+    Two examples (Finding 12, Finding 18) are given to the reader to illustrate 
     the results of the manual review as well as the mapping to the digital twin quality attributes. 
@@
 
-    \newpage
+    \section*{Acknowledgement}
+    The authors express their sincere gratitude to the FELICE project under GAID (101017151) and its dedicated members 
+    for their invaluable feedback and strong patience throughout the evaluation of the digital twin's quality.
     \bibliography{main}

### 2023-07-04 manuscripts/paper-1/Without_Names.tex
1.review corrected

@@
         \centering
-        \includegraphics[width = 1\textwidth]{Efficiency and Fidelity.png}
-        \caption{Fidelity and efficiency levels have been demonstrated with simplified CAD drawings.}~\label{fig:EfficiencyandFidelity}
+        \includegraphics[width = 0.9\textwidth]{Efficiency and Fidelity.png}
+        \caption{Fidelity and Efficiency levels have been demonstrated with simplified CAD drawings. For the assessment of 
+        Efficiency, quantitative metrics, rendering time, and model size have been utilized.}~\label{fig:EfficiencyandFidelity}
     \end{figure}

### 2023-07-04 manuscripts/paper-1/Without_Names.tex
Consistent

@@
 
-    \subsection{Digital twin quality}
+    \subsection{Digital Twin Quality}
     To analyze the state of the digital twin quality, a literature analysis was executed. 
@@
     First, to assess digital twin quality, manual reviews for each artifact were conducted (Figure~\ref{fig:QualityInspectonResultsWithArtifacts}). 
-    As a result, a total of twenty-one quality issues were identified, listed, and finally mapped to the digital twin quality attributes (Table~\ref{tab:Table1}) (Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
+    As a result, a total of twenty-one quality related issues were identified, listed, and finally mapped to the digital twin quality attributes (Table~\ref{tab:Table1}) (Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
     The mapping process revealed that a total of thirty-eight digital twin quality attributes were lacking in the artifacts (Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).  

### 2023-09-18 manuscripts/quatic-2023/main.tex
start working on second paper

--- 2023-05-15 manuscripts/paper-1/main.tex
@@
     Furthermore, he introduced the information mirroring model, which was his ideal form of product lifecycle management
-    at that time with only one goal. The goal was to gather as much relevant and useful information about the real system and leverage that information to trade the required energy, time, 
+    at that time with only one goal. The goal was to gather as much relevant and useful information about the 
+    real system and leverage that information to trade the required energy, time, 
     and material sources for the system operations.
-    Initially, this model had four main parts. The real system, virtual system, connection between the real and virtual system and virtual simulations~\cite{GrievesPLMBook}. 
-    Later, Grieves removed the latter, to simplify the model~\cite{Originsofdigitaltwinconcept}. Lastly, after co-authoring with Vicker in 2010, 
-    Grieves decided to use the NASA-invented `Digital Twin' word, instead of the information mirroring model~\cite{Originsofdigitaltwinconcept}.
+    Initially, this model had four main parts. The real system, virtual system, 
+    connection between the real and virtual system and virtual simulations~\cite{GrievesPLMBook}. 
+    Later, Grieves removed the latter, to simplify the model~\cite{Originsofdigitaltwinconcept}. 
+    Lastly, after co-authoring with Vicker in 2010, 
+    Grieves decided to use the NASA-invented `Digital Twin' word, instead of the 
+    information mirroring model~\cite{Originsofdigitaltwinconcept}.
 
-    In recent years, there is evidence that digital twins play a crucial role in the manufacturing industries, life sciences, healthcare, infrastructure and smart cities~\cite{Review2}.
-    For example, a digital wind farm from General Electric is a good illustration of how building a digital twin helped to design a better turbine, 
-    which was used to collect and analyze the data from the real system for making the process of the real system more efficient~\cite{GeneralElectricWindTurbine}. 
-    Another fascinating example of the use of digital twins is Philips' virtual heart model. The twin of the heart evolves with the data generated by ultrasonic sensors to calculate 
-    how well the real heart is pumping the blood.
-This information can be used to predict a potential heart failure, allowing for early intervention and potentially life-saving treatment~\cite{PhilipsHearth}.
-    Lastly, FELICE is another interesting example of a digital twin application in manufacturing. In the project, twin models of machines/equipment and 
-    agents are utilized to support real-time decision-making and to conduct what-if analysis and experiments~\cite{FELICE}.
+    In recent years, there is evidence that digital twins play a crucial role 
+    in the manufacturing industries, life sciences, healthcare, infrastructure and smart cities~\cite{Review2}.
+    For example, a digital wind farm from General Electric is a good illustration of how building 
+    a digital twin helped to design a better turbine, 
+    which was used to collect and analyze the data from the real system for making the process of the 
+    real system more efficient~\cite{GeneralElectricWindTurbine}. 
+    Another fascinating example of the use of digital twins is Philips' virtual heart model. The 
+    twin of the heart evolves with the data generated by ultrasonic sensors to calculate 
+    how well the real heart is pumping the blood. This information can be used to predict a potential 
+    heart failure, allowing for early intervention and potentially life-saving treatment~\cite{PhilipsHearth}. 
+    Lastly, FELICE is another interesting example of a digital twin application in manufacturing. In 
+    the project, twin models of machines/equipment and agents are utilized to support real-time decision-making 
+    and to conduct what-if analysis and experiments~\cite{FELICE}.
 
-    The previous studies predominantly focused on the design and implementation of digital twins~\cite{Review1,Review2}. 
-    However, a crucial aspect that remains unclear is how to achieve quality in these highly intricate and evolvable systems. 
-    Therefore, ascertaining the requisite level of quality of a digital twin is an arduous undertaking that requires further research.
+    The previous studies predominantly focused on the design and 
+    implementation of digital twins~\cite{Review1,Review2}. 
+    However, a crucial aspect that remains unclear is how to achieve quality in these highly 
+    intricate and evolvable systems. 
+    Therefore, ascertaining the requisite level of quality of a digital twin is an arduous 
+    undertaking that requires further research.
 
-    This paper aims not only to review the digital twin artifacts utilized in the FELICE project and evaluate the quality issues associated with them~\cite{FELICE},  
-    but also, targets to enhance the scientific understanding of the quality of digital twins. The artifacts analyzed in this study include process videos showing the current assembly procedure, 
-    a scope definition, a requirements specification, a general and operational conceptual model, and a discrete event simulation module. 
-    To evaluate these artifacts, we considered five crucial quality attributes: correctness, completeness, fidelity, efficiency, and evolvability.
+    This paper aims not only to review the digital twin artifacts utilized in the FELICE
+    project and evaluate the quality issues associated with them~\cite{FELICE},  
+    but also, targets to enhance the scientific understanding of the quality of digital twins.
+    The artifacts analyzed in this study include process videos showing the current assembly procedure, 
+    a scope definition, a requirements specification, a general and operational conceptual model, 
+    and a discrete event simulation module. 
+    To evaluate these artifacts, we considered five crucial quality attributes: correctness, 
+    completeness, fidelity, efficiency, and evolvability.
 
     \section{Related Work on Quality}
-    The notion of quality is defined in many forms in the literature. Some scholars defined quality as conformance to specifications and
-    requirements~\cite{ProductConformanceCostGilmore,LevittTheodoreProduction-LineApproach,QualityisFree}, while others saw it as a value~\cite{QualityandCompetitionanEssayinEconomicTheory} or the 
+    The notion of quality is defined in many forms in the literature.
+    Some scholars defined quality as conformance to specifications and
+    requirements~\cite{ProductConformanceCostGilmore,LevittTheodoreProduction-LineApproach,QualityisFree},
+    while others saw it as a value~\cite{QualityandCompetitionanEssayinEconomicTheory} or the 
     fitness for use~\cite{Juran1974}which evolved to fitness for purpose later~\cite{Juran2010},  
     or an abstain of loss~\cite{GenichiTaguchi}, and meeting or exceeding customer expectations~\cite{Groenrossstrategicmanagementandmarketing}. 
-    Even the ISO9000 standard defines the quality differently, which is an inherent characteristic of the entity~\cite{ISO9000}. 
+    Even the ISO9000 standard defines the quality differently, which is an inherent characteristic 
+    of the entity~\cite{ISO9000}. 
     These definitions endeavors to provide an universal understanding of quality and assess it subsequently. However, 
     they come with some strengths and weaknesses.
-For example, conforming to the requirements and specifications can be useful for assessing the quality of the system but may not always reflect the needs of the stakeholders,
+    For example, conforming to the requirements and specifications can be useful for assessing the quality 
+    of the system but may not always reflect the needs of the stakeholders,
     hence the quality of the system depends on how accurately these requirements were set~\cite{IEE7302014}.
 
-    The first serious discussions of subcategorization of quality trace back to the beginning of the 20th century with the emergence of product-focused quality management practices in manufacturing~\cite{HistoryofControlEngineering}.
-    Later on, with the development of new technologies, subcategorization of quality was evolved and extended to other areas, such as software, which appeared in the 1970s~\cite{ThePsychologyofComputerProgramming}.
-    With this emergence, assessing the software quality became inevitable and as a result, a considerable amount of software quality models and characteristics have been established~\cite{SoftwareQualityModels,Charecteristicsofsoftwarequality,AnActivityBasedQualityModelforMaintainability}.
-    As an example, ISO/IEC:25010 has standardized eight software quality characteristics, including functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability,
+    The first serious discussions of subcategorization of quality trace back to the beginning of the 20th 
+    century with the emergence of product-focused quality management practices in manufacturing~\cite{HistoryofControlEngineering}.
+    Later on, with the development of new technologies, 
+    subcategorization of quality was evolved and extended to other areas, 
+    such as software, which appeared in the 1970s~\cite{ThePsychologyofComputerProgramming}.
+    With this emergence, assessing the software quality became inevitable 
+    and as a result, a considerable amount of software quality models and 
+    characteristics have been established~\cite{SoftwareQualityModels,Charecteristicsofsoftwarequality,
+    AnActivityBasedQualityModelforMaintainability}.
+    As an example, ISO/IEC:25010 has standardized eight software quality characteristics, 
+    including functional suitability, performance efficiency, compatibility, usability, 
+    reliability, security, maintainability, 
     and portability, to determine software quality~\cite{ISO/IEC:25010}.
@@
     was considered~\cite{SomeProblemsofDigitalSystemsSimulation}.
-Surprisingly, R.
-W.
-Conway et al.identified several potential problems with computer simulation systems in this era, which are still relevant today.
-    To find and evaluate these problems, validation and verification techniques have emerged~\cite{StewartSimulation,VerificationValidationSergent,OsmanBalci}. 
+    Surprisingly, R. W. Conway et al.identified several potential problems with computer 
+    simulation systems in this era, which are still relevant today.  
+    To find and evaluate these problems,
+    validation and verification techniques have emerged~\cite{StewartSimulation,VerificationValidationSergent,OsmanBalci}. 
     Validation is the process of evaluating the simulation quality in comparison to the real system from the perspective of its intended applications. 
     On the other hand, verification is a procedure to evaluate the implementation of the simulation model and its associated data concerning the conceptual description and specifications of 
-    the model developer~\cite{StewartSimulation,VerificationValidationSergent}. These techniques are broadly categorized into six areas: informal, static, dynamic, symbolic, constraint, 
+    the model developer~\cite{StewartSimulation,VerificationValidationSergent}.
+    These techniques are broadly categorized into six areas: informal, static, dynamic, symbolic, constraint, 
     and formal techniques~\cite{balcicategories,balcitechniques}. Formal techniques involve mathematical formality, 
-    whereas informal techniques rely on human intervention and reasoning. Although mathematical techniques are more precise, informal techniques are more commonly used~\cite{balcicategories}.
+    whereas informal techniques rely on human intervention and reasoning. 
+    Although mathematical techniques are more precise, informal techniques are more commonly used~\cite{balcicategories}.
 
@@
     To analyze the state of the digital twin quality, a literature analysis was executed. 
-    The analysis especially focused on how the digital twin quality is mentioned and assessed within the academic dissertations. Therefore, various tools, such as Scopus and Google Scholar were 
+    The analysis especially focused on how the digital twin quality is mentioned and assessed 
+    within the academic dissertations. Therefore, various tools, such as Scopus and Google Scholar were 
     used to perform an extensive literature analysis on digital twin publications.
@@
     150 dissertations linked to digital twin quality, verification and validation. 
-After a thorough review of these, only 17 were considered relevant for this paper, and as a result following findings were revealed.
+    After a thorough review of these, only 17 were considered relevant for this paper,
+    and as a result following findings were revealed.
 
-    First, He Zhang et al. developed a consistency evaluation approach for digital twin models, which can be used to assess their quality. 
-    The authors also discuss essential concepts, such as consistency between real and virtual systems and ultra-fidelity models~\cite{ZHANGEVALUATIONMETHOD}.
+    First, He Zhang et al. developed a consistency evaluation approach for digital 
+    twin models, which can be used to assess their quality. 
+    The authors also discuss essential concepts, such as consistency between real and 
+    virtual systems and ultra-fidelity models~\cite{ZHANGEVALUATIONMETHOD}.
 

### 2023-09-18 manuscripts/xxx-2024/main.tex
start working on second paper

\documentclass[conference]{IEEEtran}

\usepackage[colorlinks,allcolors=blue]{hyperref}
\usepackage{amsfonts}
\usepackage{graphicx}

\begin{document}

    \title{A formal theory of digital twins}

    \author{
        \IEEEauthorblockN{Georg Hackenberg} 
        \IEEEauthorblockA{School of Engineering\\University of Applied Sciences Upper Austria\\4600 Wels, Austria} 
        \and 
        \IEEEauthorblockN{Alican Tüzün} 
        \IEEEauthorblockA{Josef Ressel Center for Data-Driven Innovation in Business Modeling\\University of Applied Sciences Upper Austria\\4xxx Steyr, Austria}
    }

    \maketitle

    \begin{abstract}
        TODO
    \end{abstract}

    \section{Introduction}
    \label{section:introduction}
    TODO~\cite{asf}

    \subsection{Research objective}
    More systematic development of high-quality digital twins in different application domains.

    \subsection{Research question}
    Unambiguous definition of the term "digital twin"?

    \subsection{Research methodology}
    Literature review + formalization

    \section{Related work}
    TODO

    \section{A digital twin theory}
    \label{section:theory}
    TODO

    \subsection{Basic concepts}

    \subsubsection{Time}
    \[
        T
    \]

    \subsubsection{State}
    \[
        S    
    \]

    \subsubsection{Stream}
    \[
        \overrightarrow{S}: T \rightarrow S
    \]

    \subsection{Our model of the real world}

    \subsubsection{State set of the environment}
    \[
        S_{Env}    
    \]

    \subsubsection{State set of the product}
    \[
        S_{Pro}    
    \]

    \subsubsection{Behavior function of the environment}
    \[
        B_{Env}: \overrightarrow{S_{Pro}} \rightarrow \overrightarrow{S_{Env}}
    \]

    \subsubsection{Behavior function of the product}
    \[
        B_{Pro}: \overrightarrow{S_{Env}} \rightarrow \overrightarrow{S_{Pro}}
    \]

    \subsubsection{Actual behavior}
    tuple of product state stream and environment state stream
    \[
        (\overrightarrow{S_{Pro}}, \overrightarrow{S_{Env}})
    \]
    such that state streams are consistent, i.e.
    \[
        B_{Env}(\overrightarrow{S_{Pro}}) = \overrightarrow{S_{Env}}
    \]
    and
    \[
        B_{Pro}(\overrightarrow{S_{Env}}) = \overrightarrow{S_{Pro}}
    \]

    \subsection{Digital twin}
    TODO

    \section{Conclusion}
    \label{section:conclusion}
    TODO

    \bibliography{main}
    \bibliographystyle{plain}

\end{document}

### 2023-09-18 manuscripts/xxx-2024/main.tex
continue working on paper outline and content

@@
     \subsection{Research methodology}
-    Literature review + formalization
+    Literature review~\ref{section:related} + formalization~\ref{section:theory} + discussion~\ref{section:discussion}.
 
     \section{Related work}
+    \label{section:related}
     TODO
@@
     \label{section:theory}
-    TODO
+    In the following, we introduce a formal theory of digital twins.
+    We start with introducing core concepts in Section~\ref{section:theory-core}.
+    Then, on top of the core concepts we build a theory of the real world in Section~\ref{section:theory-world}.
+    Finally, on top of the theory of the real world we derive a theory of digital twins in Section~\ref{section:theory-twin}.
 
-    \subsection{Basic concepts}
+    \subsection{Core concepts}
+    \label{section:theory-core}
+    The core concepts include the notion of time, the notion of state, and the notion of stream.
 
     \subsubsection{Time}
+    In our theory we do not prescribe a specific model of time such as discrete or continuous.
+    We rather employ a generic approach, where different models of time can be plugged in easily.
+    In this generic approach, time is defined as some (not further specified) set
     \[
-        T
+        T.
     \]
@@
     \subsubsection{State}
+    Similar to the above case, we do not prescribe a specific model of state.
+    Again we employ a generic approach, where various models of state can be plugged in later.
+    In this generic approach state is defined as some (not further specified) set
     \[
-        S    
+        S.
     \]
@@
     \subsubsection{Stream}
+    Finally, we include a generic model of how state changes over time.
+    Analogous to the previous two cases, concrete models of time and state can be plugged in easily.
+    In our approach, a stream is a mapping from the time domain to the state domain, i.e.
     \[
-        \overrightarrow{S}: T \rightarrow S
+        \overrightarrow{S}: T \rightarrow S.
     \]
@@
     \subsection{Our model of the real world}
+    \label{section:theory-world}
+    Based on the concepts of time, state, and stream we build our model of the real world.
+    Our model of the real world distinguishes between a product and its environment.
+    For both the product and the environment we define the set of possible states as well as a behavior function.
+    Finally, we explain what an actual behavior of product and environment is.
 
-    \subsubsection{State set of the environment}
+    \subsubsection{Environment state}
     \[
@@
 
-    \subsubsection{State set of the product}
+    \subsubsection{Product state}
     \[
@@
 
-    \subsubsection{Behavior function of the environment}
+    \subsubsection{Environment behavior}
     \[
-        B_{Env}: \overrightarrow{S_{Pro}} \rightarrow \overrightarrow{S_{Env}}
+        B_{Env}: \overrightarrow{S_{Prod}} \rightarrow \overrightarrow{S_{Env}}
     \]
 
-    \subsubsection{Behavior function of the product}
+    \subsubsection{State behavior}
     \[
-        B_{Pro}: \overrightarrow{S_{Env}} \rightarrow \overrightarrow{S_{Pro}}
+        B_{Prod}: \overrightarrow{S_{Env}} \rightarrow \overrightarrow{S_{Prod}}
     \]
 
-    \subsubsection{Actual behavior}
+    \subsubsection{World behavior}
     tuple of product state stream and environment state stream
     \[
-        (\overrightarrow{S_{Pro}}, \overrightarrow{S_{Env}})
+        B_{World} = (\overrightarrow{S_{Prod}}, \overrightarrow{S_{Env}})
     \]
@@
     \[
-        B_{Env}(\overrightarrow{S_{Pro}}) = \overrightarrow{S_{Env}}
+        B_{Env}(\overrightarrow{S_{Prod}}) = \overrightarrow{S_{Env}}
     \]
@@
     \[
-        B_{Pro}(\overrightarrow{S_{Env}}) = \overrightarrow{S_{Pro}}
+        B_{Prod}(\overrightarrow{S_{Env}}) = \overrightarrow{S_{Prod}}
     \]
 
-    \subsection{Digital twin}
+    \subsection{Our model of digital twins}
+    \label{section:theory-twin}
+    TODO
+
+    \section{Discussion}
+    \label{section:discussion}
     TODO

### 2023-09-18 manuscripts/xxx-2024/main.tex
add figures

@@
     \label{section:theory-core}
-    The core concepts include the notion of time, the notion of state, and the notion of stream.
+
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics{./figures/theory-core.pdf}
+        \caption{Illustration of core concepts}
+        \label{figure:theory-core}
+    \end{figure}
+
+    The core concepts include the notion of time, the notion of state, and the notion of behavior.
 
@@
     \subsubsection{State}
-    Similar to the above case, we do not prescribe a specific model of state.
+    Similar to the above case, we do not prescribe a specific model of state such as subatomic, atomic, molecular, mechanical, electrical, digital, etc.
     Again we employ a generic approach, where various models of state can be plugged in later.
@@
 
-    \subsubsection{Stream}
+    \subsubsection{Behavior}
     Finally, we include a generic model of how state changes over time.
     Analogous to the previous two cases, concrete models of time and state can be plugged in easily.
-    In our approach, a stream is a mapping from the time domain to the state domain, i.e.
+    In our approach, a behavior is a mapping from the time domain to the state domain, i.e.
     \[
@@
     \label{section:theory-world}
-    Based on the concepts of time, state, and stream we build our model of the real world.
-    Our model of the real world distinguishes between a product and its environment.
-    For both the product and the environment we define the set of possible states as well as a behavior function.
-    Finally, we explain what an actual behavior of product and environment is.
+
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics{./figures/theory-world.pdf}
+        \caption{Illustration of real world concepts}
+        \label{figure:theory-world}
+    \end{figure}
+
+    Based on the concepts of time, state, and behavior we build our model of the real world.
+    This model distinguishes between a product and its environment.
+    For both the product and its environment we define their states and their functions.
+    Finally, we explain the concept of world behavior.
+
+    \subsubsection{Product state}
+    In our theory, the product state describes the product perfectly at a particular point in time.
+    We assume perfect knowledge in this representation and, hence, the representation is only a theoretical construct.
+    Mathematically, the product state is defined as set
+    \[
+        S_{Prod}.
+    \]
 
     \subsubsection{Environment state}
+    Similarly, the environment state describes the environment perfectly at a particular point in time.
+    Again we assume perfect knowledge in this purely theoretical representation.
+    Hence, the environment state is defined mathematically as set
     \[
-        S_{Env}    
+        S_{Env}.
     \]
 
-    \subsubsection{Product state}
+    \subsubsection{Product function}
+    Based on product and environment state we can define the product function.
+    The product function describes the logic of how the product reacts to the environment.
+    This logic can be described as mapping from environment behavior to product behavior, i.e.
     \[
-        S_{Pro}    
+        F_{Prod}: \overrightarrow{S_{Env}} \rightarrow \overrightarrow{S_{Prod}}
     \]
 
-    \subsubsection{Environment behavior}
+    \subsubsection{Environment function}
+    Similarly, we can define the environment function.
+    The environment function describes the logic of how the environment reacts to the product.
+    Hence, this logic can be described as mapping from product behavior to environment behavior, i.e.
     \[
-        B_{Env}: \overrightarrow{S_{Prod}} \rightarrow \overrightarrow{S_{Env}}
-    \]
-
-    \subsubsection{State behavior}
-    \[
-        B_{Prod}: \overrightarrow{S_{Env}} \rightarrow \overrightarrow{S_{Prod}}
+        F_{Env}: \overrightarrow{S_{Prod}} \rightarrow \overrightarrow{S_{Env}}
     \]
@@
     \subsubsection{World behavior}
-    tuple of product state stream and environment state stream
+    Finally, based on product state and function as well as environment state and function we introduce world behavior.
+    In our theory, world behavior is a combination of consistent product and environment behavior.
+    We express world behavior as tuple
     \[
@@
     \]
-    such that state streams are consistent, i.e.
+    such that the environment behavior $\overrightarrow{S_{Env}}$ is the result of product behavior $\overrightarrow{S_{Prod}}$, i.e.
     \[
-        B_{Env}(\overrightarrow{S_{Prod}}) = \overrightarrow{S_{Env}}
+        \overrightarrow{S_{Env}} = F_{Env}(\overrightarrow{S_{Prod}})
     \]
-    and
+    and, adversely, the product behavior $\overrightarrow{S_{Prod}}$ is the result of environment behavior $\overrightarrow{S_{Env}}$, i.e.
     \[
-        B_{Prod}(\overrightarrow{S_{Env}}) = \overrightarrow{S_{Prod}}
+        \overrightarrow{S_{Prod}} = F_{Prod}(\overrightarrow{S_{Env}}).
     \]

### 2023-10-24 manuscripts/xxx-2024/main.tex
work on outline

@@
 
+    \subsection{TODO}
+    TODO
+
+    \subsubsection{Observer}
+    TODO
+
+    \subsubsection{Observation}
+    TODO
+
+    \subsubsection{Event}
+    TODO time point and time span (observer dependent)
+
     \subsection{Our model of the real world}
@@
     Finally, we explain the concept of world behavior.
+
+    \subsubsection{World state}
+    TODO
+    \[
+        S_{World} = (S_{Prod}, S_{Env}).
+    \]
 
@@
 
-    \subsubsection{Product function}
-    Based on product and environment state we can define the product function.
-    The product function describes the logic of how the product reacts to the environment.
-    This logic can be described as mapping from environment behavior to product behavior, i.e.
+    \subsubsection{World behavior}
+    TODO
     \[
-        F_{Prod}: \overrightarrow{S_{Env}} \rightarrow \overrightarrow{S_{Prod}}
+        \overrightarrow{S_{World}} = (\overrightarrow{S_{Prod}}, \overrightarrow{S_{Env}})
     \]
 
-    \subsubsection{Environment function}
-    Similarly, we can define the environment function.
-    The environment function describes the logic of how the environment reacts to the product.
-    Hence, this logic can be described as mapping from product behavior to environment behavior, i.e.
-    \[
-        F_{Env}: \overrightarrow{S_{Prod}} \rightarrow \overrightarrow{S_{Env}}
-    \]
+    \subsection{TODO}
+    TODO
 
-    \subsubsection{World behavior}
-    Finally, based on product state and function as well as environment state and function we introduce world behavior.
-    In our theory, world behavior is a combination of consistent product and environment behavior.
-    We express world behavior as tuple
-    \[
-        B_{World} = (\overrightarrow{S_{Prod}}, \overrightarrow{S_{Env}})
-    \]
-    such that the environment behavior $\overrightarrow{S_{Env}}$ is the result of product behavior $\overrightarrow{S_{Prod}}$, i.e.
-    \[
-        \overrightarrow{S_{Env}} = F_{Env}(\overrightarrow{S_{Prod}})
-    \]
-    and, adversely, the product behavior $\overrightarrow{S_{Prod}}$ is the result of environment behavior $\overrightarrow{S_{Env}}$, i.e.
-    \[
-        \overrightarrow{S_{Prod}} = F_{Prod}(\overrightarrow{S_{Env}}).
-    \]
+    \subsubsection{Input}
+    TODO
+
+    \subsubsection{Output}
+    TODO
+
+    \subsubsection{Function}
+    TODO
+
+    %\subsubsection{Product function}
+    %Based on product and environment state we can define the product function.
+    %The product function describes the logic of how the product reacts to the environment.
+    %This logic can be described as mapping from environment behavior to product behavior, i.e.
+    %\[
+    %    F_{Prod}: \overrightarrow{S_{Env}} \rightarrow \overrightarrow{S_{Prod}}
+    %\]
+
+    %\subsubsection{Environment function}
+    %Similarly, we can define the environment function.
+    %The environment function describes the logic of how the environment reacts to the product.
+    %Hence, this logic can be described as mapping from product behavior to environment behavior, i.e.
+    %\[
+    %    F_{Env}: \overrightarrow{S_{Prod}} \rightarrow \overrightarrow{S_{Env}}
+    %\]
+
+    %\subsubsection{World behavior}
+    %Finally, based on product state and function as well as environment state and function we introduce world behavior.
+    %In our theory, world behavior is a combination of consistent product and environment behavior.
+    %We express world behavior as tuple
+    %\[
+    %    B_{World} = (\overrightarrow{S_{Prod}}, \overrightarrow{S_{Env}})
+    %\]
+    %such that the environment behavior $\overrightarrow{S_{Env}}$ is the result of product behavior $\overrightarrow{S_{Prod}}$, i.e.
+    %\[
+    %    \overrightarrow{S_{Env}} = F_{Env}(\overrightarrow{S_{Prod}})
+    %\]
+    %and, adversely, the product behavior $\overrightarrow{S_{Prod}}$ is the result of environment behavior $\overrightarrow{S_{Env}}$, i.e.
+    %\[
+    %    \overrightarrow{S_{Prod}} = F_{Prod}(\overrightarrow{S_{Env}}).
+    %\]
 

### 2023-10-31 manuscripts/xxx-2024/main.tex
continue working on real world model

@@
     We start with introducing core concepts in Section~\ref{section:theory-core}.
-    Then, on top of the core concepts we build a theory of the real world in Section~\ref{section:theory-world}.
+    Then, on top of the core concepts we build a theory of the real world in Section~\ref{section:theory-universe}.
     Finally, on top of the theory of the real world we derive a theory of digital twins in Section~\ref{section:theory-twin}.
 
-    \subsection{Core concepts}
+    \subsection{Time, state, and trace}
     \label{section:theory-core}
@@
         \includegraphics{./figures/theory-core.pdf}
-        \caption{Illustration of core concepts}
+        \caption{Illustration of time, state, and trace.}
         \label{figure:theory-core}
@@
 
-    \subsubsection{Behavior}
+    \subsubsection{Trace}
     Finally, we include a generic model of how state changes over time.
@@
 
-    \subsection{TODO}
-    TODO
-
-    \subsubsection{Observer}
-    TODO
-
-    \subsubsection{Observation}
-    TODO
-
-    \subsubsection{Event}
-    TODO time point and time span (observer dependent)
-
-    \subsection{Our model of the real world}
-    \label{section:theory-world}
+    \subsection{Product, environment, and universe}
+    \label{section:theory-universe}
 
@@
         \centering
-        \includegraphics{./figures/theory-world.pdf}
-        \caption{Illustration of real world concepts}
-        \label{figure:theory-world}
+        \includegraphics{figures/theory-universe.pdf}
+        \caption{Illustration of product, environment, and universe.}
+        \label{figure:theory-universe}
     \end{figure}
@@
 
-    \subsubsection{World state}
-    TODO
-    \[
-        S_{World} = (S_{Prod}, S_{Env}).
-    \]
-
-    \subsubsection{Product state}
+    \subsubsection{Product}
     In our theory, the product state describes the product perfectly at a particular point in time.
@@
     \]
+    TODO
+    \[
+        \overrightarrow{S_{Pro}}: T \rightarrow S_{Pro}.
+    \]
 
-    \subsubsection{Environment state}
+    \subsubsection{Environment}
     Similarly, the environment state describes the environment perfectly at a particular point in time.
@@
     \]
-
-    \subsubsection{World behavior}
     TODO
     \[
-        \overrightarrow{S_{World}} = (\overrightarrow{S_{Prod}}, \overrightarrow{S_{Env}})
+        \overrightarrow{S_{Env}}: T \rightarrow S_{Env}.
     \]
 
-    \subsection{TODO}
+    \subsubsection{Universe}
+    TODO
+    \[
+        S_{Uni} = S_{Pro} \times S_{Env}.
+    \]
+    TODO
+    \[
+        \overrightarrow{S_{Uni}}: T \rightarrow S_{Uni}.
+    \]
+    TODO
+    \[
+        \overrightarrow{S_{Uni}}: T \rightarrow S_{Pro} \times S_{Env}.
+    \]
+    such that $\forall t \in T$
+    \[
+        \overrightarrow{S_{Uni}}(t) = (\overrightarrow{S_{Pro}}(t), \overrightarrow{S_{Env}}(t))
+    \]
+
+    \subsection{Function}
     TODO
 
-    \subsubsection{Input}
-    TODO
-
-    \subsubsection{Output}
-    TODO
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics{./figures/theory-world.pdf}
+        \caption{Illustration of real world concepts}
+        \label{figure:theory-function}
+    \end{figure}
 
     \subsubsection{Function}
-    TODO
+    Based on the concept of product and environment we can define the product function.
+    The product function describes the logic of how the product reacts to the environment state over time.
+    This logic can be described as mapping from environment trace to product trace, i.e.
+    \[
+        F_{Pro}: \overrightarrow{S_{Env}} \rightarrow \overrightarrow{S_{Pro}}
+    \]
+    Similarly, we can define the environment function.
+    The environment function describes the logic of how the environment reacts to the product state over time.
+    Hence, this logic can be described as mapping from product trace to environment trace, i.e.
+    \[
+        F_{Env}: \overrightarrow{S_{Pro}} \rightarrow \overrightarrow{S_{Env}}
+    \]
 
-    %\subsubsection{Product function}
-    %Based on product and environment state we can define the product function.
-    %The product function describes the logic of how the product reacts to the environment.
-    %This logic can be described as mapping from environment behavior to product behavior, i.e.
-    %\[
-    %    F_{Prod}: \overrightarrow{S_{Env}} \rightarrow \overrightarrow{S_{Prod}}
-    %\]
-
-    %\subsubsection{Environment function}
-    %Similarly, we can define the environment function.
-    %The environment function describes the logic of how the environment reacts to the product.
-    %Hence, this logic can be described as mapping from product behavior to environment behavior, i.e.
-    %\[
-    %    F_{Env}: \overrightarrow{S_{Prod}} \rightarrow \overrightarrow{S_{Env}}
-    %\]
-
-    %\subsubsection{World behavior}
+    %\subsubsection{Universe function}
     %Finally, based on product state and function as well as environment state and function we introduce world behavior.
@@
     %\[
-    %    B_{World} = (\overrightarrow{S_{Prod}}, \overrightarrow{S_{Env}})
+    %    B_{World} = (\overrightarrow{S_{Pro}}, \overrightarrow{S_{Env}})
     %\]
@@
     %\[
-    %    \overrightarrow{S_{Env}} = F_{Env}(\overrightarrow{S_{Prod}})
+    %    \overrightarrow{S_{Env}} = F_{Env}(\overrightarrow{S_{Pro}})
     %\]
@@
     %\[
-    %    \overrightarrow{S_{Prod}} = F_{Prod}(\overrightarrow{S_{Env}}).
+    %    \overrightarrow{S_{Prod}} = F_{Pro}(\overrightarrow{S_{Env}}).
     %\]
+
+    %\subsection{TODO}
+    %TODO
+
+    %\subsubsection{Observer}
+    %TODO
+
+    %\subsubsection{Observation}
+    %TODO
+
+    %\subsubsection{Event}
+    %TODO time point and time span (observer dependent)
 
